### 2024-02-02 docs/lit_codes_explore.qmd
Initial code explore doc

---
title: "literature coding explore"
date: "`r Sys.Date()`"
format:
 html: 
  self-contained: true
editor: visual
toc: TRUE
toc-title: "On this page"
theme: yeti
fontcolor: "#134f5c"
---

## Selecting the literature that was included in this systematic review

In June 2022 a systematic search was completed using Web of Science to identify articles that mentioned factors that either contributed to "successful" implementation of dynamic ocean management (DOM), hereafter referred to as a "bridge". Literature that discussed factors that would need to be addressed or considered prior to effective implementation of dynamic management approaches or tools were also included, hereafter referred to as a "barrier". In this systematic review, we coded bridges and barriers that were related to DOM voluntary programs or enforced regulations, as well as those that were related to tools (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.

During the initial search, the following table of primary and secondary terms were used:

| Primary term               | Secondary term |
|----------------------------|----------------|
| Dynamic ocean management   | Success        |
| Dynamic spatial management | Efficiency     |
| Adaptive management        | Obstacles      |
| Dynamic closures           | Limitations    |
| Bycatch reduction          |                |
| Habitat preference         |                |

A search was completed in Web of Science for each combination of primary and secondary terms. Works from the primary (i.e., peer reviewed journals) and grey (e.g., theses, book chapters) were included, and this initial search resulted in 1,351 articles. The titles and abstracts for each of these documents were scanned for relevance, and the inclusion of the terms 'dynamic' or 'adaptive' management were confirmed. From this cut, a remaining 127 articles were saved. An additional search through the NOAA Institutional Repository and Federal Register was also completed. Here, documents such as policy reports and planning documents were selected. This search resulted in 795 documents. The titles and abstracts for each of these documents were scanned for relevance, and ultimately, 10 articles were saved for a full read through to determine final inclusion. Inclusion and exclusion criteria for both queries are described here:

| Inclusion                                                                                                                                                                                                  | Exclusion                                                                                                                                                                                                    |
|------------------------------------|:-----------------------------------|
| All cases where adaptive or near-real time forms of management or tools that support this form of management were discussed, even if the specific term 'Dynamic Ocean Management' was not explicitly used. | The term 'DOM' was mentioned, or even recommended, but there was no discussion as to why (e.g. SDM studies that suggest DOM applications as a next step for their model)                                     |
| All cases where near real-time SDM tools or fleet-wide communication to avoid negative species interactions.                                                                                               | Articles that involved changes or updates to environmental data stores or remote sensing tools used for developing SDM tools to support DOM, but DOM was not specifically applied, recommended, or reviewed. |

The final list of included works consisted of 137 documents. Each of these were fully read by two reviewers and went through a final pass for determining inclusion. Additional snowball sampling was performed to identify and include articles that were referenced in this list. The abstracts of these referenced articles were read and their inclusion was determined. Lastly, the search ended in August 2023 and articles or documents published after this date were not included in this review. The final list of works analyzed for the review included 110 articles (i.e., primary literature, student theses, policy reports, textbook chapters).

## Coding the bridges and barriers as identified in the literature

Two reviewers went through each of the 110 articles to identify pieces of text that were related to the "successful" implementation of DOM or its recommendation, as well as the barriers or obstacles that hindered the efficacy of this approach or must be considered prior to it's broader application. Through this effort, 17 "bridges" and 9 "barriers" themes were coded. For both the bridges and barriers code categories, three larger groups were established: species, social, and data factors. A draft of the full list of codes/themes are depicted here. Please note that this was a draft of codes, and thus a few themes may be missing or the exact language may be revised over time.

::: panel-tabset
### Bridges

![](images/sunburst_success.png){fig-align="center" width="100%"}

### Barriers

![](images/sunburst_limits.png){width="100%"}
:::

## Visualizing the bridges and barriers themes from the literature

Below is a first attempt at how to visualize some of the data collected from this review. This first section represents general information about the articles selected for this review (e.g., study location, fisheries or shipping channels involved, species for which the tool or management program was established for).

### Study information

::: panel-tabset
#### Study regions

#### Study fisheries and shipping channels

#### Study species

#### Conservation problem being addressed
:::

### Code counts/frequencies

### Codes vs. study information

### Code co-occurrence themes

::: panel-tabset
#### All codes

#### Bridges codes

#### Barriers codes
:::

### Keywords and literature type

::: panel-tabset
#### Keywords

#### Literature type
:::

### 2024-02-02 scripts/1a_sunburst_fig.R

@@ -1,27 +1,0 @@
-#library
-library(plotly)
-
-#sunburst plot 
-d <- data.frame(
-  ids = c(
-    "Species", "Social", "Data", "Associations", "Dynamic range", "Natural history", "Habitat separations", "Limited prey",
-    "Fine scale management", "Coop management", "Incentivized", "Implementation", "Existing management",
-    "Resources","Species data", "Technology", "Environmental data", "Open access", "Scale",
-    "Social data"
-  ),
-  labels = c(
-    "Species", "Social", "Data", "Associations", "Dynamic<br>range", "Natural<br>history", "Habitat<br>separations", "Limited<br>prey",
-    "Fine<br>scale<br>management", "Coop<br>management", "Incentivized", "Implementation", "Existing<br>management",
-    "Resources","Species<br>data", "Technology", "Environmental<br>data", "Open<br>access", "Scale",
-    "Social<br>data"
-  ),
-  parents = c(
-    "", "", "", "Species","Species","Species","Species","Species","Species","Social","Social","Social","Social","Social","Data","Data","Data","Data","Data","Data"
-  ),
-  colors = c("dodgerblue4", "cadetblue4", "rosybrown4", "dodgerblue1", "dodgerblue1", "dodgerblue1", "dodgerblue1", "dodgerblue1", "dodgerblue1", "cadetblue2","cadetblue2", "cadetblue2", "cadetblue2","cadetblue2","rosybrown2","rosybrown2","rosybrown2","rosybrown2","rosybrown2","rosybrown2"),
-  stringsAsFactors = FALSE
-)
-
-fig <- plot_ly(d, ids = ~ids, labels = ~labels, parents = ~parents, type = 'sunburst', insidetextorientation='radial') %>% layout(colorway = ~colors)
-
-fig

### 2024-02-03 docs/lit_codes_explore.qmd
study info figures added to lit explore doc

@@
 ---
+
+```{r}
+#| include: false
+#| echo: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(tidyquant)
+library(here)
+
+codes_vars <- read.csv(here("data/code_w_vars.csv"))
+code_freq <- read.csv(here("data/code_freq2.csv"))
+keywords <- read.csv(here("data/keywords.csv"))
+occur_all <- read.csv(here("data/overlap_all.csv"))
+occur_br <- read.csv(here("data/overlap_bridge.csv"))
+occur_ba <- read.csv(here("data/overlap_barrier.csv"))
+```
 
@@
 
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 7
+
+codes_vars$broad_location <- as.factor(codes_vars$broad_location)
+codes_LU <- codes_vars[!duplicated(codes_vars$Lit_unit), ]
+reg_s <- codes_LU %>%
+  group_by(broad_location) %>%
+  filter(broad_location != "NA" & broad_location != "Europe and United States") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+reg_bar <- ggplot(reg_s) +
+  geom_bar(aes(x = perc, y = reorder(broad_location, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 48))+
+  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
+  geom_text(aes(x = perc, y = broad_location, label = broad_location),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Econ Sans Cnd",
+    size = 3.5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 13)
+  )
+
+reg_bar
+```
+
 #### Study fisheries and shipping channels
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-height: 10
+#| fig-width: 10
+fsh_shp <- codes_LU %>%
+  gather(col, fsh_shp, fishery_or_channel1:fishery_or_channel4) %>%
+  subset(select = fsh_shp)
+
+fsh_shp_s <- fsh_shp %>%
+  group_by(fsh_shp) %>%
+  filter(fsh_shp != "NA") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+fsh_shp_bar <- ggplot(fsh_shp_s) +
+  geom_bar(aes(x = perc, y = reorder(fsh_shp, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 14))+
+  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 15)) + 
+  geom_text(aes(x = perc, y = fsh_shp, label = fsh_shp),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Econ Sans Cnd",
+    size = 5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 16)
+  )
+
+fsh_shp_bar
+```
 
@@
 
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 7
+
+species <- codes_LU %>%
+  gather(col, taxa, focal_taxa1:focal_taxa3) %>%
+  subset(select = taxa)
+
+spp_s <- species %>%
+  group_by(taxa) %>%
+  filter(taxa != "NA" & taxa != "Marine mammals") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+taxa_bar <- ggplot(spp_s) +
+  geom_bar(aes(x = perc, y = reorder(taxa, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 23))+
+  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
+  geom_text(aes(x = perc, y = taxa, label = taxa),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Econ Sans Cnd",
+    size = 3.5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 13)
+  )
+
+taxa_bar
+```
+
 #### Conservation problem being addressed
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 7
+
+consv <- codes_LU %>%
+  gather(col, consv_topic, reason1:reason3) %>%
+  subset(select = consv_topic)
+
+consv_s <- consv %>%
+  group_by(consv_topic) %>%
+  filter(consv_topic != "NA") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+consv_bar <- ggplot(consv_s) +
+  geom_bar(aes(x = perc, y = reorder(consv_topic, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 18))+
+  scale_y_discrete(expand = expansion(add = c(0,0))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
+  geom_text(aes(x = perc, y = consv_topic, label = consv_topic),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Econ Sans Cnd",
+    size = 3.5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 13)
+  )
+
+consv_bar
+```
 :::

### 2024-02-03 docs/lit_codes_explore.qmd
update lit coding explore

@@
 title: "literature coding explore"
+author: "Emily Nazario | UC Santa Cruz | enazario'@'ucsc.edu"
 date: "`r Sys.Date()`"

### 2024-04-05 reports/lit_codes_explore.qmd
update figures for quarto doc

--- 2024-02-03 docs/lit_codes_explore.qmd
@@
 library(here)
+library(kableExtra)
+library(waffle)
+library(extrafont)
+library(hrbrthemes)
+library(patchwork)
 
-codes_vars <- read.csv(here("data/code_w_vars.csv"))
-code_freq <- read.csv(here("data/code_freq2.csv"))
-keywords <- read.csv(here("data/keywords.csv"))
-occur_all <- read.csv(here("data/overlap_all.csv"))
-occur_br <- read.csv(here("data/overlap_bridge.csv"))
-occur_ba <- read.csv(here("data/overlap_barrier.csv"))
+code_freq <- read.csv(here("data/code_freq_032224.csv"))
+codes_vars <- read.csv(here("data/code_w_vars_032224.csv"))
+keywords <- read.csv(here("data/keywords_032224.csv"))
+occur_all <- read.csv(here("data/code_configs_all_032224.csv"))
+occur_br <- read.csv(here("data/code_configs_bridges_032224.csv"))
+occur_ba <- read.csv(here("data/code_configs_barriers_032224.csv"))
+
+#change codes to new names 
+  #code_freq
+    #sp br  
+code_freq$code_cat <- replace(code_freq$code_cat, code_freq$code_cat == "Species bridge", "Ecological bridge")
+code_freq$code_cat <- replace(code_freq$code_cat, code_freq$code_cat == "Species barrier", "Ecological barrier")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Limited Prey Resources", "Target species is a prey specialist")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Fine Scale management required", "Fine-scale management appropriate for target species")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Migratory and/or dynamic range", "Highly mobile target species")
+code_freq$code_name[code_freq$code_cat == "Ecological bridge" & code_freq$code_name == "Climate change"] <- "Expected climate change induced range shifts"
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Known Species Nat History", "Life history information available for target species")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Distinct Habitat between target and non-target species", "Distinct habitat preferences among species in system")
+
+    #data br
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Advances in Tech", "Access to advanced technology and techniques")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Scale appropriate for system", "Management scale aligns with system needs")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Open-Access Public Data", "Data transparency and accessibility")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Availability for species", "Target species data availability")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Stakeholder/Anthropogenic Data Access", "Resource use data availability")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Enviro Access", "Abiotic data availability")
+
+    #soc br
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Open Communication or Co-Mngmt in place", "Co-management and communication")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Adoption Interests & Incentives", "Adoption incentives for end users")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Pre-existing regulation & management institutions", "Pre-existing regulation and management institutions")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "DOM implementation feasible (Socio-econ)", "Feasibility")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Resource Availability (economical)", "Resource availability")
+
+  #sp ba 
+code_freq$code_cat[code_freq$code_name == "Model Abuse"] <- "Data barrier"
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Switch to multi-species mngmnt", "Need for multispecies management")
+
+  #data ba
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Gaps and Accuracy", "Gaps and inaccuracy")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Model Abuse", "Model abuse")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Mismatch in scale", "Management scales do not align with system needs")
+code_freq$code_cat[code_freq$code_name == "Climate change"] <- "Data barrier"
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Climate change", "Climate change adding uncertainty to target species habitat use")
+
+  #soc ba
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Unintended consequences", "Indirect socioeconomic consequences")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Political permanence", "Lack of political administration permanence")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Communication & Distribution", "Poor communication and outreach")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Recipient participation", "Poor program implementation")
+code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Cost", "Implementation costs")
+
 ```
@@
 Literature that discussed factors that would need to be addressed or considered prior to effective implementation of dynamic management approaches or tools were also included, hereafter referred to as a "barrier".
-In this systematic review, we coded bridges and barriers that were related to DOM voluntary programs or enforced regulations, as well as those that were related to tools (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.
+In this systematic review, we coded bridges and barriers that were related to DOM voluntary programs and/or enforced regulations, as well as those that were related to tool development (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.
 
@@
 Works from the primary (i.e., peer reviewed journals) and grey (e.g., theses, book chapters) were included, and this initial search resulted in 1,351 articles.
-The titles and abstracts for each of these documents were scanned for relevance, and the inclusion of the terms 'dynamic' or 'adaptive' management were confirmed.
+The abstracts for each of these documents were scanned for relevance, and the inclusion of the terms 'dynamic' or 'adaptive' management were confirmed.
 From this cut, a remaining 127 articles were saved.
@@
 This search resulted in 795 documents.
-The titles and abstracts for each of these documents were scanned for relevance, and ultimately, 10 articles were saved for a full read through to determine final inclusion.
+The abstracts or content summaries for each of these documents were scanned for relevance, and 10 articles were saved for a full read through to determine final inclusion.
 Inclusion and exclusion criteria for both queries are described here:
@@
 
-Two reviewers went through each of the 110 articles to identify pieces of text that were related to the "successful" implementation of DOM or its recommendation, as well as the barriers or obstacles that hindered the efficacy of this approach or must be considered prior to it's broader application.
-Through this effort, 17 "bridges" and 9 "barriers" themes were coded.
-For both the bridges and barriers code categories, three larger groups were established: species, social, and data factors.
-A draft of the full list of codes/themes are depicted here.
-Please note that this was a draft of codes, and thus a few themes may be missing or the exact language may be revised over time.
+Two reviewers went through each of the 110 articles to identify pieces of text that were related to DOM bridges that were linked to the approaches success or were used as justification when systems recommended its adoption.
+The reviewers also identified the barriers that hindered the efficacy of DOM or must be considered prior to it's broader application.
+Through this effort, 19 "bridge" and 10 "barrier" categories were determined.
+For both the bridge and barrier code categories, three larger "umbrella" groups were established: species, social, and data.
+A table of the full list of codes/themes are depicted here.
+Please note that this is a draft of codes, and thus we are happy to modify the terminology throughout the study review process.
 
@@
 
-![](images/sunburst_success.png){fig-align="center" width="100%"}
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+bri_codes <- code_freq %>% 
+  filter(bridge_barr == "Bridge") %>% 
+  subset(select = -c(total, bridge_barr))
+
+colnames(bri_codes) <- c("Code category", "Code label")
+
+bri_codes %>%
+  kbl() %>%
+  kable_styling()
+```
 
@@
 
-![](images/sunburst_limits.png){width="100%"}
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+
+bar_codes <- code_freq %>% 
+  filter(bridge_barr == "Barrier") %>% 
+  subset(select = -c(total, bridge_barr))
+
+colnames(bar_codes) <- c("Code category", "Code label")
+
+bar_codes %>%
+  kbl() %>%
+  kable_styling()
+```
 :::
 
-## Visualizing the bridges and barriers themes from the literature
+## Visualizing the bridges and barrier codes from the literature
 
@@
 
-### Code counts/frequencies
+### Code appearance frequencies across articles (n = 109)
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+codes_vars2 = codes_vars
+colnames(codes_vars2) <- gsub(x = colnames(codes_vars2), pattern = "\\.", replacement = " ")
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+code_freq_new <- codes_vars2 %>%
+  mutate(br_pos = as.numeric(if_any(33:48, ~. == 1)), 
+         ba_pos = as.numeric(if_any(49:58, ~. == 1)), 
+         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Abiotic data availability", "Resource use data availability"), ~.
+== 1)),
+         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species"), ~.
+== 1)),
+         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication"), ~.
+== 1)),
+         ba_dat = as.numeric(if_any(c("Implementation costs", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~.
+== 1)),
+         ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
+         ba_soc = as.numeric(if_any(c("Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~.
+== 1)))
+
+brba_sum <- code_freq_new %>%
+  summarise(n_br = sum(br_pos), freq_br = n_br/109,
+            n_ba = sum(ba_pos), freq_ba = n_ba/109,
+            n_br_e = sum(br_eco), freq_br_e = n_br_e/109,
+            n_br_d = sum(br_dat), freq_br_d = n_br_d/109,
+            n_br_s = sum(br_soc), freq_br_s = n_br_s/109,
+            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/109,
+            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/109,
+            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/109) %>%
+  gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16)) %>%
+  subset(select = c(br_ba, value)) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 1), 
+         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s", -value, value),
+         code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
+                              if_else(br_ba %in% c("freq_ba_e", "freq_br_e"), "Ecological bridge or barrier", 
+                              if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
+                              if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA)))),
+         code_brba = if_else(br_ba %in% c("freq_br", "freq_br_e", "freq_br_s", "freq_br_d"), "bridge", "barrier"),
+         alpha_brba = if_else(br_ba %in% c("freq_br_e", "freq_br_s", "freq_br_d", "freq_ba_e", "freq_ba_s", "freq_ba_d"), "alpha", "no_alpha")) %>%
+  group_by(code_level)
+
+brba_sum$code_level <- factor(brba_sum$code_level, levels = c("Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier", "Overall bridge or barrier"))
+
+ggplot(brba_sum, aes(x = code_level, 
+             y = percent,
+             fill = code_brba)) +
+  geom_col(width = 0.7) +
+  geom_text(aes(label = percent_label),
+            position = position_stack(vjust = 0.5),
+            color = "black", 
+            size = 5) +
+  ylim(-0.6,1)+
+  coord_flip() +
+  scale_x_discrete() +
+  scale_fill_manual(values = c("lightskyblue3", "goldenrod"), labels = c("Barrier frequency", "Bridge frequency")) +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.x =element_blank(),
+        axis.text.y = element_text(size = 20, color = "black"),
+        panel.grid = element_blank(),
+        legend.position = c(-0.21, 0.99),
+        legend.text = element_text(size = 16, color = "black"),
+        strip.text.y.right = element_text(angle = 0, size = 16)) +
+  geom_hline(yintercept = 0.0, linewidth = 1) + 
+  labs(fill = "")+ 
+  guides(fill = guide_legend(nrow = 1))
+```
 

### 2024-04-08 reports/lit_codes_explore.qmd
update bridge and barrier plot

@@
 
-#### Study species
+#### Study taxa
 
@@
 taxa_bar
+```
+
+#### Study species
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 12
+
+species_Gs <- codes_LU %>%
+  gather(col, sp_name, species1:species16) %>%
+  subset(select = sp_name)
+
+spp_Gs_s <- species_Gs %>%
+  group_by(sp_name) %>%
+  filter(sp_name != "NA") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+sp_bar <- ggplot(spp_Gs_s) +
+  geom_bar(aes(x = perc, y = reorder(sp_name, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 23))+
+  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
+  geom_text(aes(x = perc, y = sp_name, label = sp_name),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Econ Sans Cnd",
+    size = 3.5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 13)
+  )
+
+sp_bar
 ```
@@
 code_freq_new <- codes_vars2 %>%
-  mutate(br_pos = as.numeric(if_any(33:48, ~. == 1)), 
+  mutate(br_pos = as.numeric(if_any(c(33:48, 59:61), ~. == 1)), 
          ba_pos = as.numeric(if_any(49:58, ~. == 1)),
@@
 == 1)),
-         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species"), ~.
+         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~.
 == 1)),
@@
             size = 5) +
-  ylim(-0.6,1)+
+  ylim(-0.7,1)+
   coord_flip() +

### 2024-04-09 reports/lit_codes_explore.qmd
code frequencies figures

@@
 
+::: panel-tabset 
+#### Broader categories
 ```{r}
@@
 
+#### Data frequencies
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+data_freq <- codes_vars2 %>%
+  subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Abiotic data availability", "Resource use data availability","Implementation costs", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
+  gather(category, pres_abs, 1:11) %>%
+  mutate(br_ba = ifelse(category == "Implementation costs" | category == "Gaps and inaccuracy" | category == "Management scales do not align with system needs" | category == "Model abuse" | category == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
+  group_by(category, br_ba)  %>%
+  summarise(n = sum(pres_abs), 
+            freq = (n/109)) %>%
+  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
+  group_by(category)
+
+my_labs <- c("0", "25", "50", "75")
+data_freq$br_ba <- factor(as.factor(data_freq$br_ba), levels = c("Data bridge", "Data barrier"))
+
+data_bar <- ggplot(data_freq) +
+  geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     limits = c(0,0.9),
+                     expand = c(0,0), 
+                     breaks = c(0, 0.25, 0.5, 0.75),
+                     labels = my_labs)+
+  scale_y_discrete(expand = expansion(add = c(0,0))) +
+  tidyquant::theme_tq() +
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+    legend.position = "none", 
+    strip.text = element_text(size = 16)) + 
+  geom_text(aes(x = freq, y = category, label = percent_label),
+    hjust = 0,
+    nudge_x = -0.0001,
+    colour = "black",
+    family = "Econ Sans Cnd",
+    size = 6)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 20)
+  ) + 
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+  facet_wrap(~br_ba, scales = "free", nrow = 2)
+data_bar
+
+```
+
+#### Ecological frequencies 
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+ecol_freq <- codes_vars2 %>%
+  subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
+  gather(category, pres_abs, 1:9) %>%
+  mutate(br_ba = ifelse(category == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
+  group_by(category, br_ba)  %>%
+  summarise(n = sum(pres_abs), 
+            freq = (n/109)) %>%
+  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
+  group_by(category)
+
+ecol_freq$category <- replace(ecol_freq$category, ecol_freq$category == "Fine scale management appropriate for target species", "Fine-scale management appropriate for target species")
+ecol_freq$br_ba <- factor(as.factor(ecol_freq$br_ba), levels = c("Ecological bridge", "Ecological barrier"))
+
+ecol_bar <- ggplot(ecol_freq) +
+  geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     limits = c(0,0.9),
+                     expand = c(0,0), 
+                     breaks = c(0, 0.25, 0.5, 0.75),
+                     labels = my_labs)+
+  scale_y_discrete(expand = expansion(add = c(0,0))) +
+  tidyquant::theme_tq() +
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+    legend.position = "none", 
+    strip.text = element_text(size = 16)) + 
+  geom_text(aes(x = freq, y = category, label = percent_label),
+    hjust = 0,
+    nudge_x = -0.0001,
+    colour = "black",
+    family = "Econ Sans Cnd",
+    size = 6)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 20)
+  ) + 
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+  facet_wrap(~br_ba, scales = "free", nrow = 2)
+
+ecol_bar
+
+```
+
+#### Social frequencies
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+soc_freq <- codes_vars2 %>%
+  subset(select = c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation")) %>%
+  gather(category, pres_abs, 1:9) %>%
+  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+  group_by(category, br_ba)  %>%
+  summarise(n = sum(pres_abs), 
+            freq = (n/109)) %>%
+  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
+  group_by(category)
+
+soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
+soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing regulation and management institutions", "Pre-existing regulation and management institutions")
+soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
+
+soc_bar <- ggplot(soc_freq) +
+  geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     limits = c(0,0.9),
+                     expand = c(0,0), 
+                     breaks = c(0, 0.25, 0.5, 0.75),
+                     labels = my_labs)+
+  scale_y_discrete(expand = expansion(add = c(0,0))) +
+  tidyquant::theme_tq() +
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+    legend.position = "none", 
+    strip.text = element_text(size = 16)) + 
+  geom_text(aes(x = freq, y = category, label = percent_label),
+    hjust = 0,
+    nudge_x = -0.0001,
+    colour = "black",
+    family = "Econ Sans Cnd",
+    size = 6)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 20)
+  ) + 
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+  facet_wrap(~br_ba, scales = "free", nrow = 2)
+soc_bar
+
+```
+:::
+
 ### Codes vs. study information

### 2024-04-09 reports/lit_codes_explore.qmd
revised code appearance frequencies figures

@@
 ### Code appearance frequencies across articles (n = 109)
+The proportions reported in these figures represent the percent of papers included these broader code categories or individual codes.
+Though, if it would be more helpful to report the more fine-scale codes as a percentage of all data/ecological/social codes (i.e., target species data availability made up 60% of all data bridge codes) I could change how these values were calculated.
 
@@
   mutate(percent_label = scales::percent(value, accuracy = 1), 
-         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s", -value, value),
+         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s", value, -value),
          code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
@@
 brba_sum$code_level <- factor(brba_sum$code_level, levels = c("Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier", "Overall bridge or barrier"))
+brba_sum$code_brba <- factor(brba_sum$code_brba, levels = c("bridge", "barrier"))
 
@@
   geom_text(aes(label = percent_label),
-            position = position_stack(vjust = 0.5),
+            position = position_stack(vjust = 0.65),
             color = "black", 
             size = 5) +
-  ylim(-0.7,1)+
+  ylim(-1,1)+
   coord_flip() +
   scale_x_discrete() +
-  scale_fill_manual(values = c("lightskyblue3", "goldenrod"), labels = c("Barrier frequency", "Bridge frequency")) +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
   theme_minimal() +
@@
 
+### Code appearance frequencies within code categories
+
 ### Codes vs. study information
@@
 #### Barriers codes
+
 :::
@@
 #### Literature type
+
 :::

### 2024-04-20 reports/lit_codes_explore.qmd
add w/in code frequencies plots

@@
 ### Code appearance frequencies within code categories
+Here, I have plotted the same information as the previous section, but as a percentage of the overall bridges and barriers groupings.
+For example, data bridges make up 37% of all bridge codes.
+The same pattern holds for the other sub-panels.
+For example, on the ecological page, abiotic indicators account for 22% of all ecological bridge codes.
+
+::: panel-tabset
+
+#### Broader categories
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+code_sum <- code_freq %>%
+  group_by(bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(code_cat) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  summarise(value = n_subtotal/n_total) %>%
+  rename("br_ba" = code_cat) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 1), 
+         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", value, -value),
+         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA))), 
+         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge"), "bridge", "barrier")) %>%
+  group_by(code_level) %>%
+  distinct()
+
+code_sum$code_level <- factor(code_sum$code_level, levels = c("Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier"))
+code_sum$code_brba <- factor(code_sum$code_brba, levels = c("bridge", "barrier"))
+
+ggplot(code_sum, aes(x = code_level, 
+             y = percent,
+             fill = code_brba)) +
+  geom_col(width = 0.7) +
+  geom_text(aes(label = percent_label),
+            position = position_stack(vjust = 0.65),
+            color = "black", 
+            size = 5) +
+  ylim(-0.4,0.7)+
+  coord_flip() +
+  scale_x_discrete() +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.x =element_blank(),
+        axis.text.y = element_text(size = 20, color = "black"),
+        panel.grid = element_blank(),
+        legend.position = c(-0.17, 0.99),
+        legend.text = element_text(size = 16, color = "black"),
+        strip.text.y.right = element_text(angle = 0, size = 16)) +
+  geom_hline(yintercept = 0.0, linewidth = 1) + 
+  labs(fill = "")+ 
+  guides(fill = guide_legend(nrow = 1))
+
+```
+
+#### Data codes
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+data_freq <- code_freq %>%
+  filter(code_cat == "Data bridge" | code_cat == "Data barrier")
+
+data_sum <- data_freq %>%
+  group_by(bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(code_name) %>% 
+  summarise(value = total/n_total) %>%
+  mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Gaps and inaccuracy" | code_name == "Management scales do not align with system needs" | code_name == "Model abuse" | code_name == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 2))
+
+my_labs <- c("0", "25", "50", "75")
+data_sum$code_cat <- factor(as.factor(data_sum$code_cat), levels = c("Data bridge", "Data barrier"))
+
+ggplot(data_sum) +
+  geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     limits = c(0,0.9),
+                     expand = c(0,0), 
+                     breaks = c(0, 0.25, 0.5, 0.75),
+                     labels = my_labs)+
+  scale_y_discrete(expand = expansion(add = c(0,0))) +
+  tidyquant::theme_tq() +
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+    legend.position = "none", 
+    strip.text = element_text(size = 16)) + 
+  geom_text(aes(x = value, y = code_name, label = percent_label),
+    hjust = 0,
+    nudge_x = -0.0001,
+    colour = "black",
+    family = "Econ Sans Cnd",
+    size = 6)+
+  labs(subtitle = "Percent from all data bridges or barriers (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 20)
+  ) + 
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+  facet_wrap(~code_cat, scales = "free", nrow = 2)
+
+```
+
+#### Ecological codes
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+eco_freq <- code_freq %>%
+  filter(code_cat == "Ecological bridge" | code_cat == "Ecological barrier")
+
+eco_sum <- eco_freq %>%
+  group_by(bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(code_name) %>% 
+  summarise(value = total/n_total) %>%
+  mutate(code_cat = ifelse(code_name == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 2))
+
+eco_sum$code_cat <- factor(as.factor(eco_sum$code_cat), levels = c("Ecological bridge", "Ecological barrier"))
+my_labs2 <- c("0", "30")
+
+ggplot(eco_sum) +
+  geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     limits = c(0,0.35),
+                     expand = c(0,0), 
+                     breaks = c(0, 0.3),
+                     labels = my_labs2)+
+  scale_y_discrete(expand = expansion(add = c(0,0))) +
+  tidyquant::theme_tq() +
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+    legend.position = "none", 
+    strip.text = element_text(size = 16)) + 
+  geom_text(aes(x = value, y = code_name, label = percent_label),
+    hjust = 0,
+    nudge_x = -0.0001,
+    colour = "black",
+    family = "Econ Sans Cnd",
+    size = 6)+
+  labs(subtitle = "Percent from all ecological bridges or barriers (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 20)
+  ) + 
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+  facet_wrap(~code_cat, scales = "free", nrow = 2)
+
+```
+
+#### Social codes
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+soc_freq <- code_freq %>%
+  filter(code_cat == "Social bridge" | code_cat == "Social barrier")
+
+soc_sum <- soc_freq %>%
+  group_by(bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(code_name) %>% 
+  summarise(value = total/n_total) %>%
+  mutate(code_cat = ifelse(code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 2))
+
+soc_sum$code_cat <- factor(as.factor(soc_sum$code_cat), levels = c("Social bridge", "Social barrier"))
+my_labs2 <- c("0", "30")
+
+ggplot(soc_sum) +
+  geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     limits = c(0,1),
+                     expand = c(0,0), 
+                     breaks = c(0,0.25, 0.5, 0.75),
+                     labels = my_labs)+
+  scale_y_discrete(expand = expansion(add = c(0,0))) +
+  tidyquant::theme_tq() +
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+    legend.position = "none", 
+    strip.text = element_text(size = 16)) + 
+  geom_text(aes(x = value, y = code_name, label = percent_label),
+    hjust = 0,
+    nudge_x = -0.0001,
+    colour = "black",
+    family = "Econ Sans Cnd",
+    size = 6)+
+  labs(subtitle = "Percent from all social bridges or barriers (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 20)
+  ) + 
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+  facet_wrap(~code_cat, scales = "free", nrow = 2)
+
+```
+:::
 

### 2024-05-14 reports/lit_codes_explore.qmd
Updated DOM review figs

@@
 ### Code appearance frequencies across articles (n = 109)
+
 The proportions reported in these figures represent the percent of papers included these broader code categories or individual codes.
-Though, if it would be more helpful to report the more fine-scale codes as a percentage of all data/ecological/social codes (i.e., target species data availability made up 60% of all data bridge codes) I could change how these values were calculated.
 
@@
 #### Broader categories
+
 ```{r}
@@
 #### Data frequencies
+
 ```{r}
@@
 #### Ecological frequencies
+
 ```{r}
@@
 #### Social frequencies
+
 ```{r}
@@
 ### Code appearance frequencies within code categories
+
 Here, I have plotted the same information as the previous section, but as a percentage of the overall bridges and barriers groupings.
@@
 ::: panel-tabset
-
 #### Broader categories
+
 ```{r}
@@
 #### Data codes
+
 ```{r}
@@
 #### Ecological codes
+
 ```{r}
@@
 #### Social codes
+
 ```{r}
@@
 
-### Codes vs. study information
-
 ### Code co-occurrence themes
-
-::: panel-tabset
-#### All codes
-
 #### Bridges codes
-
-#### Barriers codes
-
-:::
-
-### Keywords and literature type
-
-::: panel-tabset
-#### Keywords
-
-#### Literature type
-
-:::
+This figure depicts how codes from each of the three first degree categories (Ecological, Data, and Social) co-occurred together.
+This figure only includes the top 5 combinations of code co-occurrence and only includes "bridge" codes.
+A figure for the barrier's codes was not completed as no combination of barriers surpassed 3 replicate occurrences.
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+#change codes to new names 
+  #code_freq
+    #sp br  
+occur_br$Species.Bridges <- replace(occur_br$Species.Bridges, occur_br$Species.Bridges == "Limited Prey Resources", "Target species is a prey specialist")
+occur_br$Species.Bridges <- replace(occur_br$Species.Bridges, occur_br$Species.Bridges == "Fine Scale management required", "Fine-scale management appropriate for target species")
+occur_br$Species.Bridges <- replace(occur_br$Species.Bridges, occur_br$Species.Bridges == "Migratory and/or dynamic range", "Highly mobile target species")
+occur_br$Species.Bridges[occur_br$code_cat == "Ecological bridge" & occur_br$Species.Bridges == "Climate change"] <- "Expected climate change induced range shifts"
+occur_br$Species.Bridges <- replace(occur_br$Species.Bridges, occur_br$Species.Bridges == "Known Species Nat History", "Life history information available for target species")
+occur_br$Species.Bridges <- replace(occur_br$Species.Bridges, occur_br$Species.Bridges == "Distinct Habitat between target and non-target species", "Distinct habitat preferences among species in system")
+
+    #data br
+occur_br$Data.Bridge <- replace(occur_br$Data.Bridge, occur_br$Data.Bridge == "Advances in Tech", "Access to advanced technology and techniques")
+occur_br$Data.Bridge <- replace(occur_br$Data.Bridge, occur_br$Data.Bridge == "Scale appropriate for system", "Management scale aligns with system needs")
+occur_br$Data.Bridge <- replace(occur_br$Data.Bridge, occur_br$Data.Bridge == "Open-Access Public Data", "Data transparency and accessibility")
+occur_br$Data.Bridge <- replace(occur_br$Data.Bridge, occur_br$Data.Bridge == "Availability for species", "Target species data availability")
+occur_br$Data.Bridge <- replace(occur_br$Data.Bridge, occur_br$Data.Bridge == "Stakeholder/Anthropogenic Data Access", "Resource use data availability")
+occur_br$Data.Bridge <- replace(occur_br$Data.Bridge, occur_br$Data.Bridge == "Enviro Access", "Abiotic data availability")
+
+    #soc br
+occur_br$Social.Bridges <- replace(occur_br$Social.Bridges, occur_br$Social.Bridges == "Open Communication or Co-Mngmt in place", "Co-management and communication")
+occur_br$Social.Bridges <- replace(occur_br$Social.Bridges, occur_br$Social.Bridges == "Adoption Interests & Incentives", "Adoption incentives for end users")
+occur_br$Social.Bridges <- replace(occur_br$Social.Bridges, occur_br$Social.Bridges == "Pre-existing regulation & management institutions", "Pre-existing regulation and management institutions")
+occur_br$Social.Bridges <- replace(occur_br$Social.Bridges, occur_br$Social.Bridges == "DOM implementation feasible (Socio-econ)", "Feasibility")
+occur_br$Social.Bridges <- replace(occur_br$Social.Bridges, occur_br$Social.Bridges == "Resource Availability (economical)", "Resource availability")
+
+occur_br <- occur_br %>%
+  mutate(names_comb = paste(Data.Bridge, Species.Bridges, Social.Bridges, sep = "; "))
+
+occur_br_fig <- ggplot(head(occur_br)) +
+  geom_bar(aes(x = Documents, y = reorder(names_comb, Documents)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 15))+
+  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_text(size = 9),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
+  geom_text(aes(x = Documents, y = names_comb, label = Documents),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Econ Sans Cnd",
+    size = 3.5)+
+  theme(plot.subtitle = element_text(
+      family = "Econ Sans Cnd",
+      size = 13)
+  )
+
+occur_br_fig
+
+```

### 2024-06-01 reports/lit_codes_explore.qmd
added code relations figures

--- 2024-04-20 reports/lit_codes_explore.qmd
@@
 occur_ba <- read.csv(here("data/code_configs_barriers_032224.csv"))
+code_rel <- read.csv(here("data/code_rel.csv"))
 
@@
 
-### Codes vs. study information
-
 ### Code co-occurrence themes
@@
 ::: panel-tabset
-#### All codes
-
-#### Bridges codes
-
-#### Barriers codes
-
+
+#### All code relations
+This is a heatmap of all code relationships within articles. The number of co-ocurrences represents the number of times two codes co-occurered together in the same article.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 15
+#| fig-height: 12
+#| fig-align: center
+
+code_rel_melt <- reshape::melt(code_rel)
+code_rel_melt$variable <- gsub(".", " ", code_rel_melt$variable, fixed = TRUE)
+
+code_rel_melt <- code_rel_melt %>%
+  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
+
+code_rel_melt$key <- str_trim(code_rel_melt$key)
+
+colnames(code_rel_melt) <- c("brba_code1", "code1", "code2", "total")
+
+ggplot(code_rel_melt, aes(reorder(code1, -total), reorder(code2, total))) +
+geom_tile(aes(fill = total)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+labs(fill = "Number of co-occurences")+
+theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14))+
+geom_text(aes(label = total))
+```
+
+#### Most frequent code relations
+This heatmap represents the same data set as the last figure, but only includes co-occurrence values greater than or equal to 6, which is the 75% quantile of the co-occurrence totals.
+I have also added boxes around totals greater than 11, which was the 90% quantile of the co-occurrence total data set.
+Blue text represents data bridges and barriers, grey text represents ecological bridges and barriers, and orange text represents social bridges and barriers.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+#add brba column to second code col
+code_rel_melt2 <- code_rel_melt
+code_rel_melt2$brba_code2 <- NA
+
+code_rel_melt2$code2[code_rel_melt2$code2 == "Fine scale management appropriate for target species"] <- "Fine-scale management appropriate for target species"
+code_rel_melt2$code2[code_rel_melt2$code2 == "Pre existing regulation and management institutions"] <- "Pre-existing regulation and management institutions"
+code_rel_melt2$code2[code_rel_melt2$code2 == "Co management and communication"] <- "Co-management and communication"
+
+for(i in 1:nrow(code_rel_melt2)){
+  code_temp = code_rel_melt2$code2[i]
+
+  brba_temp = code_rel_melt2 %>% filter(code1 == code_temp & code2 == code_temp)
+  brba_code_temp = brba_temp$brba_code1[1]
+
+  code_rel_melt2$brba_code2[i] <- brba_code_temp
+}
+
+code_rel_melt2$brba_code2[code_rel_melt2$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
+
+group_colors = c("Data Bridge" = "dodgerblue4", "Data Barrier" = "dodgerblue4", "Ecological Bridge" = "honeydew4", "Ecological Barrier" = "honeydew4", "Social Bridge" = "darkorange4", "Social Barrier" = "darkorange4")
+
+code_rel_melt_h <- code_rel_melt2 %>%
+  filter(total >= 6) %>%
+  mutate(bor_box = ifelse(total >= 11, "TRUE", "FALSE"), 
+        bor_box = as.factor(bor_box), 
+        code1 = as.factor(code1), 
+        code2 = as.factor(code2))
+
+code_rel_melt_h$bor_box <- factor(code_rel_melt_h$bor_box, levels = c("TRUE", "FALSE"))
+
+code_rel_melt_h <- code_rel_melt_h %>%
+  mutate(code1 = reorder(code1, -total, FUN = mean),
+         code2 = reorder(code2, total, FUN = mean))
+
+unique_x_groups <- code_rel_melt_h %>%
+distinct(code1, brba_code1) %>%
+arrange(code1)
+
+unique_y_groups <- code_rel_melt_h %>%
+distinct(code2, brba_code2) %>%
+arrange(code2)
+
+x_colors <- setNames(group_colors[unique_x_groups$brba_code1], unique_x_groups$code1)
+y_colors <- setNames(group_colors[unique_y_groups$brba_code2], unique_y_groups$code2)
+
+ggplot(code_rel_melt_h, aes(reorder(code1, -total), reorder(code2, total))) +
+geom_tile(aes(fill = total, colour = bor_box)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+labs(fill = "Number of co-occurences")+
+theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]))+
+geom_text(aes(label = total))+
+scale_color_manual(values = c("black", "#00000000"))+
+guides(color = "none")
+
+```
+
+#### Data code relations
+This is a look at the data bridge and barrier code relations.
+Totals higher than or equal to 14 (90th quantile for data totals) are outlined in black.Here, red text represents codes that are barriers, and green text represents codes that are bridges.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+code_rel_d <- read.csv(here("data/code_rel_d.csv"))
+
+code_rel_melt_d <- reshape::melt(code_rel_d)
+code_rel_melt_d$variable <- gsub(".", " ", code_rel_melt_d$variable, fixed = TRUE)
+
+code_rel_melt_d <- code_rel_melt_d %>%
+  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
+
+code_rel_melt_d$key <- str_trim(code_rel_melt_d$key)
+
+colnames(code_rel_melt_d) <- c("brba_code1", "code1", "code2", "total")
+
+code_rel_melt2_d <- code_rel_melt_d
+code_rel_melt2_d$brba_code2 <- NA
+code_rel_melt2_d$brba_key1 <- NA
+code_rel_melt2_d$brba_key2 <- NA
+
+for(i in 1:nrow(code_rel_melt2_d)){
+  code_temp = code_rel_melt2_d$code2[i]
+
+  brba_temp = code_rel_melt2_d %>% filter(code1 == code_temp & code2 == code_temp)
+  brba_code_temp = brba_temp$brba_code1[1]
+
+  code_rel_melt2_d$brba_code2[i] <- brba_code_temp
+
+  if(grepl("Bridge", code_rel_melt2_d$brba_code1[i])){
+      code_rel_melt2_d$brba_key1[i] = "Bridge"
+  } else if(grepl("Barrier", code_rel_melt2_d$brba_code1[i])){
+      code_rel_melt2_d$brba_key1[i] = "Barrier"
+  }
+
+  if(grepl("Bridge", code_rel_melt2_d$brba_code2[i])){
+      code_rel_melt2_d$brba_key2[i] = "Bridge"
+  } else if(grepl("Barrier", code_rel_melt2_d$brba_code2[i])){
+      code_rel_melt2_d$brba_key2[i] = "Barrier"
+  }
+}
+
+code_rel_melt2_d <- code_rel_melt2_d %>%
+  mutate(bor_box = ifelse(total >= 14, "TRUE", "FALSE"), 
+        bor_box = as.factor(bor_box), 
+        code1 = as.factor(code1), 
+        code2 = as.factor(code2))
+
+code_rel_melt2_d$bor_box <- factor(code_rel_melt2_d$bor_box, levels = c("TRUE", "FALSE"))
+
+code_rel_melt2_d <- code_rel_melt2_d %>%
+  mutate(code1 = reorder(code1, -total, FUN = mean),
+         code2 = reorder(code2, total, FUN = mean))
+
+brba_colors <- c("Bridge" = "darkolivegreen", "Barrier" = "red4")
+
+unique_x_groups <- code_rel_melt2_d %>%
+distinct(code1, brba_key1) %>%
+arrange(code1)
+
+unique_y_groups <- code_rel_melt2_d %>%
+distinct(code2, brba_key2) %>%
+arrange(code2)
+
+x_colors <- setNames(brba_colors[unique_x_groups$brba_key1], unique_x_groups$code1)
+y_colors <- setNames(brba_colors[unique_y_groups$brba_key2], unique_y_groups$code2)
+
+ggplot(code_rel_melt2_d, aes(reorder(code1, -total), reorder(code2, total))) +
+geom_tile(aes(fill = total, colour = bor_box)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+labs(fill = "Number of co-occurences")+
+theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt2_d$code1)]), 
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt2_d$code2)]))+
+geom_text(aes(label = total))+
+scale_color_manual(values = c("black", "#00000000"))+
+guides(color = "none")
+
+```
+
+#### Ecological code relations
+This is a look at the ecological bridge and barrier code relations.
+Totals higher than or equal to 5 (90th quantile for ecological totals) are outlined in black.Here, red text represents codes that are barriers, and green text represents codes that are bridges.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+code_rel_e <- read.csv(here("data/code_rel_e.csv"))
+
+code_rel_melt_e <- reshape::melt(code_rel_e)
+code_rel_melt_e$variable <- gsub(".", " ", code_rel_melt_e$variable, fixed = TRUE)
+
+code_rel_melt_e <- code_rel_melt_e %>%
+  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
+
+code_rel_melt_e$key <- str_trim(code_rel_melt_e$key)
+
+colnames(code_rel_melt_e) <- c("brba_code1", "code1", "code2", "total")
+
+code_rel_melt2_e <- code_rel_melt_e
+code_rel_melt2_e$brba_code2 <- NA
+code_rel_melt2_e$brba_key1 <- NA
+code_rel_melt2_e$brba_key2 <- NA
+
+code_rel_melt2_e$code2[code_rel_melt2_e$code2 == "Fine scale management appropriate for target species"] <- "Fine-scale management appropriate for target species"
+code_rel_melt2_e$brba_code2[code_rel_melt2_e$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
+
+for(i in 1:nrow(code_rel_melt2_e)){
+  code_temp = code_rel_melt2_e$code2[i]
+
+  brba_temp = code_rel_melt2_e %>% filter(code1 == code_temp & code2 == code_temp)
+  brba_code_temp = brba_temp$brba_code1[1]
+
+  code_rel_melt2_e$brba_code2[i] <- brba_code_temp
+
+  if(grepl("Bridge", code_rel_melt2_e$brba_code1[i])){
+      code_rel_melt2_e$brba_key1[i] = "Bridge"
+  } else if(grepl("Barrier", code_rel_melt2_e$brba_code1[i])){
+      code_rel_melt2_e$brba_key1[i] = "Barrier"
+  }
+
+  if(grepl("Bridge", code_rel_melt2_e$brba_code2[i])){
+      code_rel_melt2_e$brba_key2[i] = "Bridge"
+  } else if(grepl("Barrier", code_rel_melt2_e$brba_code2[i])){
+      code_rel_melt2_e$brba_key2[i] = "Barrier"
+  }
+}
+code_rel_melt2_e$brba_code2[code_rel_melt2_e$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
+code_rel_melt2_e$brba_key2[code_rel_melt2_e$code2 == "Target species is a prey specialist"] <- "Bridge"
+
+code_rel_melt2_e <- code_rel_melt2_e %>%
+  mutate(bor_box = ifelse(total >= 5, "TRUE", "FALSE"), 
+        bor_box = as.factor(bor_box), 
+        code1 = as.factor(code1), 
+        code2 = as.factor(code2))
+
+code_rel_melt2_e$bor_box <- factor(code_rel_melt2_e$bor_box, levels = c("TRUE", "FALSE"))
+
+code_rel_melt2_e <- code_rel_melt2_e %>%
+  mutate(code1 = reorder(code1, -total, FUN = mean),
+         code2 = reorder(code2, total, FUN = mean))
+
+unique_x_groups <- code_rel_melt2_e %>%
+distinct(code1, brba_key1) %>%
+arrange(code1)
+
+unique_y_groups <- code_rel_melt2_e %>%
+distinct(code2, brba_key2) %>%
+arrange(code2)
+
+x_colors <- setNames(brba_colors[unique_x_groups$brba_key1], unique_x_groups$code1)
+y_colors <- setNames(brba_colors[unique_y_groups$brba_key2], unique_y_groups$code2)
+
+ggplot(code_rel_melt2_e, aes(reorder(code1, -total), reorder(code2, total))) +
+geom_tile(aes(fill = total, colour = bor_box)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+labs(fill = "Number of co-occurences")+
+theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt2_e$code1)]), 
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt2_e$code2)]))+
+geom_text(aes(label = total))+
+scale_color_manual(values = c("black", "#00000000"))+
+guides(color = "none")
+
+```
+
+#### Social code relations
+This is a look at the social bridge and barrier code relations.
+Totals higher than or equal to 5 (90th quantile for social totals) are outlined in black.Here, red text represents codes that are barriers, and green text represents codes that are bridges.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+code_rel_s <- read.csv(here("data/code_rel_s.csv"))
+
+code_rel_melt_s <- reshape::melt(code_rel_s)
+code_rel_melt_s$variable <- gsub(".", " ", code_rel_melt_s$variable, fixed = TRUE)
+
+code_rel_melt_s <- code_rel_melt_s %>%
+  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
+
+code_rel_melt_s$key <- str_trim(code_rel_melt_s$key)
+
+colnames(code_rel_melt_s) <- c("brba_code1", "code1", "code2", "total")
+
+code_rel_melt2_s <- code_rel_melt_s
+code_rel_melt2_s$brba_code2 <- NA
+code_rel_melt2_s$brba_key1 <- NA
+code_rel_melt2_s$brba_key2 <- NA
+
+code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Pre existing regulation and management institutions"] <- "Pre-existing regulation and management institutions"
+code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Co management and communication"] <- "Co-management and communication"
+
+for(i in 1:nrow(code_rel_melt2_s)){
+  code_temp = code_rel_melt2_s$code2[i]
+
+  brba_temp = code_rel_melt2_s %>% filter(code1 == code_temp & code2 == code_temp)
+  brba_code_temp = brba_temp$brba_code1[1]
+
+  code_rel_melt2_s$brba_code2[i] <- brba_code_temp
+
+  if(grepl("Bridge", code_rel_melt2_s$brba_code1[i])){
+      code_rel_melt2_s$brba_key1[i] = "Bridge"
+  } else if(grepl("Barrier", code_rel_melt2_s$brba_code1[i])){
+      code_rel_melt2_s$brba_key1[i] = "Barrier"
+  }
+
+  if(grepl("Bridge", code_rel_melt2_s$brba_code2[i])){
+      code_rel_melt2_s$brba_key2[i] = "Bridge"
+  } else if(grepl("Barrier", code_rel_melt2_s$brba_code2[i])){
+      code_rel_melt2_s$brba_key2[i] = "Barrier"
+  }
+}
+
+code_rel_melt2_s <- code_rel_melt2_s %>%
+  mutate(bor_box = ifelse(total >= 5, "TRUE", "FALSE"), 
+        bor_box = as.factor(bor_box), 
+        code1 = as.factor(code1), 
+        code2 = as.factor(code2))
+
+code_rel_melt2_s$bor_box <- factor(code_rel_melt2_s$bor_box, levels = c("TRUE", "FALSE"))
+
+code_rel_melt2_s <- code_rel_melt2_s %>%
+  mutate(code1 = reorder(code1, -total, FUN = mean),
+         code2 = reorder(code2, total, FUN = mean))
+
+unique_x_groups <- code_rel_melt2_s %>%
+distinct(code1, brba_key1) %>%
+arrange(code1)
+
+unique_y_groups <- code_rel_melt2_s %>%
+distinct(code2, brba_key2) %>%
+arrange(code2)
+
+x_colors <- setNames(brba_colors[unique_x_groups$brba_key1], unique_x_groups$code1)
+y_colors <- setNames(brba_colors[unique_y_groups$brba_key2], unique_y_groups$code2)
+
+ggplot(code_rel_melt2_s, aes(reorder(code1, -total), reorder(code2, total))) +
+geom_tile(aes(fill = total, colour = bor_box)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+labs(fill = "Number of co-occurences")+
+theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt2_s$code1)]), 
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt2_s$code2)]))+
+geom_text(aes(label = total))+
+scale_color_manual(values = c("black", "#00000000"))+
+guides(color = "none")
+
+```
 :::
-
-### Keywords and literature type
-
-::: panel-tabset
-#### Keywords
-
-#### Literature type
-
-:::

### 2024-06-03 reports/lit_codes_explore.qmd
sankey plot

@@
 library(patchwork)
+library(ggalluvial)
+library(ggrepel)
+library(forcats)
 
@@
 :::
+
+### Sankey diagram of code heirarchies 
+Here, each of the codes and their subcodes are presented. The presented percentages represent totals across all codes.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 15
+#| fig-height: 10
+
+sankey_df <- read.csv(here("data/sankey_freq.csv"))
+
+sankey_df$code_cat <- factor(sankey_df$code_cat, levels = c("Data barrier", "Ecological barrier", "Social barrier", "Data bridge", "Ecological bridge", "Social bridge"))
+
+sankey_df <- sankey_df %>%
+mutate(sum_codes = sum(total), 
+      perc_codes = (total/sum_codes)*100, 
+      round_perc = round(perc_codes, 0))
+
+ggplot(data = sankey_df,
+       aes(axis1 = fct_reorder(bridge_barr, -perc_codes), axis2 = fct_reorder(code_cat, -perc_codes), axis3 = fct_reorder(code_name, -perc_codes), y = perc_codes)) +
+  geom_alluvium(aes(fill = code_cat, color = code_cat), size = 1.5, alpha = 0.8, width = 0.05) +
+  geom_stratum(size = 1.5, color = "grey60", 
+              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
+  geom_text(stat = "stratum", 
+    aes(label = after_stat(stratum)),
+    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
+    size = c(7,7,5,5,5,5,5,5,3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3,   3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3, 3), 
+    nudge_y = c(0,0,0,0,0,0,0,0,0, #poor communication and outreach
+                0.5, #model abuse
+                1, #lack of political permanance
+                1.5, #indirect socioeconomic consequences
+                1.8, #target species is a prey specialist
+                2, #resource availability
+                2, #climate change adding uncertainty
+                2, #data transparency
+                2, #need for multi-species management
+                2, #distinct habitat preference
+                2, #fine scale management
+                1.5, #management scale system needs
+                2, #management scale aligns
+                0.8, #feasibility
+                0,0,0,0,0,0,0,0,0,0,0,0,0,0, 0), 
+    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05),
+    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +
+
+  xlim(0.89, 3.6) +
+  ylim(-1, 100)+
+  labs(y = "Percent of all codes (%)", x = "") +
+  theme_minimal()+
+  theme(axis.text.y = element_text(size = 14), 
+        axis.title.y = element_text(size = 16), 
+        legend.position = "none", 
+        axis.text.x = element_blank(), 
+        panel.grid.major = element_blank())+
+  scale_fill_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))+
+  scale_color_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))
+
+```
 

### 2024-06-28 reports/lit_codes_explore.qmd
sankey and sunburst plots

--- 2024-06-01 reports/lit_codes_explore.qmd
@@
 
+![Bridges](C:/Users/nazar/OneDrive/Documents/R/Projects/DOM Review/figures/bridges_old.png){fig-align = "center" width = 70%}
+
 ### Barriers
@@
 ```
+
+![Barriers](C:/Users/nazar/OneDrive/Documents/R/Projects/DOM Review/figures/barriers_old.png){fig-align = "center" width = 70%}
+
 :::
+
+### Sankey diagram of code heirarchies 
+Here, each of the codes and their subcodes are presented. The presented percentages represent totals across all codes.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 15
+#| fig-height: 15
+
+sankey_df <- read.csv(here("data/sankey_freq.csv"))
+
+sankey_df$code_cat <- factor(sankey_df$code_cat, levels = c("Data barrier", "Ecological barrier", "Social barrier", "Data bridge", "Ecological bridge", "Social bridge"))
+
+sankey_df <- sankey_df %>%
+mutate(sum_codes = sum(total), 
+      perc_codes = (total/sum_codes)*100, 
+      round_perc = round(perc_codes, 0))
+
+ggplot(data = sankey_df,
+       aes(axis1 = fct_reorder(bridge_barr, -perc_codes), axis2 = fct_reorder(code_cat, -perc_codes), axis3 = fct_reorder(code_name, -perc_codes), y = perc_codes)) +
+  geom_alluvium(aes(fill = code_cat, color = code_cat), size = 1.5, alpha = 0.8, width = 0.05) +
+  geom_stratum(size = 1.5, color = "grey60", 
+              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
+  geom_text(stat = "stratum", 
+    aes(label = after_stat(stratum)),
+    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
+    size = c(7,7,5,5,5,5,5,5,4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4), 
+    nudge_y = c(0,0,0,0,0,0,0,0,0, #poor communication and outreach
+                0.5, #model abuse
+                1, #lack of political permanance
+                1.5, #indirect socioeconomic consequences
+                1.8, #target species is a prey specialist
+                2, #resource availability
+                2, #climate change adding uncertainty
+                2, #data transparency
+                2, #need for multi-species management
+                2, #distinct habitat preference
+                2, #fine scale management
+                1.5, #management scale system needs
+                2, #management scale aligns
+                0.8, #feasibility
+                0,0,0,0,0,0,0,0,0,0,0,0,0,0, 0), 
+    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05),
+    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +
+
+  xlim(0.89, 3.6) +
+  ylim(-1, 100)+
+  labs(y = "Percent of all codes (%)", x = "") +
+  theme_minimal()+
+  theme(axis.text.y = element_text(size = 14), 
+        axis.title.y = element_text(size = 16), 
+        legend.position = "none", 
+        axis.text.x = element_blank(), 
+        panel.grid.major = element_blank())+
+  scale_fill_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))+
+  scale_color_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))
+
+```
 
@@
 :::
+
+### Code metadata vs. code frequencies
 

### 2024-10-09 reports/lit_codes_explore.qmd
revised fig doc

@@
 
-In June 2022 a systematic search was completed using Web of Science to identify articles that mentioned factors that either contributed to "successful" implementation of dynamic ocean management (DOM), hereafter referred to as a "bridge".
-Literature that discussed factors that would need to be addressed or considered prior to effective implementation of dynamic management approaches or tools were also included, hereafter referred to as a "barrier".
-In this systematic review, we coded bridges and barriers that were related to DOM voluntary programs and/or enforced regulations, as well as those that were related to tool development (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.
+In June 2022, a systematic search was completed using Web of Science to identify articles that discussed dynamic ocean management (DOM).
+Specifically, articles were selected if they described factors contributing to the “success” of DOM, also termed here as a “bridge”, or that noted factors that should be addressed prior to using DOM approaches or support tools, also termed here as “barriers”.
+In this systematic review, we coded bridges and barriers that were related to implemented or recommended DOM voluntary programs and/or enforced regulations, as well as those that were related to tool development (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.
 
@@
 
-A search was completed in Web of Science for each combination of primary and secondary terms.
-Works from the primary (i.e., peer reviewed journals) and grey (e.g., theses, book chapters) were included, and this initial search resulted in 1,351 articles.
-The abstracts for each of these documents were scanned for relevance, and the inclusion of the terms 'dynamic' or 'adaptive' management were confirmed.
+AA search was completed for each combination of primary and secondary terms (Table 1).
+Works from the primary (i.e., peer-reviewed journals) and grey literature (e.g., theses, book chapters) were included, and this initial search resulted in 1,351 articles.
+The abstracts for each of these documents were skimmed for relevance, and the inclusion of the terms ‘dynamic’ or ‘adaptive’ management were confirmed.
 From this cut, a remaining 127 articles were saved.
-An additional search through the NOAA Institutional Repository and Federal Register was also completed.
+An additional search using the NOAA Institutional Repository and Federal Register was also completed.
 Here, documents such as policy reports and planning documents were selected.
 This search resulted in 795 documents.
-The abstracts or content summaries for each of these documents were scanned for relevance, and 10 articles were saved for a full read through to determine final inclusion.
-Inclusion and exclusion criteria for both queries are described here:
+The abstracts or content summaries for each of these documents were skimmed for relevance, and 10 articles were saved for a full read-through to determine final inclusion.
+Articles were excluded if DOM was mentioned or recommended, but there was no discussion as to why.
+Articles were also excluded if they discussed changes or updates to environmental data sources or remote sensing tools used to develop models supporting DOM, but DOM approaches were not specifically applied, recommended, or reviewed.
+Specific inclusion and exclusion criteria are described here:
 
@@
 
-The final list of included works consisted of 137 documents.
-Each of these were fully read by two reviewers and went through a final pass for determining inclusion.
-Additional snowball sampling was performed to identify and include articles that were referenced in this list.
-The abstracts of these referenced articles were read and their inclusion was determined.
-Lastly, the search ended in August 2023 and articles or documents published after this date were not included in this review.
-The final list of works analyzed for the review included 110 articles (i.e., primary literature, student theses, policy reports, textbook chapters).
+The 137 articles were read by two reviewers and went through a final pass for determining inclusion.
+Articles that were referenced that seemed to discuss relevant topics were skimmed and their inclusion was determined.
+The search ended in August 2023, and articles or documents published after this date were not included in this review.
+The final list of works analyzed for the review included 109 articles (i.e., primary literature, student theses, policy reports, and textbook chapters).
 
@@
 
-Two reviewers went through each of the 110 articles to identify pieces of text that were related to DOM bridges that were linked to the approaches success or were used as justification when systems recommended its adoption.
-The reviewers also identified the barriers that hindered the efficacy of DOM or must be considered prior to it's broader application.
-Through this effort, 19 "bridge" and 10 "barrier" categories were determined.
-For both the bridge and barrier code categories, three larger "umbrella" groups were established: species, social, and data.
-A table of the full list of codes/themes are depicted here.
-Please note that this is a draft of codes, and thus we are happy to modify the terminology throughout the study review process.
+Two reviewers went through each of the 109 articles to identify text that was related to DOM bridges that were linked to the approach's success or were used as justification as to why DOM would be a good fit for that system/conservation problem.
+The reviewers also identified the barriers that hindered the efficacy of DOM or must be considered prior to its application.
+Through this effort, 19 “bridge” and 10 “barrier” categories were determined in the literature.
+“Bridge” and “barrier” factors were organized into four broader theme groups: ecological, social, data, or regulation/program.
+A table of the full list of codes/themes from the literature are depicted here.
+Please note that this is a draft of codes and that the sunburst diagram needs to be revised.
+I am also happy to modify the code/factor terminology throughout the study review process.
 
@@
 
-![Bridges](C:/Users/nazar/OneDrive/Documents/R/Projects/DOM Review/figures/bridges_old.png){fig-align = "center" width = 70%}
+![](images/bridges_old.png){fig-align="center" width="70%"}
 
@@
 
-![Barriers](C:/Users/nazar/OneDrive/Documents/R/Projects/DOM Review/figures/barriers_old.png){fig-align = "center" width = 70%}
-
+![](images/barriers_old.png){fig-align="center" width="70%"}
 :::
@@
 ### Sankey diagram of code heirarchies
-Here, each of the codes and their subcodes are presented. The presented percentages represent totals across all codes.
+
+Here, each of the codes and their subcodes are presented.
+The presented percentages represent totals across all codes and codes closer to the top are codes that make up higher percentages of identified codes.
 
@@
 This first section represents general information about the articles selected for this review (e.g., study location, fisheries or shipping channels involved, species for which the tool or management program was established for).
+Most of these plots may instead go in the supplemental materials or aid in interpretation.
 
@@
 eco_sum$code_cat <- factor(as.factor(eco_sum$code_cat), levels = c("Ecological bridge", "Ecological barrier"))
-my_labs2 <- c("0", "30")
+my_labs2 <- c("0", "30", "50", "75", "100")
 
@@
   scale_x_continuous(position = "top", 
-                     limits = c(0,0.35),
+                     limits = c(0,1.1),
                      expand = c(0,0), 
-                     breaks = c(0, 0.3),
+                     breaks = c(0, 0.3, 0.5, 0.75, 1),
                      labels = my_labs2)+
@@
 ::: panel-tabset
-
 #### All code relations
+
 This is a heatmap of all code relationships within articles. The number of co-ocurrences represents the number of times two codes co-occurered together in the same article.
@@
 #### Most frequent code relations
+
 This heatmap represents the same data set as the last figure, but only includes co-occurrence values greater than or equal to 6, which is the 75% quantile of the co-occurrence totals.
@@
 theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]))+
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]), 
+      panel.background = element_blank())+
 geom_text(aes(label = total))+
@@
 #### Data code relations
+
 This is a look at the data bridge and barrier code relations.
@@
 #### Ecological code relations
+
 This is a look at the ecological bridge and barrier code relations.
@@
 #### Social code relations
+
 This is a look at the social bridge and barrier code relations.

### 2025-01-14 reports/lit_codes_explore.qmd
update quarto

@@
 ---
-title: "literature coding explore"
+title: "DOM bridges and barriers: systematic review and end-user survey"
 author: "Emily Nazario | UC Santa Cruz | enazario'@'ucsc.edu"
@@
 fontcolor: "#134f5c"
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-code_freq <- read.csv(here("data/code_freq_032224.csv"))
-codes_vars <- read.csv(here("data/code_w_vars_032224.csv"))
-keywords <- read.csv(here("data/keywords_032224.csv"))
-occur_all <- read.csv(here("data/code_configs_all_032224.csv"))
-occur_br <- read.csv(here("data/code_configs_bridges_032224.csv"))
-occur_ba <- read.csv(here("data/code_configs_barriers_032224.csv"))
+#lit data
+code_freq <- read.csv(here("data/code_freq.csv"))
+codes_vars <- read.csv(here("data/code_w_vars.csv"))
+keywords <- read.csv(here("data/keywords.csv"))
 code_rel <- read.csv(here("data/code_rel.csv"))
+
+#survey data
+code_vars_s <- read.csv(here("data/surveys/draft_vars.csv"))
 
@@
 
+# Literature Review
+
 ## Selecting the literature that was included in this systematic review
 
-In June 2022, a systematic search was completed using Web of Science to identify articles that discussed dynamic ocean management (DOM).
-Specifically, articles were selected if they described factors contributing to the “success” of DOM, also termed here as a “bridge”, or that noted factors that should be addressed prior to using DOM approaches or support tools, also termed here as “barriers”.
+In September 2024, a systematic search was completed using Web of Science to identify articles that discussed dynamic ocean management (DOM).
+Articles or documents published after this date were not included in this review.
+Articles were selected if they described factors contributing to the “success” of DOM, also termed here as a “bridge”, or that noted factors that should be addressed prior to using DOM approaches or support tools, also termed here as a “barrier”.
 In this systematic review, we coded bridges and barriers that were related to implemented or recommended DOM voluntary programs and/or enforced regulations, as well as those that were related to tool development (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.
 
-During the initial search, the following table of primary and secondary terms were used:
-
-| Primary term               | Secondary term |
-|----------------------------|----------------|
-| Dynamic ocean management   | Success        |
-| Dynamic spatial management | Efficiency     |
-| Adaptive management        | Obstacles      |
-| Dynamic closures           | Limitations    |
-| Bycatch reduction          |                |
-| Habitat preference         |                |
-
-AA search was completed for each combination of primary and secondary terms (Table 1).
-Works from the primary (i.e., peer-reviewed journals) and grey literature (e.g., theses, book chapters) were included, and this initial search resulted in 1,351 articles.
-The abstracts for each of these documents were skimmed for relevance, and the inclusion of the terms ‘dynamic’ or ‘adaptive’ management were confirmed.
-From this cut, a remaining 127 articles were saved.
-An additional search using the NOAA Institutional Repository and Federal Register was also completed.
+During the initial search, the following table of terms were used.
+The "NEAR/5" operator was used to refine the search and ensure each of the terms in a given character string were found within one word of each other:
+
+| Search term                |
+|----------------------------|
+| Dynamic ocean management   |
+| Dynamic spatial management |
+| Adaptive ocean management  |
+| Dynamic ocean closures     |
+
+: **Table 1.** List of terms used in the Web of Science search. Where spaces are found between words in a search term, the "NEAR/5" operator was added.
+
+Works from the primary (i.e., peer-reviewed journals) and grey literature (e.g., theses, book chapters) were included, and this initial search resulted in 292 articles.
+Abstracts were skimmed for relevance, and a total of 141 articles were saved for further inspection An additional search using the NOAA Federal Register was also completed.
 Here, documents such as policy reports and planning documents were selected.
-This search resulted in 795 documents.
-The abstracts or content summaries for each of these documents were skimmed for relevance, and 10 articles were saved for a full read-through to determine final inclusion.
+This search resulted in 483 documents.
+The abstracts or content summaries for each of these documents were skimmed for relevance, and an additional 10 documents were saved for a full read through.
 Articles were excluded if DOM was mentioned or recommended, but there was no discussion as to why.
@@
 
-The 137 articles were read by two reviewers and went through a final pass for determining inclusion.
+The 151 articles were read by two reviewers and went through a final pass for determining inclusion.
 Articles that were referenced that seemed to discuss relevant topics were skimmed and their inclusion was determined.
-The search ended in August 2023, and articles or documents published after this date were not included in this review.
-The final list of works analyzed for the review included 109 articles (i.e., primary literature, student theses, policy reports, and textbook chapters).
+The final list of works analyzed for the review included 118 articles (i.e., primary literature, student theses, policy reports, and textbook chapters).
 
@@
 
-Two reviewers went through each of the 109 articles to identify text that was related to DOM bridges that were linked to the approach's success or were used as justification as to why DOM would be a good fit for that system/conservation problem.
+Two reviewers went through each of the 118 articles to identify text that was related to DOM bridges that were linked to the approach's success or were used as justification as to why DOM would be a good fit for that system/conservation problem.
 The reviewers also identified the barriers that hindered the efficacy of DOM or must be considered prior to its application.
 Through this effort, 19 “bridge” and 10 “barrier” categories were determined in the literature.
-“Bridge” and “barrier” factors were organized into four broader theme groups: ecological, social, data, or regulation/program.
+“Bridge” and “barrier” factors were organized into four broader theme groups: ecological, social, and data.
 A table of the full list of codes/themes from the literature are depicted here.
-Please note that this is a draft of codes and that the sunburst diagram needs to be revised.
+Please note that this is a draft of codes and that the sunburst diagrams need to be revised.
 I am also happy to modify the code/factor terminology throughout the study review process.
@@
 
-### Sankey diagram of code heirarchies
+### Sankey diagram of literature code heirarchies
 
@@
 
+#calc props for sankey_df csv (fine scale codes are raw totals from code_freq file)
+sum_codes <- sum(code_freq$total) #710 codes
+code_freq %>% 
+  group_by(bridge_barr) %>% 
+  summarise(totals = sum(total))
+
+code_freq %>% 
+  group_by(code_cat) %>% 
+  summarise(totals = sum(total))
+
+#load sankey df
 sankey_df <- read.csv(here("data/sankey_freq.csv"))
 
-sankey_df$code_cat <- factor(sankey_df$code_cat, levels = c("Data barrier", "Ecological barrier", "Social barrier", "Data bridge", "Ecological bridge", "Social bridge"))
+sankey_df$code_cat <- factor(sankey_df$code_cat, levels = c("Ecological barrier", "Data barrier", "Social barrier", "Data bridge", "Ecological bridge", "Social bridge"))
 
@@
   geom_stratum(size = 1.5, color = "grey60", 
-              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
+              width = c(1/12,1/12,1/3,1/3,1/3,1/3,1/3,1/3,1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18, 1/18)) +
   geom_text(stat = "stratum", 
     aes(label = after_stat(stratum)),
-    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
-    size = c(7,7,5,5,5,5,5,5,4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4), 
+    angle = c(90,90,0,0,0,0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
+    size = c(7,7,5,5,5,5,5,5,4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4), 
     nudge_y = c(0,0,0,0,0,0,0,0,0, #poor communication and outreach
@@
                 0.8, #feasibility
-                0,0,0,0,0,0,0,0,0,0,0,0,0,0, 0), 
-    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05),
-    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +
+                0,0,0,0,0,0,0,0,0,0,0,0,0,0), 
+    nudge_x = c(-0.01,-0.01,0,0,0,0,0,0,0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05,   0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05, 0.05),
+    hjust = c(0.5, 0.5, 0.5,0.5,0.5,0.5,0.5,0.5,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)) +
 
@@
 
-## Visualizing the bridges and barrier codes from the literature
+## Visualizing the literature bridges and barrier codes
 
@@
 This first section represents general information about the articles selected for this review (e.g., study location, fisheries or shipping channels involved, species for which the tool or management program was established for).
-Most of these plots may instead go in the supplemental materials or aid in interpretation.
+Most of these plots may instead go in the supplemental materials or aid with interpretation.
 
 ### Study information
+
+#### Article categories
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 4
+
+codes_vars$lit_type <- factor(codes_vars$lit_type , levels = c("NOAA Rule", "NMFS Notice", "Book chapter", "Thesis", "Methods", "Perspective", "Review", "Study"))
+
+ggplot(codes_vars, aes(x = "", fill = lit_type))+
+  geom_bar(position = "fill")+
+  xlab("")+
+  theme_minimal()+
+  labs(fill = "Literature category")+
+  ylab("Percentage of articles")+
+  coord_flip()+
+  scale_y_continuous(labels = scales::percent)+
+  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 8))
+
+```
 
@@
 
-### Code metadata vs. code frequencies
-
-### Code appearance frequencies across articles (n = 109)
-
-The proportions reported in these figures represent the percent of papers included these broader code categories or individual codes.
+### Code appearance frequencies across articles (n = 118)
+
+The proportions reported in these figures represent the percent of papers that mentioned a subcode within these broader code categories at least once.
 
@@
 code_freq_new <- codes_vars2 %>%
-  mutate(br_pos = as.numeric(if_any(c(33:48, 59:61), ~. == 1)), 
+  mutate(br_pos = as.numeric(if_any(c(33:48, 59:60), ~. == 1)), 
          ba_pos = as.numeric(if_any(49:58, ~. == 1)),
-         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Abiotic data availability", "Resource use data availability"), ~.
+         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Environmental data availability", "Resource use data availability"), ~.
 == 1)),
-         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~.
+         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~.
 == 1)),
@@
 == 1)),
-         ba_dat = as.numeric(if_any(c("Implementation costs", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~.
+         ba_dat = as.numeric(if_any(c("Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~.
 == 1)),
          ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
-         ba_soc = as.numeric(if_any(c("Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~.
+         ba_soc = as.numeric(if_any(c("Implementation costs", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~.
 == 1)))
@@
 brba_sum <- code_freq_new %>%
-  summarise(n_br = sum(br_pos), freq_br = n_br/109,
-            n_ba = sum(ba_pos), freq_ba = n_ba/109,
-            n_br_e = sum(br_eco), freq_br_e = n_br_e/109,
-            n_br_d = sum(br_dat), freq_br_d = n_br_d/109,
-            n_br_s = sum(br_soc), freq_br_s = n_br_s/109,
-            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/109,
-            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/109,
-            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/109) %>%
+  summarise(n_br = sum(br_pos), freq_br = n_br/118,
+            n_ba = sum(ba_pos), freq_ba = n_ba/118,
+            n_br_e = sum(br_eco), freq_br_e = n_br_e/118,
+            n_br_d = sum(br_dat), freq_br_d = n_br_d/118,
+            n_br_s = sum(br_soc), freq_br_s = n_br_s/118,
+            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/118,
+            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/118,
+            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/118) %>%
   gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16)) %>%
@@
 data_freq <- codes_vars2 %>%
-  subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Abiotic data availability", "Resource use data availability","Implementation costs", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
-  gather(category, pres_abs, 1:11) %>%
-  mutate(br_ba = ifelse(category == "Implementation costs" | category == "Gaps and inaccuracy" | category == "Management scales do not align with system needs" | category == "Model abuse" | category == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
+  subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
+  gather(category, pres_abs, 1:10) %>%
+  mutate(br_ba = ifelse(category == "Gaps and inaccuracy" | category == "Management scales do not align with system needs" | category == "Model abuse" | category == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
   group_by(category, br_ba)  %>%
   summarise(n = sum(pres_abs), 
-            freq = (n/109)) %>%
+            freq = (n/118)) %>%
   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
@@
 ecol_freq <- codes_vars2 %>%
-  subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
-  gather(category, pres_abs, 1:9) %>%
+  subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
+  gather(category, pres_abs, 1:8) %>%
   mutate(br_ba = ifelse(category == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
@@
   summarise(n = sum(pres_abs), 
-            freq = (n/109)) %>%
+            freq = (n/118)) %>%
   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
@@
 soc_freq <- codes_vars2 %>%
-  subset(select = c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation")) %>%
+  subset(select = c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
   gather(category, pres_abs, 1:9) %>%
-  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Implementation costs", "Social barrier", "Social bridge")) %>%
   group_by(category, br_ba)  %>%
   summarise(n = sum(pres_abs), 
-            freq = (n/109)) %>%
+            freq = (n/118)) %>%
   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
@@
   summarise(value = total/n_total) %>%
-  mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Gaps and inaccuracy" | code_name == "Management scales do not align with system needs" | code_name == "Model abuse" | code_name == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
+  mutate(code_cat = ifelse(code_name == "Gaps and inaccuracy" | code_name == "Management scales do not align with system needs" | code_name == "Model abuse" | code_name == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
   mutate(percent_label = scales::percent(value, accuracy = 2))
@@
   summarise(value = total/n_total) %>%
-  mutate(code_cat = ifelse(code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+  mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
   mutate(percent_label = scales::percent(value, accuracy = 2))
@@
 
+Could consider including code co-occurrence themes as a heat map, or could list the most frequent pairings as a table.
+
 ::: panel-tabset
@@
 :::
+
+# Surveys
+
+## Survey respondants
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 4
+#| fig-align: center
+
+code_vars_s <- code_vars_s %>% mutate(survey = as.factor(survey))
+code_vars_s$survey <- factor(code_vars_s$survey , levels = c("Shad surveys","WhaleWatch TMMC surveys","WhaleWatch surveys", "Yellowtail surveys"))
+
+ggplot(code_vars_s, aes(x = "", fill = survey))+
+  geom_bar(position = "fill")+
+  xlab("")+
+  theme_minimal()+
+  labs(fill = "Respondant position")+
+  ylab("Percentage of survey respondants")+
+  coord_flip()+
+  scale_y_continuous(labels = scales::percent)+
+  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 4), labels = c("River Herring Avoidance Program", "Whale Safe Southern California", "Whale Safe Northern California", "Yellowtail Flounder Avoidance Program"))
+
+```
+
+## Respondant positions
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 4
+#| fig-align: center
+
+code_vars_pos <- code_vars_s %>%
+  pivot_longer(
+    cols = "pos1":"pos5", 
+    names_to = "pos_number",
+    values_to = "pos_type"
+  )
+
+code_vars_pos <- code_vars_pos %>% mutate(pos_type = as.factor(pos_type))
+code_vars_pos$pos_type <- factor(code_vars_pos$pos_type , levels = c("Vessel operator", "Crew", "Vessel captain", "Fleet manager", "Fishery manager", "Commercial fisherman", "Fishery advisory board member", "Vessel owner", "Fishery scientist", "NA"))
+
+ggplot(code_vars_pos, aes(x = "", fill = pos_type))+
+  geom_bar(position = "fill")+
+  xlab("")+
+  theme_minimal()+
+  labs(fill = "Respondant position")+
+  ylab("Percentage of respondants")+
+  coord_flip()+
+  scale_y_continuous(labels = scales::percent)+
+  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 10))
+
+```
+
+## Respondant experience
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 5
+#| fig-height: 5
+#| fig-align: center
+
+ggplot(code_vars_s, aes(x = "", pos_num))+
+  geom_violin(size = 1.5, color = "steelblue4")+
+  geom_jitter(height = 0, width = 0.1, size = 3, color = "steelblue4", alpha = 0.5)+
+  theme_minimal() + 
+  xlab("")+
+  ylab("Number of years in position")+
+  theme(axis.title = element_text(size = 16), 
+        axis.text = element_text(size = 14, color = "black"))
+
+```

### 2025-01-14 scripts/map.R

@@ -1,0 +1,42 @@
+#load libraries
+library(tidyverse)
+library(here)
+library(tidyquant)
+library(mapdata)
+library(ggpubr)
+
+#world map
+state <- map_data("state")
+
+#get US map
+EC <- ggplot(data=state, aes(x=long, y=lat, group = group)) + 
+  geom_polygon(color = "black", fill = "grey75") + 
+  theme_tq()+
+  coord_fixed(xlim = c(-80, -66), ylim = c(32, 50), expand = TRUE)+
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(), 
+        #axis.text = element_text(size = 14, color = "black"), 
+        #axis.title = element_text(size= 16, color = "black"), 
+        panel.background = element_rect(fill='transparent'),
+        plot.background = element_rect(fill='transparent', color=NA), 
+        axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        panel.border = element_rect(color = "grey60"))
+
+
+WC <- ggplot(data=state, aes(x=long, y=lat, group = group)) + 
+  geom_polygon(color = "black", fill = "grey75") + 
+  theme_tq()+
+  coord_fixed(xlim = c(-126, -113), ylim = c(32, 49), expand = TRUE)+
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(), 
+        #axis.text = element_text(size = 14, color = "black"), 
+        #axis.title = element_text(size= 16, color = "black"), 
+        panel.background = element_rect(fill='transparent'),
+        plot.background = element_rect(fill='transparent', color=NA), 
+        axis.text = element_blank(), 
+        axis.title = element_blank(), 
+        panel.border = element_rect(color = "grey60"))
+
+ggarrange(WC, EC)
+ggsave(here("figures/maps.png"), width = 8, height = 6, units = c("in"))

### 2025-06-07 reports/lit_codes_explore.qmd
surveys figs start

@@
 #survey data
-code_vars_s <- read.csv(here("data/surveys/draft_vars.csv"))
+code_vars_s <- read.csv(here("data/surveys/code_w_vars.csv"))
+code_freq_s <- read.csv(here("data/surveys/code_freq.csv"))
 
@@
 
+ggsave(here("figures/sankey_tp.svg"), height = 10, width = 10, units = c("in"))
+
 ```
@@
   scale_y_continuous(labels = scales::percent)+
-  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 8))
+  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 8))+
+  theme(panel.background = element_rect(fill='transparent'),
+         plot.background = element_rect(fill='transparent', color=NA),
+         panel.grid.major = element_blank(),
+         panel.grid.minor = element_blank(),
+         legend.background = element_rect(fill='transparent'),
+         legend.box.background = element_rect(fill='transparent'))
+#ggsave(here("figures/lit_cat.svg"), width = 8, height = 4, units = c("in"))
 
@@
 ```
+
+## Code appearance frequencies across surveys (n = 21)
+
+The proportions reported in these figures represent the percent of surveys that mentioned a subcode within these broader code categories at least once.
+
+::: panel-tabset
+#### Broader categories
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+codes_vars_s2 = code_vars_s
+colnames(codes_vars_s2) <- gsub(x = colnames(codes_vars_s2), pattern = "\\.", replacement = " ")
+
+  #calculate frequency of bridges vs. barriers being mentioned in surveys
+code_freq_new_s <- codes_vars_s2 %>%
+  mutate(br_pos = as.numeric(if_any(38:61, ~. == 1)), 
+         ba_pos = as.numeric(if_any(21:37, ~. == 1)),
+         br_reg = as.numeric(if_any(c(38:45), ~. ==1)),
+         br_soc = as.numeric(if_any(c(46:55), ~. == 1)), 
+         br_dat = as.numeric(if_any(c(56:57), ~. == 1)), 
+         br_eco = as.numeric(if_any(c(58:61), ~. == 1)), 
+         ba_reg = as.numeric(if_any(c(21:23), ~. == 1)),
+         ba_dat = as.numeric(if_any(c(24:26), ~. == 1)), 
+         ba_eco = as.numeric(if_any(c(27), ~. == 1)), 
+         ba_soc = as.numeric(if_any(c(28:37), ~. == 1)))
+
+brba_sum_s <- code_freq_new_s %>%
+  summarise(n_br = sum(br_pos), freq_br = n_br/21,
+            n_ba = sum(ba_pos), freq_ba = n_ba/21,
+            n_br_e = sum(br_eco), freq_br_e = n_br_e/21,
+            n_br_d = sum(br_dat), freq_br_d = n_br_d/21,
+            n_br_s = sum(br_soc), freq_br_s = n_br_s/21,
+            n_br_r = sum(br_reg), freq_br_r = n_br_r/21,
+            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/21,
+            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/21,
+            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/21, 
+            n_ba_r = sum(ba_reg), freq_ba_r = n_ba_r/21) %>%  
+  gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16, 18, 20)) %>%
+  subset(select = c(br_ba, value)) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 1), 
+         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s" | br_ba == "freq_ba_r", value, -value),
+         code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
+                              if_else(br_ba %in% c("freq_ba_e", "freq_br_e"), "Ecological bridge or barrier", 
+                              if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
+                              if_else(br_ba %in% c("freq_ba_r", "freq_br_r"), "Regulatory bridge or barrier",
+                              if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA))))),
+         code_brba = if_else(br_ba %in% c("freq_br", "freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r"), "bridge", "barrier"),
+         alpha_brba = if_else(br_ba %in% c("freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r", "freq_ba_e", "freq_ba_s", "freq_ba_d", "freq_ba_r"), "alpha", "no_alpha")) %>%
+  group_by(code_level)
+
+brba_sum_s$code_level <- factor(brba_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier", "Regulatory bridge or barrier","Social bridge or barrier", "Overall bridge or barrier"))
+brba_sum_s$code_brba <- factor(brba_sum_s$code_brba, levels = c("bridge", "barrier"))
+
+ggplot(brba_sum_s, aes(x = code_level, 
+             y = percent,
+             fill = code_brba)) +
+  geom_col(width = 0.7) +
+  geom_text(aes(label = percent_label),
+            position = position_stack(vjust = 0.65),
+            color = "black", 
+            size = 5) +
+  ylim(-1,1)+
+  coord_flip() +
+  scale_x_discrete() +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.x =element_blank(),
+        axis.text.y = element_text(size = 20, color = "black"),
+        panel.grid = element_blank(),
+        legend.position = c(-0.21, 0.99),
+        legend.text = element_text(size = 16, color = "black"),
+        strip.text.y.right = element_text(angle = 0, size = 16)) +
+  geom_hline(yintercept = 0.0, linewidth = 1) + 
+  labs(fill = "")+ 
+  guides(fill = guide_legend(nrow = 1))
+```
+
+#### Data frequencies
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+# data_freq_s <- codes_vars_s2 %>%
+#   subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
+#   gather(category, pres_abs, 1:10) %>%
+#   mutate(br_ba = ifelse(category == "Gaps and inaccuracy" | category == "Management scales do not align with system needs" | category == "Model abuse" | category == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
+#   group_by(category, br_ba)  %>%
+#   summarise(n = sum(pres_abs), 
+#             freq = (n/118)) %>%
+#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
+#   group_by(category)
+# 
+# my_labs <- c("0", "25", "50", "75")
+# data_freq$br_ba <- factor(as.factor(data_freq$br_ba), levels = c("Data bridge", "Data barrier"))
+# 
+# data_bar <- ggplot(data_freq) +
+#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
+#   scale_x_continuous(position = "top", 
+#                      limits = c(0,0.9),
+#                      expand = c(0,0), 
+#                      breaks = c(0, 0.25, 0.5, 0.75),
+#                      labels = my_labs)+
+#   scale_y_discrete(expand = expansion(add = c(0,0))) +
+#   tidyquant::theme_tq() +
+#   theme(
+#     # Set background color to white
+#     panel.background = element_rect(fill = "white"),
+#     # Set the color and the width of the grid lines for the horizontal axis
+#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+#     # Remove tick marks by setting their length to 0
+#     axis.ticks.length = unit(0, "mm"),
+#     # Remove the title for both axes
+#     axis.title = element_blank(),
+#     # Only left line of the vertical axis is painted in black
+#     axis.line.y.left = element_line(color = "black"),
+#     # But customize labels for the horizontal axis
+#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+#     legend.position = "none", 
+#     strip.text = element_text(size = 16)) + 
+#   geom_text(aes(x = freq, y = category, label = percent_label),
+#     hjust = 0,
+#     nudge_x = -0.0001,
+#     colour = "black",
+#     family = "Econ Sans Cnd",
+#     size = 6)+
+#   labs(subtitle = "Percent of sum from all articles (%)") + 
+#   theme(plot.subtitle = element_text(
+#       family = "Econ Sans Cnd",
+#       size = 20)
+#   ) + 
+#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+#   facet_wrap(~br_ba, scales = "free", nrow = 2)
+# data_bar
+
+```
+
+#### Ecological frequencies
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+# ecol_freq <- codes_vars2 %>%
+#   subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
+#   gather(category, pres_abs, 1:8) %>%
+#   mutate(br_ba = ifelse(category == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
+#   group_by(category, br_ba)  %>%
+#   summarise(n = sum(pres_abs), 
+#             freq = (n/118)) %>%
+#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
+#   group_by(category)
+# 
+# ecol_freq$category <- replace(ecol_freq$category, ecol_freq$category == "Fine scale management appropriate for target species", "Fine-scale management appropriate for target species")
+# ecol_freq$br_ba <- factor(as.factor(ecol_freq$br_ba), levels = c("Ecological bridge", "Ecological barrier"))
+# 
+# ecol_bar <- ggplot(ecol_freq) +
+#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
+#   scale_x_continuous(position = "top", 
+#                      limits = c(0,0.9),
+#                      expand = c(0,0), 
+#                      breaks = c(0, 0.25, 0.5, 0.75),
+#                      labels = my_labs)+
+#   scale_y_discrete(expand = expansion(add = c(0,0))) +
+#   tidyquant::theme_tq() +
+#   theme(
+#     # Set background color to white
+#     panel.background = element_rect(fill = "white"),
+#     # Set the color and the width of the grid lines for the horizontal axis
+#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+#     # Remove tick marks by setting their length to 0
+#     axis.ticks.length = unit(0, "mm"),
+#     # Remove the title for both axes
+#     axis.title = element_blank(),
+#     # Only left line of the vertical axis is painted in black
+#     axis.line.y.left = element_line(color = "black"),
+#     # But customize labels for the horizontal axis
+#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+#     legend.position = "none", 
+#     strip.text = element_text(size = 16)) + 
+#   geom_text(aes(x = freq, y = category, label = percent_label),
+#     hjust = 0,
+#     nudge_x = -0.0001,
+#     colour = "black",
+#     family = "Econ Sans Cnd",
+#     size = 6)+
+#   labs(subtitle = "Percent of sum from all articles (%)") + 
+#   theme(plot.subtitle = element_text(
+#       family = "Econ Sans Cnd",
+#       size = 20)
+#   ) + 
+#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+#   facet_wrap(~br_ba, scales = "free", nrow = 2)
+# 
+# ecol_bar
+
+```
+
+#### Social frequencies
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
+# soc_freq <- codes_vars2 %>%
+#   subset(select = c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
+#   gather(category, pres_abs, 1:9) %>%
+#   mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Implementation costs", "Social barrier", "Social bridge")) %>%
+#   group_by(category, br_ba)  %>%
+#   summarise(n = sum(pres_abs), 
+#             freq = (n/118)) %>%
+#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
+#   group_by(category)
+# 
+# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
+# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing regulation and management institutions", "Pre-existing regulation and management institutions")
+# soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
+# 
+# 
+# soc_bar <- ggplot(soc_freq) +
+#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
+#   scale_x_continuous(position = "top", 
+#                      limits = c(0,0.9),
+#                      expand = c(0,0), 
+#                      breaks = c(0, 0.25, 0.5, 0.75),
+#                      labels = my_labs)+
+#   scale_y_discrete(expand = expansion(add = c(0,0))) +
+#   tidyquant::theme_tq() +
+#   theme(
+#     # Set background color to white
+#     panel.background = element_rect(fill = "white"),
+#     # Set the color and the width of the grid lines for the horizontal axis
+#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+#     # Remove tick marks by setting their length to 0
+#     axis.ticks.length = unit(0, "mm"),
+#     # Remove the title for both axes
+#     axis.title = element_blank(),
+#     # Only left line of the vertical axis is painted in black
+#     axis.line.y.left = element_line(color = "black"),
+#     # But customize labels for the horizontal axis
+#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+#     legend.position = "none", 
+#     strip.text = element_text(size = 16)) + 
+#   geom_text(aes(x = freq, y = category, label = percent_label),
+#     hjust = 0,
+#     nudge_x = -0.0001,
+#     colour = "black",
+#     family = "Econ Sans Cnd",
+#     size = 6)+
+#   labs(subtitle = "Percent of sum from all articles (%)") + 
+#   theme(plot.subtitle = element_text(
+#       family = "Econ Sans Cnd",
+#       size = 20)
+#   ) + 
+#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+#   facet_wrap(~br_ba, scales = "free", nrow = 2)
+# soc_bar
+
+```
+
+### Regulatory frequencies
+
+:::
+
+## Code appearance frequencies within code categories
+
+Here, I have plotted the same information as the previous section, but as a percentage of the overall bridges and barriers groupings.
+For example, data bridges make up 37% of all bridge codes.
+The same pattern holds for the other sub-panels.
+For example, on the ecological page, abiotic indicators account for 22% of all ecological bridge codes.
+
+::: panel-tabset
+#### Broader categories
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+code_sum_s <- code_freq_s %>%
+  group_by(bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(code_cat) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  summarise(value = n_subtotal/n_total) %>%
+  rename("br_ba" = code_cat) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 1), 
+         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Regulation barrier", value, -value),
+         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+                              if_else(br_ba %in% c("Regulation barrier", "Regulation bridge"), "Regulatory bridge or barrier",
+                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA)))), 
+         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Regulation bridge"), "bridge", "barrier")) %>%
+  group_by(code_level) %>%
+  distinct()
+
+code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier","Regulatory bridge or barrier", "Social bridge or barrier"))
+code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))
+
+ggplot(code_sum_s, aes(x = code_level, 
+             y = percent,
+             fill = code_brba)) +
+  geom_col(width = 0.7) +
+  geom_text(aes(label = percent_label),
+            position = position_stack(vjust = 0.65),
+            color = "black", 
+            size = 5) +
+  ylim(-0.7,0.7)+
+  coord_flip() +
+  scale_x_discrete() +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.x =element_blank(),
+        axis.text.y = element_text(size = 20, color = "black"),
+        panel.grid = element_blank(),
+        legend.position = c(-0.17, 0.99),
+        legend.text = element_text(size = 16, color = "black"),
+        strip.text.y.right = element_text(angle = 0, size = 16)) +
+  geom_hline(yintercept = 0.0, linewidth = 1) + 
+  labs(fill = "")+ 
+  guides(fill = guide_legend(nrow = 1))
+
+```
+
+#### Data codes
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+# data_freq <- code_freq %>%
+#   filter(code_cat == "Data bridge" | code_cat == "Data barrier")
+# 
+# data_sum <- data_freq %>%
+#   group_by(bridge_barr) %>%
+#   mutate(n_total = sum(total)) %>%
+#   ungroup() %>%
+#   group_by(code_name) %>% 
+#   summarise(value = total/n_total) %>%
+#   mutate(code_cat = ifelse(code_name == "Gaps and inaccuracy" | code_name == "Management scales do not align with system needs" | code_name == "Model abuse" | code_name == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
+#   mutate(percent_label = scales::percent(value, accuracy = 2))
+#   
+# my_labs <- c("0", "25", "50", "75")
+# data_sum$code_cat <- factor(as.factor(data_sum$code_cat), levels = c("Data bridge", "Data barrier"))
+# 
+# ggplot(data_sum) +
+#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
+#   scale_x_continuous(position = "top", 
+#                      limits = c(0,0.9),
+#                      expand = c(0,0), 
+#                      breaks = c(0, 0.25, 0.5, 0.75),
+#                      labels = my_labs)+
+#   scale_y_discrete(expand = expansion(add = c(0,0))) +
+#   tidyquant::theme_tq() +
+#   theme(
+#     # Set background color to white
+#     panel.background = element_rect(fill = "white"),
+#     # Set the color and the width of the grid lines for the horizontal axis
+#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+#     # Remove tick marks by setting their length to 0
+#     axis.ticks.length = unit(0, "mm"),
+#     # Remove the title for both axes
+#     axis.title = element_blank(),
+#     # Only left line of the vertical axis is painted in black
+#     axis.line.y.left = element_line(color = "black"),
+#     # But customize labels for the horizontal axis
+#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+#     legend.position = "none", 
+#     strip.text = element_text(size = 16)) + 
+#   geom_text(aes(x = value, y = code_name, label = percent_label),
+#     hjust = 0,
+#     nudge_x = -0.0001,
+#     colour = "black",
+#     family = "Econ Sans Cnd",
+#     size = 6)+
+#   labs(subtitle = "Percent from all data bridges or barriers (%)") + 
+#   theme(plot.subtitle = element_text(
+#       family = "Econ Sans Cnd",
+#       size = 20)
+#   ) + 
+#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+#   facet_wrap(~code_cat, scales = "free", nrow = 2)
+
+```
+
+#### Ecological codes
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+# eco_freq <- code_freq %>%
+#   filter(code_cat == "Ecological bridge" | code_cat == "Ecological barrier")
+# 
+# eco_sum <- eco_freq %>%
+#   group_by(bridge_barr) %>%
+#   mutate(n_total = sum(total)) %>%
+#   ungroup() %>%
+#   group_by(code_name) %>% 
+#   summarise(value = total/n_total) %>%
+#   mutate(code_cat = ifelse(code_name == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
+#   mutate(percent_label = scales::percent(value, accuracy = 2))
+#   
+# eco_sum$code_cat <- factor(as.factor(eco_sum$code_cat), levels = c("Ecological bridge", "Ecological barrier"))
+# my_labs2 <- c("0", "30", "50", "75", "100")
+# 
+# ggplot(eco_sum) +
+#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
+#   scale_x_continuous(position = "top", 
+#                      limits = c(0,1.1),
+#                      expand = c(0,0), 
+#                      breaks = c(0, 0.3, 0.5, 0.75, 1),
+#                      labels = my_labs2)+
+#   scale_y_discrete(expand = expansion(add = c(0,0))) +
+#   tidyquant::theme_tq() +
+#   theme(
+#     # Set background color to white
+#     panel.background = element_rect(fill = "white"),
+#     # Set the color and the width of the grid lines for the horizontal axis
+#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+#     # Remove tick marks by setting their length to 0
+#     axis.ticks.length = unit(0, "mm"),
+#     # Remove the title for both axes
+#     axis.title = element_blank(),
+#     # Only left line of the vertical axis is painted in black
+#     axis.line.y.left = element_line(color = "black"),
+#     # But customize labels for the horizontal axis
+#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+#     legend.position = "none", 
+#     strip.text = element_text(size = 16)) + 
+#   geom_text(aes(x = value, y = code_name, label = percent_label),
+#     hjust = 0,
+#     nudge_x = -0.0001,
+#     colour = "black",
+#     family = "Econ Sans Cnd",
+#     size = 6)+
+#   labs(subtitle = "Percent from all ecological bridges or barriers (%)") + 
+#   theme(plot.subtitle = element_text(
+#       family = "Econ Sans Cnd",
+#       size = 20)
+#   ) + 
+#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+#   facet_wrap(~code_cat, scales = "free", nrow = 2)
+
+```
+
+#### Social codes
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-align: center
+
+# soc_freq <- code_freq %>%
+#   filter(code_cat == "Social bridge" | code_cat == "Social barrier")
+# 
+# soc_sum <- soc_freq %>%
+#   group_by(bridge_barr) %>%
+#   mutate(n_total = sum(total)) %>%
+#   ungroup() %>%
+#   group_by(code_name) %>% 
+#   summarise(value = total/n_total) %>%
+#   mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+#   mutate(percent_label = scales::percent(value, accuracy = 2))
+#   
+# soc_sum$code_cat <- factor(as.factor(soc_sum$code_cat), levels = c("Social bridge", "Social barrier"))
+# my_labs2 <- c("0", "30")
+# 
+# ggplot(soc_sum) +
+#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
+#   scale_x_continuous(position = "top", 
+#                      limits = c(0,1),
+#                      expand = c(0,0), 
+#                      breaks = c(0,0.25, 0.5, 0.75),
+#                      labels = my_labs)+
+#   scale_y_discrete(expand = expansion(add = c(0,0))) +
+#   tidyquant::theme_tq() +
+#   theme(
+#     # Set background color to white
+#     panel.background = element_rect(fill = "white"),
+#     # Set the color and the width of the grid lines for the horizontal axis
+#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+#     # Remove tick marks by setting their length to 0
+#     axis.ticks.length = unit(0, "mm"),
+#     # Remove the title for both axes
+#     axis.title = element_blank(),
+#     # Only left line of the vertical axis is painted in black
+#     axis.line.y.left = element_line(color = "black"),
+#     # But customize labels for the horizontal axis
+#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
+#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
+#     legend.position = "none", 
+#     strip.text = element_text(size = 16)) + 
+#   geom_text(aes(x = value, y = code_name, label = percent_label),
+#     hjust = 0,
+#     nudge_x = -0.0001,
+#     colour = "black",
+#     family = "Econ Sans Cnd",
+#     size = 6)+
+#   labs(subtitle = "Percent from all social bridges or barriers (%)") + 
+#   theme(plot.subtitle = element_text(
+#       family = "Econ Sans Cnd",
+#       size = 20)
+#   ) + 
+#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
+#   facet_wrap(~code_cat, scales = "free", nrow = 2)
+
+```
+
+### Regulatory codes
+:::

### 2025-08-21 reports/lit_codes_explore.qmd
updated bridge themes

@@
 #lit data
-code_freq <- read.csv(here("data/code_freq.csv"))
-codes_vars <- read.csv(here("data/code_w_vars.csv"))
+code_freq <- read.csv(here("data/code_freq_lit.csv"))
+codes_vars <- read.csv(here("data/code_w_vars_lit.csv"))
 keywords <- read.csv(here("data/keywords.csv"))
@@
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Known Species Nat History", "Life history information available for target species")
-code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Distinct Habitat between target and non-target species", "Distinct habitat preferences among species in system")
 
@@
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Scale appropriate for system", "Management scale aligns with system needs")
-code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Open-Access Public Data", "Data transparency and accessibility")
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Availability for species", "Target species data availability")
@@
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Open Communication or Co-Mngmt in place", "Co-management and communication")
-code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Adoption Interests & Incentives", "Adoption incentives for end users")
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Pre-existing regulation & management institutions", "Pre-existing regulation and management institutions")
@@
          ba_pos = as.numeric(if_any(49:58, ~. == 1)),
-         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Environmental data availability", "Resource use data availability"), ~.
+         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability"), ~.
 == 1)),
-         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~.
+         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~.
 == 1)),
-         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication"), ~.
-== 1)),
+         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication"), ~. == 1)), 
          ba_dat = as.numeric(if_any(c("Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~.
@@
 data_freq <- codes_vars2 %>%
-  subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
+  subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
   gather(category, pres_abs, 1:10) %>%
@@
 ecol_freq <- codes_vars2 %>%
-  subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
+  subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
   gather(category, pres_abs, 1:8) %>%
@@
 soc_freq <- codes_vars2 %>%
-  subset(select = c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
+  subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
   gather(category, pres_abs, 1:9) %>%
@@
 soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
-soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing regulation and management institutions", "Pre-existing regulation and management institutions")
+soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing conditions", "Pre-existing conditions")
 soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
@@
 code_rel_melt2$code2[code_rel_melt2$code2 == "Fine scale management appropriate for target species"] <- "Fine-scale management appropriate for target species"
-code_rel_melt2$code2[code_rel_melt2$code2 == "Pre existing regulation and management institutions"] <- "Pre-existing regulation and management institutions"
+code_rel_melt2$code2[code_rel_melt2$code2 == "Pre existing conditions"] <- "Pre-existing conditions"
 code_rel_melt2$code2[code_rel_melt2$code2 == "Co management and communication"] <- "Co-management and communication"
@@
 
-code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Pre existing regulation and management institutions"] <- "Pre-existing regulation and management institutions"
+code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Pre existing conditions"] <- "Pre-existing conditions"
 code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Co management and communication"] <- "Co-management and communication"
@@
 # data_freq_s <- codes_vars_s2 %>%
-#   subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
+#   subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
 #   gather(category, pres_abs, 1:10) %>%
@@
 # ecol_freq <- codes_vars2 %>%
-#   subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
+#   subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
 #   gather(category, pres_abs, 1:8) %>%
@@
 # soc_freq <- codes_vars2 %>%
-#   subset(select = c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
+#   subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
 #   gather(category, pres_abs, 1:9) %>%
@@
 # soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
-# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing regulation and management institutions", "Pre-existing regulation and management institutions")
+# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing conditions", "Pre-existing conditions")
 # soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
@@
 
-### Regulatory frequencies
+#### Regulatory frequencies
 
@@
 
-### Regulatory codes
+#### Regulatory codes
 :::

### 2025-08-22 reports/lit_codes_explore.qmd
updated barriers

@@
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Unintended consequences", "Indirect socioeconomic consequences")
-code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Political permanence", "Lack of political administration permanence")
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Communication & Distribution", "Poor communication and outreach")
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Recipient participation", "Poor program implementation")
-code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Cost", "Implementation costs")
 
@@
                 0.5, #model abuse
-                1, #lack of political permanance
+                1, #Discontinuity
                 1.5, #indirect socioeconomic consequences
@@
          ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
-         ba_soc = as.numeric(if_any(c("Implementation costs", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~.
-== 1)))
+         ba_soc = as.numeric(if_any(c("Cost", "Indirect socioeconomic consequences", "Discontinuity", "Poor communication and outreach", "Poor program implementation"), ~. == 1)))
 
@@
 soc_freq <- codes_vars2 %>%
-  subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
+  subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Discontinuity", "Cost", "Poor communication and outreach", "Poor program implementation")) %>%
   gather(category, pres_abs, 1:9) %>%
-  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Implementation costs", "Social barrier", "Social bridge")) %>%
+  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Discontinuity" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Cost", "Social barrier", "Social bridge")) %>%
   group_by(category, br_ba)  %>%
@@
   summarise(value = total/n_total) %>%
-  mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+  mutate(code_cat = ifelse(code_name == "Cost" | code_name == "Indirect socioeconomic consequences" | code_name == "Discontinuity" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
   mutate(percent_label = scales::percent(value, accuracy = 2))
@@
 # soc_freq <- codes_vars2 %>%
-#   subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Lack of political administration permanence", "Implementation costs", "Poor communication and outreach", "Poor program implementation")) %>%
+#   subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Discontinuity", "Cost", "Poor communication and outreach", "Poor program implementation")) %>%
 #   gather(category, pres_abs, 1:9) %>%
-#   mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Lack of political administration permanence" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Implementation costs", "Social barrier", "Social bridge")) %>%
+#   mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Discontinuity" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Cost", "Social barrier", "Social bridge")) %>%
 #   group_by(category, br_ba)  %>%
@@
 #   summarise(value = total/n_total) %>%
-#   mutate(code_cat = ifelse(code_name == "Implementation costs" | code_name == "Indirect socioeconomic consequences" | code_name == "Lack of political administration permanence" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
+#   mutate(code_cat = ifelse(code_name == "Cost" | code_name == "Indirect socioeconomic consequences" | code_name == "Discontinuity" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
 #   mutate(percent_label = scales::percent(value, accuracy = 2))

### 2025-09-20 reports/draft_results.qmd
res fig 2

--- 2025-08-22 reports/lit_codes_explore.qmd
@@
 ---
-title: "DOM bridges and barriers: systematic review and end-user survey"
+title: "DOM bridges and barriers: systematic review and survey"
 author: "Emily Nazario | UC Santa Cruz | enazario'@'ucsc.edu"
@@
 
-# Literature Review
+## Questions
 
-## Selecting the literature that was included in this systematic review
+**Which themes overlap between the literature and surveys?**
 
-In September 2024, a systematic search was completed using Web of Science to identify articles that discussed dynamic ocean management (DOM).
-Articles or documents published after this date were not included in this review.
-Articles were selected if they described factors contributing to the “success” of DOM, also termed here as a “bridge”, or that noted factors that should be addressed prior to using DOM approaches or support tools, also termed here as a “barrier”.
-In this systematic review, we coded bridges and barriers that were related to implemented or recommended DOM voluntary programs and/or enforced regulations, as well as those that were related to tool development (e.g., species spatial modeling tools such as EcoCast) that support dynamic management approaches.
+**Which themes only appear in the literature? Which themes are unique to the surveys?**
 
-During the initial search, the following table of terms were used.
-The "NEAR/5" operator was used to refine the search and ensure each of the terms in a given character string were found within one word of each other:
+**How do themes vary between fishing vs. shipping contexts?**
 
-| Search term                |
-|----------------------------|
-| Dynamic ocean management   |
-| Dynamic spatial management |
-| Adaptive ocean management  |
-| Dynamic ocean closures     |
+**How do themes vary with positionality of the respondent (surveys only)?**
 
-: **Table 1.** List of terms used in the Web of Science search. Where spaces are found between words in a search term, the "NEAR/5" operator was added.
+## Result 1: Bridges and barriers according to review and survey
 
-Works from the primary (i.e., peer-reviewed journals) and grey literature (e.g., theses, book chapters) were included, and this initial search resulted in 292 articles.
-Abstracts were skimmed for relevance, and a total of 141 articles were saved for further inspection An additional search using the NOAA Federal Register was also completed.
-Here, documents such as policy reports and planning documents were selected.
-This search resulted in 483 documents.
-The abstracts or content summaries for each of these documents were skimmed for relevance, and an additional 10 documents were saved for a full read through.
-Articles were excluded if DOM was mentioned or recommended, but there was no discussion as to why.
-Articles were also excluded if they discussed changes or updates to environmental data sources or remote sensing tools used to develop models supporting DOM, but DOM approaches were not specifically applied, recommended, or reviewed.
-Specific inclusion and exclusion criteria are described here:
+Here I've presented three options for presenting the themes and sub-themes identified in the review and surveys.
+I'd love feedback on which option or combination of options best visualize the codes!
+Depending on your feedback, I'll then spend time cleaning up the best option.
 
-| Inclusion | Exclusion |
-|------------------------------------|:-----------------------------------|
-| All cases where adaptive or near-real time forms of management or tools that support this form of management were discussed, even if the specific term 'Dynamic Ocean Management' was not explicitly used.
-| The term 'DOM' was mentioned, or even recommended, but there was no discussion as to why (e.g.
-SDM studies that suggest DOM applications as a next step for their model) |
-| All cases where near real-time SDM tools or fleet-wide communication to avoid negative species interactions.
-| Articles that involved changes or updates to environmental data stores or remote sensing tools used for developing SDM tools to support DOM, but DOM was not specifically applied, recommended, or reviewed.
-|
+### Option 1 - Sankey diagram
 
-The 151 articles were read by two reviewers and went through a final pass for determining inclusion.
-Articles that were referenced that seemed to discuss relevant topics were skimmed and their inclusion was determined.
-The final list of works analyzed for the review included 118 articles (i.e., primary literature, student theses, policy reports, and textbook chapters).
-
-## Coding the bridges and barriers as identified in the literature
-
-Two reviewers went through each of the 118 articles to identify text that was related to DOM bridges that were linked to the approach's success or were used as justification as to why DOM would be a good fit for that system/conservation problem.
-The reviewers also identified the barriers that hindered the efficacy of DOM or must be considered prior to its application.
-Through this effort, 19 “bridge” and 10 “barrier” categories were determined in the literature.
-“Bridge” and “barrier” factors were organized into four broader theme groups: ecological, social, and data.
-A table of the full list of codes/themes from the literature are depicted here.
-Please note that this is a draft of codes and that the sunburst diagrams need to be revised.
-I am also happy to modify the code/factor terminology throughout the study review process.
-
-::: panel-tabset
-### Bridges
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-
-bri_codes <- code_freq %>% 
-  filter(bridge_barr == "Bridge") %>% 
-  subset(select = -c(total, bridge_barr))
-
-colnames(bri_codes) <- c("Code category", "Code label")
-
-bri_codes %>%
-  kbl() %>%
-  kable_styling()
-```
-
-![](images/bridges_old.png){fig-align="center" width="70%"}
-
-### Barriers
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-
-bar_codes <- code_freq %>% 
-  filter(bridge_barr == "Barrier") %>% 
-  subset(select = -c(total, bridge_barr))
-
-colnames(bar_codes) <- c("Code category", "Code label")
-
-bar_codes %>%
-  kbl() %>%
-  kable_styling()
-```
-
-![](images/barriers_old.png){fig-align="center" width="70%"}
-:::
-
-### Sankey diagram of literature code heirarchies
-
-Here, each of the codes and their subcodes are presented.
-The presented percentages represent totals across all codes and codes closer to the top are codes that make up higher percentages of identified codes.
+Plot below only presents the review themes and sub-themes. If this is the best way to communicate the codes, I will add a diagram visualizing the survey codes.
 
@@
   ylim(-1, 100)+
-  labs(y = "Percent of all codes (%)", x = "") +
+  labs(y = "Proportion of all codes (%)", x = "") +
   theme_minimal()+
@@
   scale_color_manual(values = c("#F48136", "#F46036", "#F44336", "#CFE2F3", "#C5E0B4", "#45818E"))
-
-ggsave(here("figures/sankey_tp.svg"), height = 10, width = 10, units = c("in"))
-
 ```
 
-## Visualizing the literature bridges and barrier codes
+### Option 2 - Sunburst figure
 
-Below is a first attempt at how to visualize some of the data collected from this review.
-This first section represents general information about the articles selected for this review (e.g., study location, fisheries or shipping channels involved, species for which the tool or management program was established for).
-Most of these plots may instead go in the supplemental materials or aid with interpretation.
+Plots below are from an old draft of the review themes and sub-themes. If this is the nicest way to plot the codes, I will update the diagram and generate one for the survey themes as well.
 
-### Study information
+![](images/bridges_old.png){fig-align="center" width="70%"}
 
-#### Article categories
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 7
-#| fig-height: 4
+![](images/barriers_old.png){fig-align="center" width="70%"}
 
-codes_vars$lit_type <- factor(codes_vars$lit_type , levels = c("NOAA Rule", "NMFS Notice", "Book chapter", "Thesis", "Methods", "Perspective", "Review", "Study"))
-
-ggplot(codes_vars, aes(x = "", fill = lit_type))+
-  geom_bar(position = "fill")+
-  xlab("")+
-  theme_minimal()+
-  labs(fill = "Literature category")+
-  ylab("Percentage of articles")+
-  coord_flip()+
-  scale_y_continuous(labels = scales::percent)+
-  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 8))+
-  theme(panel.background = element_rect(fill='transparent'),
-         plot.background = element_rect(fill='transparent', color=NA),
-         panel.grid.major = element_blank(),
-         panel.grid.minor = element_blank(),
-         legend.background = element_rect(fill='transparent'),
-         legend.box.background = element_rect(fill='transparent'))
-#ggsave(here("figures/lit_cat.svg"), width = 8, height = 4, units = c("in"))
-
-```
+### Option 3 - Table
 
 ::: panel-tabset
-#### Study regions
+
+#### Review: Bridge themes
 
@@
 #| warning: false
-#| fig-width: 7
-#| fig-height: 7
 
-codes_vars$broad_location <- as.factor(codes_vars$broad_location)
-codes_LU <- codes_vars[!duplicated(codes_vars$Lit_unit), ]
-reg_s <- codes_LU %>%
-  group_by(broad_location) %>%
-  filter(broad_location != "NA" & broad_location != "Europe and United States") %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  mutate(perc = count/sum(count)*100)
+bri_codes <- code_freq %>% 
+  filter(bridge_barr == "Bridge") %>% 
+  subset(select = -c(total, bridge_barr))
 
-reg_bar <- ggplot(reg_s) +
-  geom_bar(aes(x = perc, y = reorder(broad_location, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     expand = c(0,0), 
-                     limits = c(0, 48))+
-  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # Remove labels from the vertical axis
-    axis.text.y = element_blank(),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
-  geom_text(aes(x = perc, y = broad_location, label = broad_location),
-    hjust = 0,
-    nudge_x = 0.3,
-    colour = "dodgerblue4",
-    family = "Econ Sans Cnd",
-    size = 3.5)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 13)
-  )
+colnames(bri_codes) <- c("Code category", "Code label")
 
-reg_bar
+bri_codes %>%
+  kbl() %>%
+  kable_styling()
 ```
 
-#### Study fisheries and shipping channels
+#### Review: Barrier themes
 
@@
 #| warning: false
-#| fig-height: 10
-#| fig-width: 10
-fsh_shp <- codes_LU %>%
-  gather(col, fsh_shp, fishery_or_channel1:fishery_or_channel4) %>%
-  subset(select = fsh_shp)
 
-fsh_shp_s <- fsh_shp %>%
-  group_by(fsh_shp) %>%
-  filter(fsh_shp != "NA") %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  mutate(perc = count/sum(count)*100)
+bar_codes <- code_freq %>% 
+  filter(bridge_barr == "Barrier") %>% 
+  subset(select = -c(total, bridge_barr))
 
-fsh_shp_bar <- ggplot(fsh_shp_s) +
-  geom_bar(aes(x = perc, y = reorder(fsh_shp, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     expand = c(0,0), 
-                     limits = c(0, 14))+
-  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # Remove labels from the vertical axis
-    axis.text.y = element_blank(),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 15)) + 
-  geom_text(aes(x = perc, y = fsh_shp, label = fsh_shp),
-    hjust = 0,
-    nudge_x = 0.3,
-    colour = "dodgerblue4",
-    family = "Econ Sans Cnd",
-    size = 5)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 16)
-  )
+colnames(bar_codes) <- c("Code category", "Code label")
 
-fsh_shp_bar
+bar_codes %>%
+  kbl() %>%
+  kable_styling()
 ```
 
-#### Study taxa
+#### Survey: Bridge themes
 
@@
 #| warning: false
-#| fig-width: 7
-#| fig-height: 7
 
-species <- codes_LU %>%
-  gather(col, taxa, focal_taxa1:focal_taxa3) %>%
-  subset(select = taxa)
+bri_codes_s <- code_freq_s %>% 
+  filter(bridge_barr == "Bridge") %>% 
+  subset(select = -c(total, bridge_barr))
 
-spp_s <- species %>%
-  group_by(taxa) %>%
-  filter(taxa != "NA" & taxa != "Marine mammals") %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  mutate(perc = count/sum(count)*100)
+colnames(bri_codes_s) <- c("Code category", "Code label")
 
-taxa_bar <- ggplot(spp_s) +
-  geom_bar(aes(x = perc, y = reorder(taxa, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     expand = c(0,0), 
-                     limits = c(0, 23))+
-  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # Remove labels from the vertical axis
-    axis.text.y = element_blank(),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
-  geom_text(aes(x = perc, y = taxa, label = taxa),
-    hjust = 0,
-    nudge_x = 0.3,
-    colour = "dodgerblue4",
-    family = "Econ Sans Cnd",
-    size = 3.5)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 13)
-  )
+bri_codes_s %>%
+  kbl() %>%
+  kable_styling()
 
-taxa_bar
 ```
 
-#### Study species
+#### Survey: Barrier themes
 
@@
 #| warning: false
-#| fig-width: 7
-#| fig-height: 12
 
-species_Gs <- codes_LU %>%
-  gather(col, sp_name, species1:species16) %>%
-  subset(select = sp_name)
+bar_codes_s <- code_freq_s %>% 
+  filter(bridge_barr == "Barrier") %>% 
+  subset(select = -c(total, bridge_barr))
 
-spp_Gs_s <- species_Gs %>%
-  group_by(sp_name) %>%
-  filter(sp_name != "NA") %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  mutate(perc = count/sum(count)*100)
+colnames(bar_codes_s) <- c("Code category", "Code label")
 
-sp_bar <- ggplot(spp_Gs_s) +
-  geom_bar(aes(x = perc, y = reorder(sp_name, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     expand = c(0,0), 
-                     limits = c(0, 23))+
-  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # Remove labels from the vertical axis
-    axis.text.y = element_blank(),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
-  geom_text(aes(x = perc, y = sp_name, label = sp_name),
-    hjust = 0,
-    nudge_x = 0.3,
-    colour = "dodgerblue4",
-    family = "Econ Sans Cnd",
-    size = 3.5)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 13)
-  )
+bar_codes_s %>%
+  kbl() %>%
+  kable_styling()
 
-sp_bar
-```
-
-#### Conservation problem being addressed
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 7
-#| fig-height: 7
-
-consv <- codes_LU %>%
-  gather(col, consv_topic, reason1:reason3) %>%
-  subset(select = consv_topic)
-
-consv_s <- consv %>%
-  group_by(consv_topic) %>%
-  filter(consv_topic != "NA") %>%
-  summarise(count = n()) %>%
-  ungroup() %>%
-  mutate(perc = count/sum(count)*100)
-
-consv_bar <- ggplot(consv_s) +
-  geom_bar(aes(x = perc, y = reorder(consv_topic, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     expand = c(0,0), 
-                     limits = c(0, 18))+
-  scale_y_discrete(expand = expansion(add = c(0,0))) + 
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # Remove labels from the vertical axis
-    axis.text.y = element_blank(),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
-  geom_text(aes(x = perc, y = consv_topic, label = consv_topic),
-    hjust = 0,
-    nudge_x = 0.3,
-    colour = "dodgerblue4",
-    family = "Econ Sans Cnd",
-    size = 3.5)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 13)
-  )
-
-consv_bar
 ```
@@
 
-### Code appearance frequencies across articles (n = 118)
-
-The proportions reported in these figures represent the percent of papers that mentioned a subcode within these broader code categories at least once.
+## Result 2: Frequencies according to review and survey
 
 ::: panel-tabset
-#### Broader categories
+
+### Literature 
+Code appearance frequencies across articles (n = 118).
+The proportions reported in these figures represent the percent of papers that mentioned a subcode within these broader code categories at least once.
 
@@
 #| fig-align: center
-
-codes_vars2 = codes_vars
-colnames(codes_vars2) <- gsub(x = colnames(codes_vars2), pattern = "\\.", replacement = " ")
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-code_freq_new <- codes_vars2 %>%
-  mutate(br_pos = as.numeric(if_any(c(33:48, 59:60), ~. == 1)), 
-         ba_pos = as.numeric(if_any(49:58, ~. == 1)),
-         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability"), ~.
-== 1)),
-         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~.
-== 1)),
-         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication"), ~. == 1)), 
-         ba_dat = as.numeric(if_any(c("Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~.
-== 1)),
-         ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
-         ba_soc = as.numeric(if_any(c("Cost", "Indirect socioeconomic consequences", "Discontinuity", "Poor communication and outreach", "Poor program implementation"), ~. == 1)))
-
-brba_sum <- code_freq_new %>%
-  summarise(n_br = sum(br_pos), freq_br = n_br/118,
-            n_ba = sum(ba_pos), freq_ba = n_ba/118,
-            n_br_e = sum(br_eco), freq_br_e = n_br_e/118,
-            n_br_d = sum(br_dat), freq_br_d = n_br_d/118,
-            n_br_s = sum(br_soc), freq_br_s = n_br_s/118,
-            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/118,
-            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/118,
-            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/118) %>%
-  gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16)) %>%
-  subset(select = c(br_ba, value)) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 1), 
-         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s", value, -value),
-         code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
-                              if_else(br_ba %in% c("freq_ba_e", "freq_br_e"), "Ecological bridge or barrier", 
-                              if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA)))),
-         code_brba = if_else(br_ba %in% c("freq_br", "freq_br_e", "freq_br_s", "freq_br_d"), "bridge", "barrier"),
-         alpha_brba = if_else(br_ba %in% c("freq_br_e", "freq_br_s", "freq_br_d", "freq_ba_e", "freq_ba_s", "freq_ba_d"), "alpha", "no_alpha")) %>%
-  group_by(code_level)
-
-brba_sum$code_level <- factor(brba_sum$code_level, levels = c("Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier", "Overall bridge or barrier"))
-brba_sum$code_brba <- factor(brba_sum$code_brba, levels = c("bridge", "barrier"))
-
-ggplot(brba_sum, aes(x = code_level, 
-             y = percent,
-             fill = code_brba)) +
-  geom_col(width = 0.7) +
-  geom_text(aes(label = percent_label),
-            position = position_stack(vjust = 0.65),
-            color = "black", 
-            size = 5) +
-  ylim(-1,1)+
-  coord_flip() +
-  scale_x_discrete() +
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
-  theme_minimal() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        axis.text.x =element_blank(),
-        axis.text.y = element_text(size = 20, color = "black"),
-        panel.grid = element_blank(),
-        legend.position = c(-0.21, 0.99),
-        legend.text = element_text(size = 16, color = "black"),
-        strip.text.y.right = element_text(angle = 0, size = 16)) +
-  geom_hline(yintercept = 0.0, linewidth = 1) + 
-  labs(fill = "")+ 
-  guides(fill = guide_legend(nrow = 1))
-```
-
-#### Data frequencies
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-data_freq <- codes_vars2 %>%
-  subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
-  gather(category, pres_abs, 1:10) %>%
-  mutate(br_ba = ifelse(category == "Gaps and inaccuracy" | category == "Management scales do not align with system needs" | category == "Model abuse" | category == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
-  group_by(category, br_ba)  %>%
-  summarise(n = sum(pres_abs), 
-            freq = (n/118)) %>%
-  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
-  group_by(category)
-
-my_labs <- c("0", "25", "50", "75")
-data_freq$br_ba <- factor(as.factor(data_freq$br_ba), levels = c("Data bridge", "Data barrier"))
-
-data_bar <- ggplot(data_freq) +
-  geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     limits = c(0,0.9),
-                     expand = c(0,0), 
-                     breaks = c(0, 0.25, 0.5, 0.75),
-                     labels = my_labs)+
-  scale_y_discrete(expand = expansion(add = c(0,0))) +
-  tidyquant::theme_tq() +
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-    legend.position = "none", 
-    strip.text = element_text(size = 16)) + 
-  geom_text(aes(x = freq, y = category, label = percent_label),
-    hjust = 0,
-    nudge_x = -0.0001,
-    colour = "black",
-    family = "Econ Sans Cnd",
-    size = 6)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 20)
-  ) + 
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-  facet_wrap(~br_ba, scales = "free", nrow = 2)
-data_bar
-
-```
-
-#### Ecological frequencies
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-ecol_freq <- codes_vars2 %>%
-  subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
-  gather(category, pres_abs, 1:8) %>%
-  mutate(br_ba = ifelse(category == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
-  group_by(category, br_ba)  %>%
-  summarise(n = sum(pres_abs), 
-            freq = (n/118)) %>%
-  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
-  group_by(category)
-
-ecol_freq$category <- replace(ecol_freq$category, ecol_freq$category == "Fine scale management appropriate for target species", "Fine-scale management appropriate for target species")
-ecol_freq$br_ba <- factor(as.factor(ecol_freq$br_ba), levels = c("Ecological bridge", "Ecological barrier"))
-
-ecol_bar <- ggplot(ecol_freq) +
-  geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     limits = c(0,0.9),
-                     expand = c(0,0), 
-                     breaks = c(0, 0.25, 0.5, 0.75),
-                     labels = my_labs)+
-  scale_y_discrete(expand = expansion(add = c(0,0))) +
-  tidyquant::theme_tq() +
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-    legend.position = "none", 
-    strip.text = element_text(size = 16)) + 
-  geom_text(aes(x = freq, y = category, label = percent_label),
-    hjust = 0,
-    nudge_x = -0.0001,
-    colour = "black",
-    family = "Econ Sans Cnd",
-    size = 6)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 20)
-  ) + 
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-  facet_wrap(~br_ba, scales = "free", nrow = 2)
-
-ecol_bar
-
-```
-
-#### Social frequencies
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-soc_freq <- codes_vars2 %>%
-  subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Discontinuity", "Cost", "Poor communication and outreach", "Poor program implementation")) %>%
-  gather(category, pres_abs, 1:9) %>%
-  mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Discontinuity" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Cost", "Social barrier", "Social bridge")) %>%
-  group_by(category, br_ba)  %>%
-  summarise(n = sum(pres_abs), 
-            freq = (n/118)) %>%
-  mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
-  group_by(category)
-
-soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
-soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing conditions", "Pre-existing conditions")
-soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
-
-soc_bar <- ggplot(soc_freq) +
-  geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     limits = c(0,0.9),
-                     expand = c(0,0), 
-                     breaks = c(0, 0.25, 0.5, 0.75),
-                     labels = my_labs)+
-  scale_y_discrete(expand = expansion(add = c(0,0))) +
-  tidyquant::theme_tq() +
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-    legend.position = "none", 
-    strip.text = element_text(size = 16)) + 
-  geom_text(aes(x = freq, y = category, label = percent_label),
-    hjust = 0,
-    nudge_x = -0.0001,
-    colour = "black",
-    family = "Econ Sans Cnd",
-    size = 6)+
-  labs(subtitle = "Percent of sum from all articles (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 20)
-  ) + 
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-  facet_wrap(~br_ba, scales = "free", nrow = 2)
-soc_bar
-
-```
-:::
-
-### Code appearance frequencies within code categories
-
-Here, I have plotted the same information as the previous section, but as a percentage of the overall bridges and barriers groupings.
-For example, data bridges make up 37% of all bridge codes.
-The same pattern holds for the other sub-panels.
-For example, on the ecological page, abiotic indicators account for 22% of all ecological bridge codes.
-
-::: panel-tabset
-#### Broader categories
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 10
-#| fig-height: 7
-#| fig-align: center
+#| include: FALSE
 
@@
 
+#ggsave("figures/ms_figs/all_freq/all_freq.png", width = 8, height = 5, units = ("in"))
 ```
-
-#### Data codes
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-data_freq <- code_freq %>%
-  filter(code_cat == "Data bridge" | code_cat == "Data barrier")
-
-data_sum <- data_freq %>%
-  group_by(bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(code_name) %>% 
-  summarise(value = total/n_total) %>%
-  mutate(code_cat = ifelse(code_name == "Gaps and inaccuracy" | code_name == "Management scales do not align with system needs" | code_name == "Model abuse" | code_name == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 2))
-
-my_labs <- c("0", "25", "50", "75")
-data_sum$code_cat <- factor(as.factor(data_sum$code_cat), levels = c("Data bridge", "Data barrier"))
-
-ggplot(data_sum) +
-  geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     limits = c(0,0.9),
-                     expand = c(0,0), 
-                     breaks = c(0, 0.25, 0.5, 0.75),
-                     labels = my_labs)+
-  scale_y_discrete(expand = expansion(add = c(0,0))) +
-  tidyquant::theme_tq() +
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-    legend.position = "none", 
-    strip.text = element_text(size = 16)) + 
-  geom_text(aes(x = value, y = code_name, label = percent_label),
-    hjust = 0,
-    nudge_x = -0.0001,
-    colour = "black",
-    family = "Econ Sans Cnd",
-    size = 6)+
-  labs(subtitle = "Percent from all data bridges or barriers (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 20)
-  ) + 
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-  facet_wrap(~code_cat, scales = "free", nrow = 2)
-
-```
-
-#### Ecological codes
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-eco_freq <- code_freq %>%
-  filter(code_cat == "Ecological bridge" | code_cat == "Ecological barrier")
-
-eco_sum <- eco_freq %>%
-  group_by(bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(code_name) %>% 
-  summarise(value = total/n_total) %>%
-  mutate(code_cat = ifelse(code_name == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 2))
-
-eco_sum$code_cat <- factor(as.factor(eco_sum$code_cat), levels = c("Ecological bridge", "Ecological barrier"))
-my_labs2 <- c("0", "30", "50", "75", "100")
-
-ggplot(eco_sum) +
-  geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     limits = c(0,1.1),
-                     expand = c(0,0), 
-                     breaks = c(0, 0.3, 0.5, 0.75, 1),
-                     labels = my_labs2)+
-  scale_y_discrete(expand = expansion(add = c(0,0))) +
-  tidyquant::theme_tq() +
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-    legend.position = "none", 
-    strip.text = element_text(size = 16)) + 
-  geom_text(aes(x = value, y = code_name, label = percent_label),
-    hjust = 0,
-    nudge_x = -0.0001,
-    colour = "black",
-    family = "Econ Sans Cnd",
-    size = 6)+
-  labs(subtitle = "Percent from all ecological bridges or barriers (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 20)
-  ) + 
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-  facet_wrap(~code_cat, scales = "free", nrow = 2)
-
-```
-
-#### Social codes
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-soc_freq <- code_freq %>%
-  filter(code_cat == "Social bridge" | code_cat == "Social barrier")
-
-soc_sum <- soc_freq %>%
-  group_by(bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(code_name) %>% 
-  summarise(value = total/n_total) %>%
-  mutate(code_cat = ifelse(code_name == "Cost" | code_name == "Indirect socioeconomic consequences" | code_name == "Discontinuity" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 2))
-
-soc_sum$code_cat <- factor(as.factor(soc_sum$code_cat), levels = c("Social bridge", "Social barrier"))
-my_labs2 <- c("0", "30")
-
-ggplot(soc_sum) +
-  geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
-  scale_x_continuous(position = "top", 
-                     limits = c(0,1),
-                     expand = c(0,0), 
-                     breaks = c(0,0.25, 0.5, 0.75),
-                     labels = my_labs)+
-  scale_y_discrete(expand = expansion(add = c(0,0))) +
-  tidyquant::theme_tq() +
-  theme(
-    # Set background color to white
-    panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
-    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
-    axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
-    axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
-    axis.line.y.left = element_line(color = "black"),
-    # But customize labels for the horizontal axis
-    axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-    axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-    legend.position = "none", 
-    strip.text = element_text(size = 16)) + 
-  geom_text(aes(x = value, y = code_name, label = percent_label),
-    hjust = 0,
-    nudge_x = -0.0001,
-    colour = "black",
-    family = "Econ Sans Cnd",
-    size = 6)+
-  labs(subtitle = "Percent from all social bridges or barriers (%)") + 
-  theme(plot.subtitle = element_text(
-      family = "Econ Sans Cnd",
-      size = 20)
-  ) + 
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-  facet_wrap(~code_cat, scales = "free", nrow = 2)
-
-```
-:::
-
-### Code co-occurrence themes
-
-Could consider including code co-occurrence themes as a heat map, or could list the most frequent pairings as a table.
-
-::: panel-tabset
-#### All code relations
-
-This is a heatmap of all code relationships within articles. The number of co-ocurrences represents the number of times two codes co-occurered together in the same article.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 15
-#| fig-height: 12
-#| fig-align: center
-
-code_rel_melt <- reshape::melt(code_rel)
-code_rel_melt$variable <- gsub(".", " ", code_rel_melt$variable, fixed = TRUE)
-
-code_rel_melt <- code_rel_melt %>%
-  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
-
-code_rel_melt$key <- str_trim(code_rel_melt$key)
-
-colnames(code_rel_melt) <- c("brba_code1", "code1", "code2", "total")
-
-ggplot(code_rel_melt, aes(reorder(code1, -total), reorder(code2, total))) +
-geom_tile(aes(fill = total)) + 
-scale_fill_gradient2(high = "red")+
-ylab("")+
-xlab("")+
-labs(fill = "Number of co-occurences")+
-theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14))+
-geom_text(aes(label = total))
-```
-
-#### Most frequent code relations
-
-This heatmap represents the same data set as the last figure, but only includes co-occurrence values greater than or equal to 6, which is the 75% quantile of the co-occurrence totals.
-I have also added boxes around totals greater than 11, which was the 90% quantile of the co-occurrence total data set.
-Blue text represents data bridges and barriers, grey text represents ecological bridges and barriers, and orange text represents social bridges and barriers.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-#add brba column to second code col
-code_rel_melt2 <- code_rel_melt
-code_rel_melt2$brba_code2 <- NA
-
-code_rel_melt2$code2[code_rel_melt2$code2 == "Fine scale management appropriate for target species"] <- "Fine-scale management appropriate for target species"
-code_rel_melt2$code2[code_rel_melt2$code2 == "Pre existing conditions"] <- "Pre-existing conditions"
-code_rel_melt2$code2[code_rel_melt2$code2 == "Co management and communication"] <- "Co-management and communication"
-
-for(i in 1:nrow(code_rel_melt2)){
-  code_temp = code_rel_melt2$code2[i]
-
-  brba_temp = code_rel_melt2 %>% filter(code1 == code_temp & code2 == code_temp)
-  brba_code_temp = brba_temp$brba_code1[1]
-
-  code_rel_melt2$brba_code2[i] <- brba_code_temp
-}
-
-code_rel_melt2$brba_code2[code_rel_melt2$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
-
-group_colors = c("Data Bridge" = "dodgerblue4", "Data Barrier" = "dodgerblue4", "Ecological Bridge" = "honeydew4", "Ecological Barrier" = "honeydew4", "Social Bridge" = "darkorange4", "Social Barrier" = "darkorange4")
-
-code_rel_melt_h <- code_rel_melt2 %>%
-  filter(total >= 6) %>%
-  mutate(bor_box = ifelse(total >= 11, "TRUE", "FALSE"), 
-        bor_box = as.factor(bor_box), 
-        code1 = as.factor(code1), 
-        code2 = as.factor(code2))
-
-code_rel_melt_h$bor_box <- factor(code_rel_melt_h$bor_box, levels = c("TRUE", "FALSE"))
-
-code_rel_melt_h <- code_rel_melt_h %>%
-  mutate(code1 = reorder(code1, -total, FUN = mean),
-         code2 = reorder(code2, total, FUN = mean))
-
-unique_x_groups <- code_rel_melt_h %>%
-distinct(code1, brba_code1) %>%
-arrange(code1)
-
-unique_y_groups <- code_rel_melt_h %>%
-distinct(code2, brba_code2) %>%
-arrange(code2)
-
-x_colors <- setNames(group_colors[unique_x_groups$brba_code1], unique_x_groups$code1)
-y_colors <- setNames(group_colors[unique_y_groups$brba_code2], unique_y_groups$code2)
-
-ggplot(code_rel_melt_h, aes(reorder(code1, -total), reorder(code2, total))) +
-geom_tile(aes(fill = total, colour = bor_box)) + 
-scale_fill_gradient2(high = "red")+
-ylab("")+
-xlab("")+
-labs(fill = "Number of co-occurences")+
-theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]), 
-      panel.background = element_blank())+
-geom_text(aes(label = total))+
-scale_color_manual(values = c("black", "#00000000"))+
-guides(color = "none")
-
-```
-
-#### Data code relations
-
-This is a look at the data bridge and barrier code relations.
-Totals higher than or equal to 14 (90th quantile for data totals) are outlined in black.Here, red text represents codes that are barriers, and green text represents codes that are bridges.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-code_rel_d <- read.csv(here("data/code_rel_d.csv"))
-
-code_rel_melt_d <- reshape::melt(code_rel_d)
-code_rel_melt_d$variable <- gsub(".", " ", code_rel_melt_d$variable, fixed = TRUE)
-
-code_rel_melt_d <- code_rel_melt_d %>%
-  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
-
-code_rel_melt_d$key <- str_trim(code_rel_melt_d$key)
-
-colnames(code_rel_melt_d) <- c("brba_code1", "code1", "code2", "total")
-
-code_rel_melt2_d <- code_rel_melt_d
-code_rel_melt2_d$brba_code2 <- NA
-code_rel_melt2_d$brba_key1 <- NA
-code_rel_melt2_d$brba_key2 <- NA
-
-for(i in 1:nrow(code_rel_melt2_d)){
-  code_temp = code_rel_melt2_d$code2[i]
-
-  brba_temp = code_rel_melt2_d %>% filter(code1 == code_temp & code2 == code_temp)
-  brba_code_temp = brba_temp$brba_code1[1]
-
-  code_rel_melt2_d$brba_code2[i] <- brba_code_temp
-
-  if(grepl("Bridge", code_rel_melt2_d$brba_code1[i])){
-      code_rel_melt2_d$brba_key1[i] = "Bridge"
-  } else if(grepl("Barrier", code_rel_melt2_d$brba_code1[i])){
-      code_rel_melt2_d$brba_key1[i] = "Barrier"
-  }
-
-  if(grepl("Bridge", code_rel_melt2_d$brba_code2[i])){
-      code_rel_melt2_d$brba_key2[i] = "Bridge"
-  } else if(grepl("Barrier", code_rel_melt2_d$brba_code2[i])){
-      code_rel_melt2_d$brba_key2[i] = "Barrier"
-  }
-}
-
-code_rel_melt2_d <- code_rel_melt2_d %>%
-  mutate(bor_box = ifelse(total >= 14, "TRUE", "FALSE"), 
-        bor_box = as.factor(bor_box), 
-        code1 = as.factor(code1), 
-        code2 = as.factor(code2))
-
-code_rel_melt2_d$bor_box <- factor(code_rel_melt2_d$bor_box, levels = c("TRUE", "FALSE"))
-
-code_rel_melt2_d <- code_rel_melt2_d %>%
-  mutate(code1 = reorder(code1, -total, FUN = mean),
-         code2 = reorder(code2, total, FUN = mean))
-
-brba_colors <- c("Bridge" = "darkolivegreen", "Barrier" = "red4")
-
-unique_x_groups <- code_rel_melt2_d %>%
-distinct(code1, brba_key1) %>%
-arrange(code1)
-
-unique_y_groups <- code_rel_melt2_d %>%
-distinct(code2, brba_key2) %>%
-arrange(code2)
-
-x_colors <- setNames(brba_colors[unique_x_groups$brba_key1], unique_x_groups$code1)
-y_colors <- setNames(brba_colors[unique_y_groups$brba_key2], unique_y_groups$code2)
-
-ggplot(code_rel_melt2_d, aes(reorder(code1, -total), reorder(code2, total))) +
-geom_tile(aes(fill = total, colour = bor_box)) + 
-scale_fill_gradient2(high = "red")+
-ylab("")+
-xlab("")+
-labs(fill = "Number of co-occurences")+
-theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt2_d$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt2_d$code2)]))+
-geom_text(aes(label = total))+
-scale_color_manual(values = c("black", "#00000000"))+
-guides(color = "none")
-
-```
-
-#### Ecological code relations
-
-This is a look at the ecological bridge and barrier code relations.
-Totals higher than or equal to 5 (90th quantile for ecological totals) are outlined in black.Here, red text represents codes that are barriers, and green text represents codes that are bridges.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-code_rel_e <- read.csv(here("data/code_rel_e.csv"))
-
-code_rel_melt_e <- reshape::melt(code_rel_e)
-code_rel_melt_e$variable <- gsub(".", " ", code_rel_melt_e$variable, fixed = TRUE)
-
-code_rel_melt_e <- code_rel_melt_e %>%
-  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
-
-code_rel_melt_e$key <- str_trim(code_rel_melt_e$key)
-
-colnames(code_rel_melt_e) <- c("brba_code1", "code1", "code2", "total")
-
-code_rel_melt2_e <- code_rel_melt_e
-code_rel_melt2_e$brba_code2 <- NA
-code_rel_melt2_e$brba_key1 <- NA
-code_rel_melt2_e$brba_key2 <- NA
-
-code_rel_melt2_e$code2[code_rel_melt2_e$code2 == "Fine scale management appropriate for target species"] <- "Fine-scale management appropriate for target species"
-code_rel_melt2_e$brba_code2[code_rel_melt2_e$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
-
-for(i in 1:nrow(code_rel_melt2_e)){
-  code_temp = code_rel_melt2_e$code2[i]
-
-  brba_temp = code_rel_melt2_e %>% filter(code1 == code_temp & code2 == code_temp)
-  brba_code_temp = brba_temp$brba_code1[1]
-
-  code_rel_melt2_e$brba_code2[i] <- brba_code_temp
-
-  if(grepl("Bridge", code_rel_melt2_e$brba_code1[i])){
-      code_rel_melt2_e$brba_key1[i] = "Bridge"
-  } else if(grepl("Barrier", code_rel_melt2_e$brba_code1[i])){
-      code_rel_melt2_e$brba_key1[i] = "Barrier"
-  }
-
-  if(grepl("Bridge", code_rel_melt2_e$brba_code2[i])){
-      code_rel_melt2_e$brba_key2[i] = "Bridge"
-  } else if(grepl("Barrier", code_rel_melt2_e$brba_code2[i])){
-      code_rel_melt2_e$brba_key2[i] = "Barrier"
-  }
-}
-code_rel_melt2_e$brba_code2[code_rel_melt2_e$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
-code_rel_melt2_e$brba_key2[code_rel_melt2_e$code2 == "Target species is a prey specialist"] <- "Bridge"
-
-code_rel_melt2_e <- code_rel_melt2_e %>%
-  mutate(bor_box = ifelse(total >= 5, "TRUE", "FALSE"), 
-        bor_box = as.factor(bor_box), 
-        code1 = as.factor(code1), 
-        code2 = as.factor(code2))
-
-code_rel_melt2_e$bor_box <- factor(code_rel_melt2_e$bor_box, levels = c("TRUE", "FALSE"))
-
-code_rel_melt2_e <- code_rel_melt2_e %>%
-  mutate(code1 = reorder(code1, -total, FUN = mean),
-         code2 = reorder(code2, total, FUN = mean))
-
-unique_x_groups <- code_rel_melt2_e %>%
-distinct(code1, brba_key1) %>%
-arrange(code1)
-
-unique_y_groups <- code_rel_melt2_e %>%
-distinct(code2, brba_key2) %>%
-arrange(code2)
-
-x_colors <- setNames(brba_colors[unique_x_groups$brba_key1], unique_x_groups$code1)
-y_colors <- setNames(brba_colors[unique_y_groups$brba_key2], unique_y_groups$code2)
-
-ggplot(code_rel_melt2_e, aes(reorder(code1, -total), reorder(code2, total))) +
-geom_tile(aes(fill = total, colour = bor_box)) + 
-scale_fill_gradient2(high = "red")+
-ylab("")+
-xlab("")+
-labs(fill = "Number of co-occurences")+
-theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt2_e$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt2_e$code2)]))+
-geom_text(aes(label = total))+
-scale_color_manual(values = c("black", "#00000000"))+
-guides(color = "none")
-
-```
-
-#### Social code relations
-
-This is a look at the social bridge and barrier code relations.
-Totals higher than or equal to 5 (90th quantile for social totals) are outlined in black.Here, red text represents codes that are barriers, and green text represents codes that are bridges.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-code_rel_s <- read.csv(here("data/code_rel_s.csv"))
-
-code_rel_melt_s <- reshape::melt(code_rel_s)
-code_rel_melt_s$variable <- gsub(".", " ", code_rel_melt_s$variable, fixed = TRUE)
-
-code_rel_melt_s <- code_rel_melt_s %>%
-  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
-
-code_rel_melt_s$key <- str_trim(code_rel_melt_s$key)
-
-colnames(code_rel_melt_s) <- c("brba_code1", "code1", "code2", "total")
-
-code_rel_melt2_s <- code_rel_melt_s
-code_rel_melt2_s$brba_code2 <- NA
-code_rel_melt2_s$brba_key1 <- NA
-code_rel_melt2_s$brba_key2 <- NA
-
-code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Pre existing conditions"] <- "Pre-existing conditions"
-code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Co management and communication"] <- "Co-management and communication"
-
-for(i in 1:nrow(code_rel_melt2_s)){
-  code_temp = code_rel_melt2_s$code2[i]
-
-  brba_temp = code_rel_melt2_s %>% filter(code1 == code_temp & code2 == code_temp)
-  brba_code_temp = brba_temp$brba_code1[1]
-
-  code_rel_melt2_s$brba_code2[i] <- brba_code_temp
-
-  if(grepl("Bridge", code_rel_melt2_s$brba_code1[i])){
-      code_rel_melt2_s$brba_key1[i] = "Bridge"
-  } else if(grepl("Barrier", code_rel_melt2_s$brba_code1[i])){
-      code_rel_melt2_s$brba_key1[i] = "Barrier"
-  }
-
-  if(grepl("Bridge", code_rel_melt2_s$brba_code2[i])){
-      code_rel_melt2_s$brba_key2[i] = "Bridge"
-  } else if(grepl("Barrier", code_rel_melt2_s$brba_code2[i])){
-      code_rel_melt2_s$brba_key2[i] = "Barrier"
-  }
-}
-
-code_rel_melt2_s <- code_rel_melt2_s %>%
-  mutate(bor_box = ifelse(total >= 5, "TRUE", "FALSE"), 
-        bor_box = as.factor(bor_box), 
-        code1 = as.factor(code1), 
-        code2 = as.factor(code2))
-
-code_rel_melt2_s$bor_box <- factor(code_rel_melt2_s$bor_box, levels = c("TRUE", "FALSE"))
-
-code_rel_melt2_s <- code_rel_melt2_s %>%
-  mutate(code1 = reorder(code1, -total, FUN = mean),
-         code2 = reorder(code2, total, FUN = mean))
-
-unique_x_groups <- code_rel_melt2_s %>%
-distinct(code1, brba_key1) %>%
-arrange(code1)
-
-unique_y_groups <- code_rel_melt2_s %>%
-distinct(code2, brba_key2) %>%
-arrange(code2)
-
-x_colors <- setNames(brba_colors[unique_x_groups$brba_key1], unique_x_groups$code1)
-y_colors <- setNames(brba_colors[unique_y_groups$brba_key2], unique_y_groups$code2)
-
-ggplot(code_rel_melt2_s, aes(reorder(code1, -total), reorder(code2, total))) +
-geom_tile(aes(fill = total, colour = bor_box)) + 
-scale_fill_gradient2(high = "red")+
-ylab("")+
-xlab("")+
-labs(fill = "Number of co-occurences")+
-theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14, face = "bold", color = x_colors[levels(code_rel_melt2_s$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt2_s$code2)]))+
-geom_text(aes(label = total))+
-scale_color_manual(values = c("black", "#00000000"))+
-guides(color = "none")
-
-```
-:::
-
-# Surveys
-
-## Survey respondants
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 7
-#| fig-height: 4
-#| fig-align: center
-
-code_vars_s <- code_vars_s %>% mutate(survey = as.factor(survey))
-code_vars_s$survey <- factor(code_vars_s$survey , levels = c("Shad surveys","WhaleWatch TMMC surveys","WhaleWatch surveys", "Yellowtail surveys"))
-
-ggplot(code_vars_s, aes(x = "", fill = survey))+
-  geom_bar(position = "fill")+
-  xlab("")+
-  theme_minimal()+
-  labs(fill = "Respondant position")+
-  ylab("Percentage of survey respondants")+
-  coord_flip()+
-  scale_y_continuous(labels = scales::percent)+
-  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 4), labels = c("River Herring Avoidance Program", "Whale Safe Southern California", "Whale Safe Northern California", "Yellowtail Flounder Avoidance Program"))
-
-```
-
-## Respondant positions
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 7
-#| fig-height: 4
-#| fig-align: center
-
-code_vars_pos <- code_vars_s %>%
-  pivot_longer(
-    cols = "pos1":"pos5", 
-    names_to = "pos_number",
-    values_to = "pos_type"
-  )
-
-code_vars_pos <- code_vars_pos %>% mutate(pos_type = as.factor(pos_type))
-code_vars_pos$pos_type <- factor(code_vars_pos$pos_type , levels = c("Vessel operator", "Crew", "Vessel captain", "Fleet manager", "Fishery manager", "Commercial fisherman", "Fishery advisory board member", "Vessel owner", "Fishery scientist", "NA"))
-
-ggplot(code_vars_pos, aes(x = "", fill = pos_type))+
-  geom_bar(position = "fill")+
-  xlab("")+
-  theme_minimal()+
-  labs(fill = "Respondant position")+
-  ylab("Percentage of respondants")+
-  coord_flip()+
-  scale_y_continuous(labels = scales::percent)+
-  scale_fill_manual(values = MetBrewer::met.brewer("Veronese", n = 10))
-
-```
-
-## Respondant experience
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 5
-#| fig-height: 5
-#| fig-align: center
-
-ggplot(code_vars_s, aes(x = "", pos_num))+
-  geom_violin(size = 1.5, color = "steelblue4")+
-  geom_jitter(height = 0, width = 0.1, size = 3, color = "steelblue4", alpha = 0.5)+
-  theme_minimal() + 
-  xlab("")+
-  ylab("Number of years in position")+
-  theme(axis.title = element_text(size = 16), 
-        axis.text = element_text(size = 14, color = "black"))
-
-```
-
-## Code appearance frequencies across surveys (n = 21)
-
-The proportions reported in these figures represent the percent of surveys that mentioned a subcode within these broader code categories at least once.
-
-::: panel-tabset
-#### Broader categories
 
@@
 
-codes_vars_s2 = code_vars_s
-colnames(codes_vars_s2) <- gsub(x = colnames(codes_vars_s2), pattern = "\\.", replacement = " ")
+#reformat data
+code_sum_br <- code_freq %>%
+  filter(bridge_barr == "Bridge") %>%
+  mutate(n_total = sum(total)) %>%
+  group_by(code_cat, code_name) %>%
+  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
+  mutate(percent = scales::percent(value, accuracy = 1), 
+         code_name = factor(code_name)) %>%
+  ungroup() %>%
+  group_by(code_cat) %>%
+  arrange(code_name, desc(percent))
 
-  #calculate frequency of bridges vs. barriers being mentioned in surveys
-code_freq_new_s <- codes_vars_s2 %>%
-  mutate(br_pos = as.numeric(if_any(38:61, ~. == 1)), 
-         ba_pos = as.numeric(if_any(21:37, ~. == 1)),
-         br_reg = as.numeric(if_any(c(38:45), ~. ==1)),
-         br_soc = as.numeric(if_any(c(46:55), ~. == 1)), 
-         br_dat = as.numeric(if_any(c(56:57), ~. == 1)), 
-         br_eco = as.numeric(if_any(c(58:61), ~. == 1)), 
-         ba_reg = as.numeric(if_any(c(21:23), ~. == 1)),
-         ba_dat = as.numeric(if_any(c(24:26), ~. == 1)), 
-         ba_eco = as.numeric(if_any(c(27), ~. == 1)), 
-         ba_soc = as.numeric(if_any(c(28:37), ~. == 1)))
+#plot
+br_freq <- ggplot(code_sum_br, aes(x = value*100, y = reorder(code_name, value))) + 
+  geom_point(size = 5, color = "goldenrod") + 
+  scale_x_continuous(limits = c(0, 30), 
+                     breaks = seq(0, 30, 5), 
+                     name = "Percent appearance (%)") +
+  theme_minimal() +
+  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
+  theme(strip.placement = "outside",
+        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
+        axis.text = element_text(size = 12, color = "black"), 
+        axis.title = element_text(size = 14, color = "black")) +
+  ylab("")
 
-brba_sum_s <- code_freq_new_s %>%
-  summarise(n_br = sum(br_pos), freq_br = n_br/21,
-            n_ba = sum(ba_pos), freq_ba = n_ba/21,
-            n_br_e = sum(br_eco), freq_br_e = n_br_e/21,
-            n_br_d = sum(br_dat), freq_br_d = n_br_d/21,
-            n_br_s = sum(br_soc), freq_br_s = n_br_s/21,
-            n_br_r = sum(br_reg), freq_br_r = n_br_r/21,
-            n_ba_e = sum(ba_eco), freq_ba_e = n_ba_e/21,
-            n_ba_d = sum(ba_dat), freq_ba_d = n_ba_d/21,
-            n_ba_s = sum(ba_soc), freq_ba_s = n_ba_s/21, 
-            n_ba_r = sum(ba_reg), freq_ba_r = n_ba_r/21) %>%  
-  gather(br_ba, value, c(2,4,6, 8, 10, 12, 14, 16, 18, 20)) %>%
-  subset(select = c(br_ba, value)) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 1), 
-         percent = if_else(br_ba == "freq_ba" | br_ba == "freq_ba_e" | br_ba == "freq_ba_d" | br_ba == "freq_ba_s" | br_ba == "freq_ba_r", value, -value),
-         code_level = if_else(br_ba %in% c("freq_ba", "freq_br"), "Overall bridge or barrier", 
-                              if_else(br_ba %in% c("freq_ba_e", "freq_br_e"), "Ecological bridge or barrier", 
-                              if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("freq_ba_r", "freq_br_r"), "Regulatory bridge or barrier",
-                              if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA))))),
-         code_brba = if_else(br_ba %in% c("freq_br", "freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r"), "bridge", "barrier"),
-         alpha_brba = if_else(br_ba %in% c("freq_br_e", "freq_br_s", "freq_br_d", "freq_br_r", "freq_ba_e", "freq_ba_s", "freq_ba_d", "freq_ba_r"), "alpha", "no_alpha")) %>%
-  group_by(code_level)
-
-brba_sum_s$code_level <- factor(brba_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier", "Regulatory bridge or barrier","Social bridge or barrier", "Overall bridge or barrier"))
-brba_sum_s$code_brba <- factor(brba_sum_s$code_brba, levels = c("bridge", "barrier"))
-
-ggplot(brba_sum_s, aes(x = code_level, 
-             y = percent,
-             fill = code_brba)) +
-  geom_col(width = 0.7) +
-  geom_text(aes(label = percent_label),
-            position = position_stack(vjust = 0.65),
-            color = "black", 
-            size = 5) +
-  ylim(-1,1)+
-  coord_flip() +
-  scale_x_discrete() +
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
-  theme_minimal() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        axis.text.x =element_blank(),
-        axis.text.y = element_text(size = 20, color = "black"),
-        panel.grid = element_blank(),
-        legend.position = c(-0.21, 0.99),
-        legend.text = element_text(size = 16, color = "black"),
-        strip.text.y.right = element_text(angle = 0, size = 16)) +
-  geom_hline(yintercept = 0.0, linewidth = 1) + 
-  labs(fill = "")+ 
-  guides(fill = guide_legend(nrow = 1))
-```
-
-#### Data frequencies
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-# data_freq_s <- codes_vars_s2 %>%
-#   subset(select = c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency", "Environmental data availability", "Resource use data availability", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use")) %>%
-#   gather(category, pres_abs, 1:10) %>%
-#   mutate(br_ba = ifelse(category == "Gaps and inaccuracy" | category == "Management scales do not align with system needs" | category == "Model abuse" | category == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
-#   group_by(category, br_ba)  %>%
-#   summarise(n = sum(pres_abs), 
-#             freq = (n/118)) %>%
-#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
-#   group_by(category)
-# 
-# my_labs <- c("0", "25", "50", "75")
-# data_freq$br_ba <- factor(as.factor(data_freq$br_ba), levels = c("Data bridge", "Data barrier"))
-# 
-# data_bar <- ggplot(data_freq) +
-#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
-#   scale_x_continuous(position = "top", 
-#                      limits = c(0,0.9),
-#                      expand = c(0,0), 
-#                      breaks = c(0, 0.25, 0.5, 0.75),
-#                      labels = my_labs)+
-#   scale_y_discrete(expand = expansion(add = c(0,0))) +
-#   tidyquant::theme_tq() +
-#   theme(
-#     # Set background color to white
-#     panel.background = element_rect(fill = "white"),
-#     # Set the color and the width of the grid lines for the horizontal axis
-#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-#     # Remove tick marks by setting their length to 0
-#     axis.ticks.length = unit(0, "mm"),
-#     # Remove the title for both axes
-#     axis.title = element_blank(),
-#     # Only left line of the vertical axis is painted in black
-#     axis.line.y.left = element_line(color = "black"),
-#     # But customize labels for the horizontal axis
-#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-#     legend.position = "none", 
-#     strip.text = element_text(size = 16)) + 
-#   geom_text(aes(x = freq, y = category, label = percent_label),
-#     hjust = 0,
-#     nudge_x = -0.0001,
-#     colour = "black",
-#     family = "Econ Sans Cnd",
-#     size = 6)+
-#   labs(subtitle = "Percent of sum from all articles (%)") + 
-#   theme(plot.subtitle = element_text(
-#       family = "Econ Sans Cnd",
-#       size = 20)
-#   ) + 
-#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-#   facet_wrap(~br_ba, scales = "free", nrow = 2)
-# data_bar
+#ggsave("figures/ms_figs/all_freq/br_freq.png", width = 7, height = 8, units = c("in"))
 
 ```
-
-#### Ecological frequencies
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-# ecol_freq <- codes_vars2 %>%
-#   subset(select = c("Expected climate change induced range shifts", "Distinct habitat preferences", "Highly mobile target species", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence","Need for multispecies management")) %>%
-#   gather(category, pres_abs, 1:8) %>%
-#   mutate(br_ba = ifelse(category == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
-#   group_by(category, br_ba)  %>%
-#   summarise(n = sum(pres_abs), 
-#             freq = (n/118)) %>%
-#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
-#   group_by(category)
-# 
-# ecol_freq$category <- replace(ecol_freq$category, ecol_freq$category == "Fine scale management appropriate for target species", "Fine-scale management appropriate for target species")
-# ecol_freq$br_ba <- factor(as.factor(ecol_freq$br_ba), levels = c("Ecological bridge", "Ecological barrier"))
-# 
-# ecol_bar <- ggplot(ecol_freq) +
-#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
-#   scale_x_continuous(position = "top", 
-#                      limits = c(0,0.9),
-#                      expand = c(0,0), 
-#                      breaks = c(0, 0.25, 0.5, 0.75),
-#                      labels = my_labs)+
-#   scale_y_discrete(expand = expansion(add = c(0,0))) +
-#   tidyquant::theme_tq() +
-#   theme(
-#     # Set background color to white
-#     panel.background = element_rect(fill = "white"),
-#     # Set the color and the width of the grid lines for the horizontal axis
-#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-#     # Remove tick marks by setting their length to 0
-#     axis.ticks.length = unit(0, "mm"),
-#     # Remove the title for both axes
-#     axis.title = element_blank(),
-#     # Only left line of the vertical axis is painted in black
-#     axis.line.y.left = element_line(color = "black"),
-#     # But customize labels for the horizontal axis
-#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-#     legend.position = "none", 
-#     strip.text = element_text(size = 16)) + 
-#   geom_text(aes(x = freq, y = category, label = percent_label),
-#     hjust = 0,
-#     nudge_x = -0.0001,
-#     colour = "black",
-#     family = "Econ Sans Cnd",
-#     size = 6)+
-#   labs(subtitle = "Percent of sum from all articles (%)") + 
-#   theme(plot.subtitle = element_text(
-#       family = "Econ Sans Cnd",
-#       size = 20)
-#   ) + 
-#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-#   facet_wrap(~br_ba, scales = "free", nrow = 2)
-# 
-# ecol_bar
-
-```
-
-#### Social frequencies
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
-# soc_freq <- codes_vars2 %>%
-#   subset(select = c("Resource availability", "Pre existing conditions", "Adoption incentives", "Feasibility", "Co management and communication", "Indirect socioeconomic consequences", "Discontinuity", "Cost", "Poor communication and outreach", "Poor program implementation")) %>%
-#   gather(category, pres_abs, 1:9) %>%
-#   mutate(br_ba = ifelse(category == "Indirect socioeconomic consequences" | category == "Discontinuity" | category == "Poor communication and outreach" | category == "Poor program implementation" | category == "Cost", "Social barrier", "Social bridge")) %>%
-#   group_by(category, br_ba)  %>%
-#   summarise(n = sum(pres_abs), 
-#             freq = (n/118)) %>%
-#   mutate(percent_label = scales::percent(freq, accuracy = 2)) %>%
-#   group_by(category)
-# 
-# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Co management and communication", "Co-management and communication")
-# soc_freq$category <- replace(soc_freq$category, soc_freq$category == "Pre existing conditions", "Pre-existing conditions")
-# soc_freq$br_ba <- factor(as.factor(soc_freq$br_ba), levels = c("Social bridge", "Social barrier"))
-# 
-# 
-# soc_bar <- ggplot(soc_freq) +
-#   geom_bar(aes(x = freq, y = reorder(category, freq), fill = br_ba), width = 0.6, stat = "identity")+
-#   scale_x_continuous(position = "top", 
-#                      limits = c(0,0.9),
-#                      expand = c(0,0), 
-#                      breaks = c(0, 0.25, 0.5, 0.75),
-#                      labels = my_labs)+
-#   scale_y_discrete(expand = expansion(add = c(0,0))) +
-#   tidyquant::theme_tq() +
-#   theme(
-#     # Set background color to white
-#     panel.background = element_rect(fill = "white"),
-#     # Set the color and the width of the grid lines for the horizontal axis
-#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-#     # Remove tick marks by setting their length to 0
-#     axis.ticks.length = unit(0, "mm"),
-#     # Remove the title for both axes
-#     axis.title = element_blank(),
-#     # Only left line of the vertical axis is painted in black
-#     axis.line.y.left = element_line(color = "black"),
-#     # But customize labels for the horizontal axis
-#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-#     legend.position = "none", 
-#     strip.text = element_text(size = 16)) + 
-#   geom_text(aes(x = freq, y = category, label = percent_label),
-#     hjust = 0,
-#     nudge_x = -0.0001,
-#     colour = "black",
-#     family = "Econ Sans Cnd",
-#     size = 6)+
-#   labs(subtitle = "Percent of sum from all articles (%)") + 
-#   theme(plot.subtitle = element_text(
-#       family = "Econ Sans Cnd",
-#       size = 20)
-#   ) + 
-#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-#   facet_wrap(~br_ba, scales = "free", nrow = 2)
-# soc_bar
-
-```
-
-#### Regulatory frequencies
-
-:::
-
-## Code appearance frequencies within code categories
-
-Here, I have plotted the same information as the previous section, but as a percentage of the overall bridges and barriers groupings.
-For example, data bridges make up 37% of all bridge codes.
-The same pattern holds for the other sub-panels.
-For example, on the ecological page, abiotic indicators account for 22% of all ecological bridge codes.
-
-::: panel-tabset
-#### Broader categories
 
@@
 
-code_sum_s <- code_freq_s %>%
-  group_by(bridge_barr) %>%
+#reformat data
+code_sum_ba <- code_freq %>%
+  filter(bridge_barr == "Barrier") %>%
   mutate(n_total = sum(total)) %>%
+  group_by(code_cat, code_name) %>%
+  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
+  mutate(percent = scales::percent(value, accuracy = 1), 
+         code_name = factor(code_name)) %>%
   ungroup() %>%
   group_by(code_cat) %>%
-  mutate(n_subtotal = sum(total)) %>%
-  summarise(value = n_subtotal/n_total) %>%
-  rename("br_ba" = code_cat) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 1), 
-         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Regulation barrier", value, -value),
-         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
-                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("Regulation barrier", "Regulation bridge"), "Regulatory bridge or barrier",
-                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA)))), 
-         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Regulation bridge"), "bridge", "barrier")) %>%
-  group_by(code_level) %>%
-  distinct()
+  arrange(code_name, desc(percent))
 
-code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier","Regulatory bridge or barrier", "Social bridge or barrier"))
-code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))
+#plot
+ba_freq <- ggplot(code_sum_ba, aes(x = value*100, y = reorder(code_name, value))) + 
+  geom_point(size = 5, color = "lightskyblue3") + 
+  scale_x_continuous(limits = c(0, 30), 
+                     breaks = seq(0, 30, 5), 
+                     name = "Percent appearance (%)") +
+  theme_minimal() +
+  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
+  theme(strip.placement = "outside",
+        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
+        axis.text = element_text(size = 12, color = "black"), 
+        axis.title = element_text(size = 14, color = "black")) +
+  ylab("")
 
-ggplot(code_sum_s, aes(x = code_level, 
-             y = percent,
-             fill = code_brba)) +
-  geom_col(width = 0.7) +
-  geom_text(aes(label = percent_label),
-            position = position_stack(vjust = 0.65),
-            color = "black", 
-            size = 5) +
-  ylim(-0.7,0.7)+
-  coord_flip() +
-  scale_x_discrete() +
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
-  theme_minimal() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        axis.text.x =element_blank(),
-        axis.text.y = element_text(size = 20, color = "black"),
-        panel.grid = element_blank(),
-        legend.position = c(-0.17, 0.99),
-        legend.text = element_text(size = 16, color = "black"),
-        strip.text.y.right = element_text(angle = 0, size = 16)) +
-  geom_hline(yintercept = 0.0, linewidth = 1) + 
-  labs(fill = "")+ 
-  guides(fill = guide_legend(nrow = 1))
+#ggsave("figures/ms_figs/all_freq/ba_freq.png", width = 8, height = 8, units = c("in"))
 
@@
 
-#### Data codes
+![](images/br_ba_freq.png){fig-align="center" width="8in", height = "10in"}
 
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
+### Surveys
 
-# data_freq <- code_freq %>%
-#   filter(code_cat == "Data bridge" | code_cat == "Data barrier")
-# 
-# data_sum <- data_freq %>%
-#   group_by(bridge_barr) %>%
-#   mutate(n_total = sum(total)) %>%
-#   ungroup() %>%
-#   group_by(code_name) %>% 
-#   summarise(value = total/n_total) %>%
-#   mutate(code_cat = ifelse(code_name == "Gaps and inaccuracy" | code_name == "Management scales do not align with system needs" | code_name == "Model abuse" | code_name == "Climate change adding uncertainty to target species habitat use", "Data barrier", "Data bridge")) %>%
-#   mutate(percent_label = scales::percent(value, accuracy = 2))
-#   
-# my_labs <- c("0", "25", "50", "75")
-# data_sum$code_cat <- factor(as.factor(data_sum$code_cat), levels = c("Data bridge", "Data barrier"))
-# 
-# ggplot(data_sum) +
-#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
-#   scale_x_continuous(position = "top", 
-#                      limits = c(0,0.9),
-#                      expand = c(0,0), 
-#                      breaks = c(0, 0.25, 0.5, 0.75),
-#                      labels = my_labs)+
-#   scale_y_discrete(expand = expansion(add = c(0,0))) +
-#   tidyquant::theme_tq() +
-#   theme(
-#     # Set background color to white
-#     panel.background = element_rect(fill = "white"),
-#     # Set the color and the width of the grid lines for the horizontal axis
-#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-#     # Remove tick marks by setting their length to 0
-#     axis.ticks.length = unit(0, "mm"),
-#     # Remove the title for both axes
-#     axis.title = element_blank(),
-#     # Only left line of the vertical axis is painted in black
-#     axis.line.y.left = element_line(color = "black"),
-#     # But customize labels for the horizontal axis
-#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-#     legend.position = "none", 
-#     strip.text = element_text(size = 16)) + 
-#   geom_text(aes(x = value, y = code_name, label = percent_label),
-#     hjust = 0,
-#     nudge_x = -0.0001,
-#     colour = "black",
-#     family = "Econ Sans Cnd",
-#     size = 6)+
-#   labs(subtitle = "Percent from all data bridges or barriers (%)") + 
-#   theme(plot.subtitle = element_text(
-#       family = "Econ Sans Cnd",
-#       size = 20)
-#   ) + 
-#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-#   facet_wrap(~code_cat, scales = "free", nrow = 2)
+:::
 
-```
+## Result 3: Variations by industry (fishing vs. shipping)
 
-#### Ecological codes
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-# eco_freq <- code_freq %>%
-#   filter(code_cat == "Ecological bridge" | code_cat == "Ecological barrier")
-# 
-# eco_sum <- eco_freq %>%
-#   group_by(bridge_barr) %>%
-#   mutate(n_total = sum(total)) %>%
-#   ungroup() %>%
-#   group_by(code_name) %>% 
-#   summarise(value = total/n_total) %>%
-#   mutate(code_cat = ifelse(code_name == "Need for multispecies management", "Ecological barrier", "Ecological bridge")) %>%
-#   mutate(percent_label = scales::percent(value, accuracy = 2))
-#   
-# eco_sum$code_cat <- factor(as.factor(eco_sum$code_cat), levels = c("Ecological bridge", "Ecological barrier"))
-# my_labs2 <- c("0", "30", "50", "75", "100")
-# 
-# ggplot(eco_sum) +
-#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
-#   scale_x_continuous(position = "top", 
-#                      limits = c(0,1.1),
-#                      expand = c(0,0), 
-#                      breaks = c(0, 0.3, 0.5, 0.75, 1),
-#                      labels = my_labs2)+
-#   scale_y_discrete(expand = expansion(add = c(0,0))) +
-#   tidyquant::theme_tq() +
-#   theme(
-#     # Set background color to white
-#     panel.background = element_rect(fill = "white"),
-#     # Set the color and the width of the grid lines for the horizontal axis
-#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-#     # Remove tick marks by setting their length to 0
-#     axis.ticks.length = unit(0, "mm"),
-#     # Remove the title for both axes
-#     axis.title = element_blank(),
-#     # Only left line of the vertical axis is painted in black
-#     axis.line.y.left = element_line(color = "black"),
-#     # But customize labels for the horizontal axis
-#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-#     legend.position = "none", 
-#     strip.text = element_text(size = 16)) + 
-#   geom_text(aes(x = value, y = code_name, label = percent_label),
-#     hjust = 0,
-#     nudge_x = -0.0001,
-#     colour = "black",
-#     family = "Econ Sans Cnd",
-#     size = 6)+
-#   labs(subtitle = "Percent from all ecological bridges or barriers (%)") + 
-#   theme(plot.subtitle = element_text(
-#       family = "Econ Sans Cnd",
-#       size = 20)
-#   ) + 
-#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-#   facet_wrap(~code_cat, scales = "free", nrow = 2)
-
-```
-
-#### Social codes
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-align: center
-
-# soc_freq <- code_freq %>%
-#   filter(code_cat == "Social bridge" | code_cat == "Social barrier")
-# 
-# soc_sum <- soc_freq %>%
-#   group_by(bridge_barr) %>%
-#   mutate(n_total = sum(total)) %>%
-#   ungroup() %>%
-#   group_by(code_name) %>% 
-#   summarise(value = total/n_total) %>%
-#   mutate(code_cat = ifelse(code_name == "Cost" | code_name == "Indirect socioeconomic consequences" | code_name == "Discontinuity" | code_name == "Poor communication and outreach" | code_name == "Poor program implementation", "Social barrier", "Social bridge")) %>%
-#   mutate(percent_label = scales::percent(value, accuracy = 2))
-#   
-# soc_sum$code_cat <- factor(as.factor(soc_sum$code_cat), levels = c("Social bridge", "Social barrier"))
-# my_labs2 <- c("0", "30")
-# 
-# ggplot(soc_sum) +
-#   geom_bar(aes(x = value, y = reorder(code_name, value), fill = code_cat), width = 0.6, stat = "identity")+
-#   scale_x_continuous(position = "top", 
-#                      limits = c(0,1),
-#                      expand = c(0,0), 
-#                      breaks = c(0,0.25, 0.5, 0.75),
-#                      labels = my_labs)+
-#   scale_y_discrete(expand = expansion(add = c(0,0))) +
-#   tidyquant::theme_tq() +
-#   theme(
-#     # Set background color to white
-#     panel.background = element_rect(fill = "white"),
-#     # Set the color and the width of the grid lines for the horizontal axis
-#     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-#     # Remove tick marks by setting their length to 0
-#     axis.ticks.length = unit(0, "mm"),
-#     # Remove the title for both axes
-#     axis.title = element_blank(),
-#     # Only left line of the vertical axis is painted in black
-#     axis.line.y.left = element_line(color = "black"),
-#     # But customize labels for the horizontal axis
-#     axis.text.x = element_text(family = "Econ Sans Cnd", size = 16), 
-#     axis.text.y = element_text(family = "Econ Sans Cnd", size = 16), 
-#     legend.position = "none", 
-#     strip.text = element_text(size = 16)) + 
-#   geom_text(aes(x = value, y = code_name, label = percent_label),
-#     hjust = 0,
-#     nudge_x = -0.0001,
-#     colour = "black",
-#     family = "Econ Sans Cnd",
-#     size = 6)+
-#   labs(subtitle = "Percent from all social bridges or barriers (%)") + 
-#   theme(plot.subtitle = element_text(
-#       family = "Econ Sans Cnd",
-#       size = 20)
-#   ) + 
-#   scale_fill_manual(values = c("goldenrod", "lightskyblue3"))+
-#   facet_wrap(~code_cat, scales = "free", nrow = 2)
-
-```
-
-#### Regulatory codes
-:::
+## Result 4: Variations by position (survey only)

### 2025-09-20 reports/lit_codes_explore.qmd
res fig 2

@@
 
-## Code appearance frequencies across surveys (n = 21)
+## Code appearance frequencies across surveys (n = 2, not including EcoCast)
 
@@
 code_freq_new_s <- codes_vars_s2 %>%
-  mutate(br_pos = as.numeric(if_any(38:61, ~. == 1)), 
-         ba_pos = as.numeric(if_any(21:37, ~. == 1)),
-         br_reg = as.numeric(if_any(c(38:45), ~. ==1)),
-         br_soc = as.numeric(if_any(c(46:55), ~. == 1)), 
-         br_dat = as.numeric(if_any(c(56:57), ~. == 1)), 
-         br_eco = as.numeric(if_any(c(58:61), ~. == 1)), 
-         ba_reg = as.numeric(if_any(c(21:23), ~. == 1)),
-         ba_dat = as.numeric(if_any(c(24:26), ~. == 1)), 
-         ba_eco = as.numeric(if_any(c(27), ~. == 1)), 
-         ba_soc = as.numeric(if_any(c(28:37), ~. == 1)))
+  mutate(br_pos = as.numeric(if_any(37:54, ~. == 1)), 
+         ba_pos = as.numeric(if_any(21:36, ~. == 1)),
+         br_reg = as.numeric(if_any(c(37:44, 50), ~. ==1)),
+         br_soc = as.numeric(if_any(c(45:49, 51), ~. == 1)), 
+         br_dat = as.numeric(if_any(c(52), ~. == 1)), 
+         br_eco = as.numeric(if_any(c(53, 54), ~. == 1)), 
+         ba_reg = as.numeric(if_any(c(21, 22), ~. == 1)),
+         ba_dat = as.numeric(if_any(c(23:25), ~. == 1)), 
+         ba_eco = as.numeric(if_any(c(26), ~. == 1)), 
+         ba_soc = as.numeric(if_any(c(27:36), ~. == 1)))
 
 brba_sum_s <- code_freq_new_s %>%
-  summarise(n_br = sum(br_pos), freq_br = n_br/21,
+  summarise(n_br = sum(br_pos), freq_br = n_br/21, #total number of surveys not including EcoCast
             n_ba = sum(ba_pos), freq_ba = n_ba/21,
@@
                               if_else(br_ba %in% c("freq_ba_d", "freq_br_d"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("freq_ba_r", "freq_br_r"), "Regulatory bridge or barrier",
+                              if_else(br_ba %in% c("freq_ba_r", "freq_br_r"), "Implementation bridge or barrier",
                               if_else(br_ba %in% c("freq_ba_s", "freq_br_s"), "Social bridge or barrier", NA))))),
@@
 
-brba_sum_s$code_level <- factor(brba_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier", "Regulatory bridge or barrier","Social bridge or barrier", "Overall bridge or barrier"))
+brba_sum_s$code_level <- factor(brba_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier", "Implementation bridge or barrier","Social bridge or barrier", "Overall bridge or barrier"))
 brba_sum_s$code_brba <- factor(brba_sum_s$code_brba, levels = c("bridge", "barrier"))
@@
 
-#### Regulatory frequencies
+#### Implementation frequencies
 
@@
                               if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("Regulation barrier", "Regulation bridge"), "Regulatory bridge or barrier",
+                              if_else(br_ba %in% c("Regulation barrier", "Regulation bridge"), "Implementation bridge or barrier",
                               if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA)))), 
@@
 
-code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier","Regulatory bridge or barrier", "Social bridge or barrier"))
+code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Ecological bridge or barrier", "Data bridge or barrier","Implementation bridge or barrier", "Social bridge or barrier"))
 code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))
@@
 
-#### Regulatory codes
+#### Implementation codes
 :::

### 2025-09-22 reports/draft_results.qmd
updated figures

@@
 
-**Which themes overlap between the literature and surveys?**
+**Which themes appear in both sources?**
 
-**Which themes only appear in the literature? Which themes are unique to the surveys?**
+**What new information have surveys added beyond what was already written in the literature?**
 
@@
 ::: panel-tabset
-
 #### Review: Bridge themes
@@
 
+Code appearance frequencies across all bridge **OR** barrier codes. The proportions reported in these figures represent the percent of codes that theme or sub-theme comprises.
+
 ::: panel-tabset
-
 ### Literature
-Code appearance frequencies across articles (n = 118).
-The proportions reported in these figures represent the percent of papers that mentioned a subcode within these broader code categories at least once.
 
@@
   geom_point(size = 5, color = "goldenrod") + 
-  scale_x_continuous(limits = c(0, 30), 
-                     breaks = seq(0, 30, 5), 
-                     name = "Percent appearance (%)") +
+  # scale_x_continuous(limits = c(0, 30), 
+  #                    breaks = seq(0, 30, 5), 
+  #                    name = "Percent appearance (%)") +
   theme_minimal() +
   facet_wrap("code_cat", ncol = 1, scales = "free_y") +
+  scale_x_reverse(limits = c(30, 0), 
+                  #breaks = seq(0, 30, 5), 
+                  name = "Percent appearance (%)")+
   theme(strip.placement = "outside",
@@
   scale_x_continuous(limits = c(0, 30), 
-                     breaks = seq(0, 30, 5), 
+                     breaks = seq(0, 30, 10), 
                      name = "Percent appearance (%)") +
+  scale_y_discrete(position = "right") +
   theme_minimal() +
@@
   theme(strip.placement = "outside",
-        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
+        strip.text = element_text(face = "bold", size = 14, hjust = 1), 
         axis.text = element_text(size = 12, color = "black"), 
@@
 
-![](images/br_ba_freq.png){fig-align="center" width="8in", height = "10in"}
+![](images/br_ba_freq.png){fig-align="center" width="10in", height = "12in"}
 
@@
 
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+#theme bridge/barrier
+code_sum_s <- code_freq_s %>%
+  group_by(bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(code_cat) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  summarise(value = n_subtotal/n_total) %>%
+  rename("br_ba" = code_cat) %>%
+  mutate(percent_label = scales::percent(value, accuracy = 1), 
+         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Implementation barrier", value, -value),
+         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", 
+                              if_else(br_ba %in% c("Implementation bridge", "Implementation barrier"), "Implementation bridge or barrier", NA)))), 
+         code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge"), "bridge", "barrier")) %>%
+  group_by(code_level) %>%
+  distinct()
+
+code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Implementation bridge or barrier", "Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier"))
+code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))
+
+all_freq_survey <- ggplot(code_sum_s, aes(x = code_level, 
+             y = percent,
+             fill = code_brba)) +
+  geom_col(width = 0.7) +
+  geom_text(aes(label = percent_label),
+            position = position_stack(vjust = 0.65),
+            color = "black", 
+            size = 5) +
+  ylim(-0.55,0.7)+
+  coord_flip() +
+  scale_x_discrete() +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.x =element_blank(),
+        axis.text.y = element_text(size = 26, color = "black"),
+        panel.grid = element_blank(),
+        legend.position = c(-0.17, 0.99),
+        legend.text = element_text(size = 20, color = "black"),
+        strip.text.y.right = element_text(angle = 0, size = 18)) +
+  geom_hline(yintercept = 0.0, linewidth = 1) + 
+  labs(fill = "")+ 
+  guides(fill = guide_legend(nrow = 1))
+
+#ggsave("figures/ms_figs/all_freq/all_freq_survey.png", width = 13, height = 8, units = ("in"))
+
+#bridge freq
+#reformat data
+code_freq_s$code_cat <- factor(code_freq_s$code_cat, levels = c("Data bridge", "Data barrier", "Ecological bridge", "Ecological barrier", "Social bridge", "Social barrier", "Implementation bridge","Implementation barrier"))
+
+code_sum_br_s <- code_freq_s %>%
+  filter(bridge_barr == "Bridge") %>%
+  mutate(n_total = sum(total)) %>%
+  group_by(code_cat, code_name) %>%
+  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
+  mutate(percent = scales::percent(value, accuracy = 1), 
+         code_name = factor(code_name)) %>%
+  ungroup() %>%
+  group_by(code_cat) %>%
+  arrange(code_name, desc(percent))
+
+#plot
+br_freq_s <- ggplot(code_sum_br_s, aes(x = value*100, y = reorder(code_name, value))) + 
+  geom_point(size = 5, color = "goldenrod") + 
+  # scale_x_continuous(limits = c(0, 30), 
+  #                    breaks = seq(0, 30, 5), 
+  #                    name = "Percent appearance (%)") +
+  theme_minimal() +
+  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
+  scale_x_reverse(limits = c(20, 0), 
+                  #breaks = seq(0, 30, 5), 
+                  name = "Percent appearance (%)")+
+  theme(strip.placement = "outside",
+        strip.text = element_text(face = "bold", size = 14, hjust = 0), 
+        axis.text = element_text(size = 12, color = "black"), 
+        axis.title = element_text(size = 14, color = "black")) +
+  ylab("")
+
+#ggsave("figures/ms_figs/all_freq/br_freq_survey.png", width = 6, height = 8, units = c("in"))
+
+#barrier freq
+#reformat data
+code_sum_ba_s <- code_freq_s %>%
+  filter(bridge_barr == "Barrier") %>%
+  mutate(n_total = sum(total)) %>%
+  group_by(code_cat, code_name) %>%
+  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
+  mutate(percent = scales::percent(value, accuracy = 1), 
+         code_name = factor(code_name)) %>%
+  ungroup() %>%
+  group_by(code_cat) %>%
+  arrange(code_name, desc(percent))
+
+#plot
+ba_freq_s <- ggplot(code_sum_ba_s, aes(x = value*100, y = reorder(code_name, value))) + 
+  geom_point(size = 5, color = "lightskyblue3") + 
+  scale_x_continuous(limits = c(0, 20), 
+                     breaks = seq(0, 20, 10), 
+                     name = "Percent appearance (%)") +
+  scale_y_discrete(position = "right") +
+  theme_minimal() +
+  facet_wrap("code_cat", ncol = 1, scales = "free_y") +
+  theme(strip.placement = "outside",
+        strip.text = element_text(face = "bold", size = 16, hjust = 1), 
+        axis.text = element_text(size = 12, color = "black"), 
+        axis.title = element_text(size = 14, color = "black")) +
+  ylab("")
+
+#ggsave("figures/ms_figs/all_freq/ba_freq_survey.png", width = 6, height = 9, units = c("in"))
+
+```
+
+![](images/br_ba_freq_survey.png){fig-align="center" width="10in", height = "12in"}
 :::
 
-## Result 3: Variations by industry (fishing vs. shipping)
+## Result 3: Variations by industry
+
+### 3.1: Conservation problems DOM has been used to address
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 9
+#| fig-height: 5.5
+#| fig-align: center
+
+codes_vars$broad_location <- as.factor(codes_vars$broad_location)
+codes_LU <- codes_vars[!duplicated(codes_vars$Lit_unit), ]
+
+consv <- codes_LU %>%
+  gather(col, consv_topic, reason1:reason3) %>%
+  subset(select = consv_topic)
+
+consv_s <- consv %>%
+  group_by(consv_topic) %>%
+  filter(consv_topic != "NA") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+consv_bar <- ggplot(consv_s) +
+  geom_bar(aes(x = perc, y = reorder(consv_topic, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 45))+
+  scale_y_discrete(expand = expansion(add = c(0,0))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Arial", size = 12)) + 
+  geom_text(aes(x = perc, y = consv_topic, label = consv_topic),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Arial",
+    size = 3.5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Arial",
+      size = 13)
+  )
+
+consv_bar
+```
+
+### 3.2: Fishing vs. shipping
 

### 2025-09-24 reports/draft_results.qmd
time series and heat map

@@
 
-## Result 2: Frequencies according to review and survey
+## Result 2: Codes by review and survey
+
+### Result 2.1: Frequencies according to review and survey
 
@@
 
+### Result 2.2: Time series of top theme from literature, co-management
+
+Grey is the number of DOM publications per year, while blue is the number of times co-management and communication was referenced.
+Whanted to see if this code was referenced more over time, but seems that it just tracks the number of DOM publications.
+Likely won't include.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 7
+#| fig-height: 5
+#| fig-align: center
+
+code_ts <- codes_vars %>% 
+  mutate(year = str_extract_all(Doc, "\\d+\\.?\\d*"), 
+         year = as.Date(as.character(year), format = "%Y"), 
+         year = year(year)) %>%
+  select(c(Doc, year, Co.management.and.communication)) %>%
+  group_by(year) %>%
+  summarise(n_appear = sum(Co.management.and.communication), 
+            n_year = n())
+
+colnames(code_ts) <- c("Year", "com", "pubs")
+
+ggplot(code_ts, aes(as.numeric(Year))) + 
+  geom_path(aes(y = com), linewidth = 1.5, color = "dodgerblue4") + 
+  geom_point(aes(y= com), size = 5, fill = "dodgerblue4", color = "black", shape = 21) + 
+  geom_path(aes(y = pubs), linewidth = 1.5, color = "grey60") + 
+  geom_point(aes(y = pubs), size = 5, fill = "grey60", color = "black", shape = 21) +
+  xlab("") +
+  ylab("Count (#)") +
+  theme_minimal() + 
+  theme(axis.text = element_text(size = 14, color = "black"), 
+        axis.title = element_text(size = 16, color = "black")) 
+```
+
+### Result 2.3: Heat maps of theme co-occurence
+
+This heatmap represents number of times two codes co-occurered together in the same article, or "theme co-occurence".
+I have filtered totals greater than or equal to 11, which was the 90% quantile of the co-occurrence total data set.
+Blue text represents data bridges and barriers, grey text represents ecological bridges and barriers, and orange text represents social bridges and barriers.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 5
+#| fig-height: 5
+#| fig-align: center
+#| include: FALSE
+
+code_rel_melt <- reshape::melt(code_rel)
+code_rel_melt$variable <- gsub(".", " ", code_rel_melt$variable, fixed = TRUE)
+
+code_rel_melt <- code_rel_melt %>%
+  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
+
+code_rel_melt$key <- str_trim(code_rel_melt$key)
+
+colnames(code_rel_melt) <- c("brba_code1", "code1", "code2", "total")
+
+#add brba column to second code col
+code_rel_melt2 <- code_rel_melt
+code_rel_melt2$brba_code2 <- NA
+
+code_rel_melt2$code2[code_rel_melt2$code2 == "Fine scale management appropriate for target species"] <- "Fine-scale management appropriate for target species"
+code_rel_melt2$code2[code_rel_melt2$code2 == "Pre existing regulation and management institutions"] <- "Pre-existing regulation and management institutions"
+code_rel_melt2$code2[code_rel_melt2$code2 == "Co management and communication"] <- "Co-management and communication"
+
+for(i in 1:nrow(code_rel_melt2)){
+  code_temp = code_rel_melt2$code2[i]
+
+  brba_temp = code_rel_melt2 %>% filter(code1 == code_temp & code2 == code_temp)
+  brba_code_temp = brba_temp$brba_code1[1]
+
+  code_rel_melt2$brba_code2[i] <- brba_code_temp
+}
+
+code_rel_melt2$brba_code2[code_rel_melt2$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
+
+group_colors = c("Data Bridge" = "dodgerblue4", "Data Barrier" = "dodgerblue4", "Ecological Bridge" = "honeydew4", "Ecological Barrier" = "honeydew4", "Social Bridge" = "darkorange4", "Social Barrier" = "darkorange4")
+
+code_rel_melt_h <- code_rel_melt2 %>%
+  filter(total >= 11) %>%
+  mutate(bor_box = ifelse(total >= 11, "TRUE", "FALSE"), 
+        bor_box = as.factor(bor_box), 
+        code1 = as.factor(code1), 
+        code2 = as.factor(code2))
+
+code_rel_melt_h$bor_box <- factor(code_rel_melt_h$bor_box, levels = c("TRUE", "FALSE"))
+
+code_rel_melt_h <- code_rel_melt_h %>%
+  mutate(code1 = reorder(code1, -total, FUN = mean),
+         code2 = reorder(code2, total, FUN = mean))
+
+unique_x_groups <- code_rel_melt_h %>%
+distinct(code1, brba_code1) %>%
+arrange(code1)
+
+unique_y_groups <- code_rel_melt_h %>%
+distinct(code2, brba_code2) %>%
+arrange(code2)
+
+x_colors <- setNames(group_colors[unique_x_groups$brba_code1], unique_x_groups$code1)
+y_colors <- setNames(group_colors[unique_y_groups$brba_code2], unique_y_groups$code2)
+
+ggplot(code_rel_melt_h, aes(x = code1, y = reorder(code2, total))) +
+geom_tile(aes(fill = total, colour = bor_box)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+labs(fill = "Number of co-occurences")+
+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]), 
+      panel.background = element_blank())+
+geom_text(aes(label = total))+
+scale_color_manual(values = c("black", "#00000000"))+
+guides(color = "none")
+
+#ggsave("figures/ms_figs/heat_tile.png", width = 10, height = 8, units = c("in"))
+
+```
+
+![](images/heat_tile_ai.png){fig-align="center" width="10in", height = "8in"}
+
 ## Result 3: Variations by industry
 
-### 3.1: Conservation problems DOM has been used to address
+### 3.1: Management and conservation problems DOM has been used to address
 

### 2025-09-27 reports/draft_results.qmd
stack bar and radar plots

@@
 code_freq$code_name <- replace(code_freq$code_name, code_freq$code_name == "Recipient participation", "Poor program implementation")
+
+theme_ms <- function(){
+  theme_minimal() %+replace%    
+    theme(axis.text = element_text(size = 14, color = "black"), 
+          axis.title = element_text(size = 16, color = "black"), 
+          strip.text = element_text(size = 13, color = "black"))
+}
 
@@
 
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+
+#format data
+freq_job_survey <- code_vars_s %>% 
+  select(c(1, 21:54)) %>% 
+  janitor::clean_names() %>%
+  pivot_longer(2:35, names_to = "sub_theme", values_to = "total") %>%
+  group_by(survey, sub_theme) %>%
+  summarise(total = sum(total), 
+            .groups = "drop") %>%
+  mutate(fish_ship = ifelse(str_detect(survey, "WhaleWatch"), "Shipping", "Fishing"))
+
+lib_job_survey <- code_freq_s %>%
+  mutate(id = paste(bridge_barr, code_cat, code_name, sep = "_")) %>% 
+  select(id)
+
+freq_job_survey$id <- NA
+for(i in 1:nrow(freq_job_survey)){
+  curr_code = freq_job_survey$sub_theme[i]
+  curr_id = lib_job_survey$id[agrepl(curr_code, lib_job_survey$id, 6)]
+
+  freq_job_survey$id[i] <- curr_id
+
+}
+
+freq_job_survey$id[freq_job_survey$sub_theme == "stigmatization"] <- "Barrier_Social barrier_Stigmatization"
+freq_job_survey$id[freq_job_survey$sub_theme == "cost"] <- "Barrier_Social barrier_Cost"
+
+freq_job_survey <- freq_job_survey %>%
+  separate_wider_delim(id, delim = "_", names = c("bridge_barr", "code_cat", "code_name"))
+
+freq_job_survey$bridge_barr <- factor(freq_job_survey$bridge_barr, levels = c("Bridge", "Barrier"))
+
+#calculate proportions
+freq_job_survey2 <- freq_job_survey %>%
+  group_by(fish_ship, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(fish_ship, bridge_barr, code_cat) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(code_level = if_else(code_cat %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+                              if_else(code_cat %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+                              if_else(code_cat %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", 
+                              if_else(code_cat %in% c("Implementation bridge", "Implementation barrier"), "Implementation bridge or barrier", NA)))), 
+          id = paste(fish_ship, bridge_barr, code_cat)) %>%
+  distinct(id, .keep_all = TRUE)
+
+#stacked bar plots
+stack_survey <- ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
+    geom_bar(position="stack", stat="identity") +
+    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
+    facet_wrap(~bridge_barr) +
+    labs(fill = "Sub-theme") +
+    theme_ms() +
+    xlab("") + 
+    ylab("Proportion of theme (%)")
+
+#radar plots
+freq_job_survey3 <- freq_job_survey %>%
+  group_by(fish_ship, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(fish_ship, bridge_barr, code_name) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
+  distinct(id, .keep_all = TRUE) %>%
+  select(-c(id))
+
+top_survey <- freq_job_survey3 %>% group_by(fish_ship, bridge_barr) %>% arrange(desc(value)) %>% top_n(3) %>% ungroup()
+
+top_bridge <- top_survey %>% 
+  filter(bridge_barr == "Bridge") %>% 
+  pivot_wider(names_from = code_name, values_from = value) %>% 
+  select(-bridge_barr) %>%
+  mutate_all(~replace_na(., 0))
+
+top_barrier <- top_survey %>% 
+  filter(bridge_barr == "Barrier") %>% 
+  pivot_wider(names_from = code_name, values_from = value) %>% 
+  select(-bridge_barr) %>%
+  mutate_all(~replace_na(., 0))
+
+radar_br_survey <- ggradar::ggradar(top_bridge,
+        values.radar = c(0, 14, 22), 
+        background.circle.colour = "white",
+        axis.line.colour = "gray60",
+        gridline.min.colour = "gray60",
+        gridline.mid.colour = "gray60",
+        gridline.max.colour = "gray60",
+        group.colours = c("#F29325", "#007172"),
+        legend.position = "bottom", 
+        fill = TRUE, 
+        axis.label.size = 3.5)
+
+radar_ba_survey <- ggradar::ggradar(top_barrier,
+        values.radar = c(0, 17, 28), 
+        background.circle.colour = "white",
+        axis.line.colour = "gray60",
+        gridline.min.colour = "gray60",
+        gridline.mid.colour = "gray60",
+        gridline.max.colour = "gray60",
+        group.colours = c("#F29325", "#007172"),
+        legend.position = "none", 
+        fill = TRUE, 
+        axis.label.size = 3.5)
+
+stack_survey | radar_br_survey | radar_ba_survey
+```
+
 ## Result 4: Variations by position (survey only)

### 2025-09-28 reports/draft_results.qmd
assemble radar and stack

@@
 #| fig-align: center
+#| include: false
 
@@
 #stacked bar plots
-stack_survey <- ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
+ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
     geom_bar(position="stack", stat="identity") +
@@
     theme_ms() +
+    theme(legend.position = "right")+
     xlab("") + 
     ylab("Proportion of theme (%)")
+
+#ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))
 
@@
 
-top_survey <- freq_job_survey3 %>% group_by(fish_ship, bridge_barr) %>% arrange(desc(value)) %>% top_n(3) %>% ungroup()
+top_survey <- freq_job_survey3 %>% 
+                group_by(fish_ship, bridge_barr) %>% 
+                arrange(desc(value)) %>% 
+                top_n(3) %>% 
+                ungroup() %>%
+                select(code_name)
 
-top_bridge <- top_survey %>% 
+top_bridge <- freq_job_survey3 %>%
+  subset(code_name %in% top_survey$code_name) %>% 
   filter(bridge_barr == "Bridge") %>% 
@@
 
-top_barrier <- top_survey %>% 
+top_barrier <- freq_job_survey3 %>%
+  subset(code_name %in% top_survey$code_name) %>%
   filter(bridge_barr == "Barrier") %>% 
@@
 
-radar_br_survey <- ggradar::ggradar(top_bridge,
-        values.radar = c(0, 14, 22), 
+ggradar::ggradar(top_bridge,
+        values.radar = c(0, 16, 22), 
         background.circle.colour = "white",
@@
         fill = TRUE, 
-        axis.label.size = 3.5)
+        axis.label.size = 3)
 
-radar_ba_survey <- ggradar::ggradar(top_barrier,
+#ggsave("figures/ms_figs/industry/radar_br_survey.png", height = 8, width = 8, units = c("in"))
+
+ggradar::ggradar(top_barrier,
         values.radar = c(0, 17, 28), 
@@
         fill = TRUE, 
-        axis.label.size = 3.5)
+        axis.label.size = 3)
 
-stack_survey | radar_br_survey | radar_ba_survey
+#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
+
 ```
 
+::: panel-tabset
+
+#### Surveys
+
+![](images/survey_combo.png){fig-align="center" width="5in", height = "8in"}
+
+#### Literature
+
+:::
+
 ## Result 4: Variations by position (survey only)

### 2025-10-02 reports/draft_results.qmd
finish figure draft!

@@
 code_freq <- read.csv(here("data/code_freq_lit.csv"))
-codes_vars <- read.csv(here("data/code_w_vars_lit.csv"))
+code_vars <- read.csv(here("data/code_w_vars_lit.csv"))
 keywords <- read.csv(here("data/keywords.csv"))
@@
 
-code_ts <- codes_vars %>% 
+code_ts <- code_vars %>% 
   mutate(year = str_extract_all(Doc, "\\d+\\.?\\d*"), 
@@
 
-codes_vars$broad_location <- as.factor(codes_vars$broad_location)
-codes_LU <- codes_vars[!duplicated(codes_vars$Lit_unit), ]
+code_vars$broad_location <- as.factor(code_vars$broad_location)
+codes_LU <- code_vars[!duplicated(code_vars$Lit_unit), ]
 
@@
 #| include: false
+
+#survey figs
 
@@
 
+#get sample sizes of survey respondants by position
+n_job_survey <- code_vars_s %>% 
+  select(c(1, 21:54)) %>% 
+  janitor::clean_names()
+
+table(n_job_survey$survey)
+
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+#| include: false
+
+#literature figs
+
+#format data
+freq_job_lit <- code_vars %>% 
+  select(c(1, 27:29, 33:60)) %>%
+  janitor::clean_names() %>%
+  pivot_longer(2:4, names_to = "test", values_to = "fish_ship") %>%
+  select(-c(test)) %>%
+  pivot_longer(2:29, names_to = "sub_theme", values_to = "total") %>%
+  group_by(fish_ship, sub_theme) %>%
+  summarise(total = sum(total), 
+            .groups = "drop") %>%
+  filter(fish_ship == "Bycatch" | fish_ship == "Ship strikes" | fish_ship == "Overfishing" | fish_ship == "Entanglement" | fish_ship == "Avoid fisheries discharge")
+
+lib_job_lit <- code_freq %>%
+  mutate(id = paste(bridge_barr, code_cat, code_name, sep = "_")) %>% 
+  select(id)
+
+freq_job_lit$id <- NA
+for(i in 1:nrow(freq_job_lit)){
+  curr_code = freq_job_lit$sub_theme[i]
+  curr_id = lib_job_lit$id[agrepl(curr_code, lib_job_lit$id, 10)] #6 refers to the number of characters that can be diff
+
+  freq_job_lit$id[i] <- curr_id
+
+}
+
+freq_job_lit$id[freq_job_lit$sub_theme == "abiotic_data_availability"] <- "Bridge_Data bridge_Abiotic data availability"
+freq_job_lit$id[freq_job_lit$sub_theme == "abiotic_indicators_of_target_species_presence"] <- 
+"Bridge_Ecological bridge_Abiotic indicators of target species presence"
+freq_job_lit$id[freq_job_lit$sub_theme == "cost"] <- 
+"Barrier_Social barrier_Cost"
+freq_job_lit$id[freq_job_lit$sub_theme == "discontinuity"] <- 
+"Barrier_Social barrier_Discontinuity"
+freq_job_lit$id[freq_job_lit$sub_theme == "feasibility"] <- 
+"Bridge_Social bridge_Feasibility"
+freq_job_lit$id[freq_job_lit$sub_theme == "model_abuse"] <- 
+"Barrier_Data barrier_Model abuse"
+freq_job_lit$id[freq_job_lit$sub_theme == "resource_availability"] <- 
+"Bridge_Social bridge_Resource availability"
+
+freq_job_lit <- freq_job_lit %>%
+  separate_wider_delim(id, delim = "_", names = c("bridge_barr", "code_cat", "code_name"))
+
+freq_job_lit$bridge_barr <- factor(freq_job_lit$bridge_barr, levels = c("Bridge", "Barrier"))
+
+freq_job_lit <- freq_job_lit %>%
+  mutate(fish_ship = ifelse(fish_ship == "Ship strikes", "Shipping", "Fishing"))
+
+#calculate proportions
+freq_job_lit2 <- freq_job_lit %>%
+  group_by(fish_ship, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(fish_ship, bridge_barr, code_cat) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(code_level = if_else(code_cat %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+                              if_else(code_cat %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+                              if_else(code_cat %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA))), 
+          id = paste(fish_ship, bridge_barr, code_cat)) %>%
+  distinct(id, .keep_all = TRUE)
+
+#stacked bar plots
+ggplot(freq_job_lit2, aes(fill=code_level, y=value, x=fish_ship)) + 
+    geom_bar(position="stack", stat="identity") +
+    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","#45818E")) +
+    facet_wrap(~bridge_barr) +
+    labs(fill = "Sub-theme") +
+    theme_ms() +
+    theme(legend.position = "right")+
+    xlab("") + 
+    ylab("Proportion of theme (%)")
+
+#ggsave("figures/ms_figs/industry/stack_lit.png", width = 7, height = 6, units = c("in"))
+
+#radar plots
+freq_job_lit3 <- freq_job_lit %>%
+  group_by(fish_ship, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(fish_ship, bridge_barr, code_name) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
+  distinct(id, .keep_all = TRUE) %>%
+  select(-c(id))
+
+top_lit <- freq_job_lit3 %>% 
+                group_by(fish_ship, bridge_barr) %>% 
+                arrange(desc(value)) %>% 
+                top_n(3) %>% 
+                ungroup() %>%
+                select(code_name)
+
+top_bridge <- freq_job_lit3 %>%
+  subset(code_name %in% top_lit$code_name) %>% 
+  filter(bridge_barr == "Bridge") %>% 
+  pivot_wider(names_from = code_name, values_from = value) %>% 
+  select(-bridge_barr) %>%
+  mutate_all(~replace_na(., 0))
+
+top_barrier <- freq_job_lit3 %>%
+  subset(code_name %in% top_lit$code_name) %>%
+  filter(bridge_barr == "Barrier") %>% 
+  pivot_wider(names_from = code_name, values_from = value) %>% 
+  select(-bridge_barr) %>%
+  mutate_all(~replace_na(., 0))
+
+ggradar::ggradar(top_bridge,
+        values.radar = c(0, 8, 16), 
+        background.circle.colour = "white",
+        axis.line.colour = "gray60",
+        gridline.min.colour = "gray60",
+        gridline.mid.colour = "gray60",
+        gridline.max.colour = "gray60",
+        group.colours = c("#F29325", "#007172"),
+        legend.position = "bottom", 
+        fill = TRUE, 
+        axis.label.size = 3)
+
+#ggsave("figures/ms_figs/industry/radar_br_lit.png", height = 8, width = 8, units = c("in"))
+
+ggradar::ggradar(top_barrier,
+        values.radar = c(0, 17, 37), 
+        background.circle.colour = "white",
+        axis.line.colour = "gray60",
+        gridline.min.colour = "gray60",
+        gridline.mid.colour = "gray60",
+        gridline.max.colour = "gray60",
+        group.colours = c("#F29325", "#007172"),
+        legend.position = "none", 
+        fill = TRUE, 
+        axis.label.size = 3)
+
+#ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
+
+#get sample sizes of survey respondants by position
+n_job_lit <- code_vars %>% 
+  select(c(1, 27:29, 33:60)) %>%
+  janitor::clean_names()  %>%
+  pivot_longer(2:4, names_to = "test", values_to = "fish_ship") %>%
+  select(-c(test)) %>%
+  filter(fish_ship == "Bycatch" | fish_ship == "Ship strikes" | fish_ship == "Overfishing" | fish_ship == "Entanglement" | fish_ship == "Avoid fisheries discharge") %>%
+  mutate(fish_ship = ifelse(fish_ship == "Ship strikes", "Shipping", "Fishing"))
+
+table(n_job_lit$fish_ship)
+
 ```
@@
 ::: panel-tabset
+
+#### Literature
+
+![](images/lit_combo.png){fig-align="center" width="5in", height = "8in"}
 
@@
 
-#### Literature
-
 :::
@@
 ## Result 4: Variations by position (survey only)
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 10
+#| fig-height: 7
+#| fig-align: center
+#| include: false
+
+#survey figs
+
+#format data
+freq_pos_survey <- code_vars_s %>% 
+  select(c(6:10, 21:54)) %>% 
+  janitor::clean_names() %>%
+  pivot_longer(1:5, names_to = "test", values_to = "position") %>%
+  select(-c(test)) %>%
+  pivot_longer(1:34, names_to = "sub_theme", values_to = "total") %>%
+  group_by(position, sub_theme) %>%
+  summarise(total = sum(total), 
+            .groups = "drop") %>%
+  drop_na(position)
+
+lib_job_survey <- code_freq_s %>%
+  mutate(id = paste(bridge_barr, code_cat, code_name, sep = "_")) %>% 
+  select(id)
+
+freq_pos_survey$id <- NA
+for(i in 1:nrow(freq_pos_survey)){
+  curr_code = freq_pos_survey$sub_theme[i]
+  curr_id = lib_job_survey$id[agrepl(curr_code, lib_job_survey$id, 6)]
+
+  freq_pos_survey$id[i] <- curr_id
+
+}
+
+freq_pos_survey$id[freq_pos_survey$sub_theme == "stigmatization"] <- "Barrier_Social barrier_Stigmatization"
+freq_pos_survey$id[freq_pos_survey$sub_theme == "cost"] <- "Barrier_Social barrier_Cost"
+
+freq_pos_survey <- freq_pos_survey %>%
+  separate_wider_delim(id, delim = "_", names = c("bridge_barr", "code_cat", "code_name"))
+
+freq_pos_survey$bridge_barr <- factor(freq_pos_survey$bridge_barr, levels = c("Bridge", "Barrier"))
+
+#calculate proportions
+freq_pos_survey2 <- freq_pos_survey %>%
+  group_by(position, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
+  group_by(position, bridge_barr, code_cat) %>% 
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(code_level = if_else(code_cat %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+                              if_else(code_cat %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+                              if_else(code_cat %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", 
+                              if_else(code_cat %in% c("Implementation bridge", "Implementation barrier"), "Implementation bridge or barrier", NA)))), 
+          id = paste(position, bridge_barr, code_cat)) %>%
+  distinct(id, .keep_all = TRUE)
+
+#stacked bar plots
+ggplot(freq_pos_survey2, aes(fill=code_level, y=value, x=position)) + 
+    geom_bar(position="stack", stat="identity") +
+    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
+    facet_wrap(~bridge_barr) +
+    labs(fill = "Sub-theme") +
+    theme_ms() +
+    theme(legend.position = "top")+
+    xlab("") + 
+    ylab("Proportion of theme (%)")+
+    theme(axis.text.x = element_text(size = 14, color = "black", angle = 60, hjust = 1))
+
+#ggsave("figures/ms_figs/position/stack_survey.png", width = 10, height = 8, units = c("in"))
+
+#get sample sizes of survey respondants by position
+n_pos_survey <- code_vars_s %>% 
+  select(c(6:10, 21:54)) %>% 
+  janitor::clean_names() %>%
+  pivot_longer(1:5, names_to = "test", values_to = "position") %>%
+  select(-c(test)) %>%
+  drop_na(position)
+
+table(n_pos_survey$position)
+
+```
+
+![](images/position.png){fig-align="center" width="8in", height = "6in"}

### 2025-10-08 reports/draft_results.qmd
update figs

@@
 #| warning: false
-#| fig-width: 9
-#| fig-height: 5.5
+#| fig-width: 10
+#| fig-height: 5
 #| fig-align: center
@@
     facet_wrap(~bridge_barr) +
-    labs(fill = "Sub-theme") +
+    labs(fill = "") +
+    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
     theme_ms() +
-    theme(legend.position = "right")+
+    theme(legend.position = "top", 
+          legend.justification = "left", 
+          legend.text = element_text(size = 14, color = "black"))+
     xlab("") + 
@@
     facet_wrap(~bridge_barr) +
-    labs(fill = "Sub-theme") +
+    labs(fill = "") +
+    guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
     theme_ms() +
-    theme(legend.position = "right")+
+    theme(legend.position = "top", 
+          legend.justification = "left", 
+          legend.text = element_text(size = 14, color = "black")) +
     xlab("") + 
@@
     facet_wrap(~bridge_barr) +
-    labs(fill = "Sub-theme") +
+    labs(fill = "") +
     theme_ms() +
-    theme(legend.position = "top")+
+    theme(legend.position = "top", 
+          legend.justification.top = "left", 
+          legend.title = element_text(size = 16, color = "black"), 
+          legend.text = element_text(size = 14, color = "black"))+
+    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
     xlab("") + 

### 2025-10-15 reports/draft_results.qmd
update from props

@@
 
-![](images/bridges_old.png){fig-align="center" width="70%"}
-
-![](images/barriers_old.png){fig-align="center" width="70%"}
+![](images/sunburst.png){fig-align="center" width="100%"}
 
@@
 
-Code appearance frequencies across all bridge **OR** barrier codes. The proportions reported in these figures represent the percent of codes that theme or sub-theme comprises.
+Code appearance counts across all bridge **OR** barrier codes. The values represent counts of themes or sub-themes.
 
@@
   code_sum <- code_freq %>%
-  group_by(bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(code_cat) %>% 
-  mutate(n_subtotal = sum(total)) %>%
-  summarise(value = n_subtotal/n_total) %>%
+  #mutate(n_total = sum(total)) %>%
+  #group_by(code_cat) %>% 
+  #mutate(n_subtotal = sum(total)) %>%
+  #summarise(value = n_subtotal/n_total) %>%
   rename("br_ba" = code_cat) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 1), 
-         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", value, -value),
-         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
-                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA))), 
+  # mutate(percent_label = scales::percent(value, accuracy = 1), 
+  #        percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", value, -value),
+  #        code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
+  #                             if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
+  #                             if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", NA))), 
+  #        code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge"), "bridge", "barrier")) %>%
+  mutate(percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier", -total, total),
+         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological", 
+                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data",
+                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social", NA))), 
          code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge"), "bridge", "barrier")) %>%
-  group_by(code_level) %>%
+  group_by(code_brba, code_level) %>%
+  summarize(value = sum(percent)) %>%
+  mutate(value_label = ifelse(code_brba == "barrier", value*-1, value)) %>%
   distinct()
 
-code_sum$code_level <- factor(code_sum$code_level, levels = c("Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier"))
-code_sum$code_brba <- factor(code_sum$code_brba, levels = c("bridge", "barrier"))
+code_sum$code_level <- factor(code_sum$code_level, levels = c("Social", "Ecological", "Data"))
+code_sum$code_brba <- factor(code_sum$code_brba, levels = c("barrier", "bridge"))
 
 ggplot(code_sum, aes(x = code_level, 
-             y = percent,
+             y = value,
              fill = code_brba)) +
   geom_col(width = 0.7) +
-  geom_text(aes(label = percent_label),
-            position = position_stack(vjust = 0.65),
+  geom_text(aes(label = value_label),
+            position = position_stack(vjust = 0.5),
             color = "black", 
             size = 5) +
-  ylim(-0.4,0.7)+
+  #ylim(-0.4,0.7)+
   coord_flip() +
   scale_x_discrete() +
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Barrier", "Bridge")) +
   theme_minimal() +
@@
         panel.grid = element_blank(),
-        legend.position = c(-0.17, 0.99),
+        legend.position = c(-0.05, 1),
         legend.text = element_text(size = 16, color = "black"),
@@
 
-#ggsave("figures/ms_figs/all_freq/all_freq.png", width = 8, height = 5, units = ("in"))
+#ggsave("figures/ms_figs/all_freq/all_freq.png", width = 8, height = 6, units = ("in"))
+#ggsave("figures/slides_svg/freq_lit.svg", width = 8, height = 6, units = ("in"))
 ```
@@
   filter(bridge_barr == "Bridge") %>%
-  mutate(n_total = sum(total)) %>%
-  group_by(code_cat, code_name) %>%
-  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
-  mutate(percent = scales::percent(value, accuracy = 1), 
+  #mutate(n_total = sum(total)) %>%
+  #group_by(code_cat, code_name) %>%
+  #summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
+  mutate(#percent = scales::percent(value, accuracy = 1), 
          code_name = factor(code_name)) %>%
@@
   group_by(code_cat) %>%
-  arrange(code_name, desc(percent))
+  arrange(code_name, desc(total))
 
 #plot
-br_freq <- ggplot(code_sum_br, aes(x = value*100, y = reorder(code_name, value))) + 
-  geom_point(size = 5, color = "goldenrod") + 
+br_freq <- ggplot(code_sum_br, aes(x = total, y = reorder(code_name, total))) + 
+  geom_point(size = 5, color = "lightskyblue3") + 
   # scale_x_continuous(limits = c(0, 30), 
@@
   facet_wrap("code_cat", ncol = 1, scales = "free_y") +
-  scale_x_reverse(limits = c(30, 0), 
+  scale_x_continuous(limits = c(0, 75), 
                   #breaks = seq(0, 30, 5), 
-                  name = "Percent appearance (%)")+
+                  name = "Sub-theme count (#)")+
+  scale_y_discrete(position = "right") +
   theme(strip.placement = "outside",
@@
   filter(bridge_barr == "Barrier") %>%
-  mutate(n_total = sum(total)) %>%
-  group_by(code_cat, code_name) %>%
-  summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
-  mutate(percent = scales::percent(value, accuracy = 1), 
+  #mutate(n_total = sum(total)) %>%
+  #group_by(code_cat, code_name) %>%
+  #summarise(value = total/n_total) %>% #percentages represent total number of bridge or barriers codes that code represents
+  mutate(#percent = scales::percent(value, accuracy = 1), 
          code_name = factor(code_name)) %>%
@@
   group_by(code_cat) %>%
-  arrange(code_name, desc(percent))
+  arrange(code_name, desc(total))
 
 #plot
-ba_freq <- ggplot(code_sum_ba, aes(x = value*100, y = reorder(code_name, value))) + 
-  geom_point(size = 5, color = "lightskyblue3") + 
-  scale_x_continuous(limits = c(0, 30), 
-                     breaks = seq(0, 30, 10), 
-                     name = "Percent appearance (%)") +
-  scale_y_discrete(position = "right") +
+ba_freq <- ggplot(code_sum_ba, aes(x = total, y = reorder(code_name, total))) + 
+  geom_point(size = 5, color = "goldenrod") + 
+  scale_x_reverse(limits = c(75, 0), 
+                     breaks = seq(0,60, 20), 
+                     name = "Sub-theme count (#)") +
   theme_minimal() +
@@
 
-#ggsave("figures/ms_figs/all_freq/ba_freq.png", width = 8, height = 8, units = c("in"))
+#ggsave("figures/ms_figs/all_freq/ba_freq.png", width = 7.5, height = 8, units = c("in"))
 
@@
  code_sum_s <- code_freq_s %>%
-  group_by(bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(code_cat) %>% 
-  mutate(n_subtotal = sum(total)) %>%
-  summarise(value = n_subtotal/n_total) %>%
   rename("br_ba" = code_cat) %>%
-  mutate(percent_label = scales::percent(value, accuracy = 1), 
-         percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Implementation barrier", value, -value),
-         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
-                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
-                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", 
-                              if_else(br_ba %in% c("Implementation bridge", "Implementation barrier"), "Implementation bridge or barrier", NA)))), 
+  mutate(percent = if_else(br_ba == "Data barrier" | br_ba == "Ecological barrier" | br_ba == "Social barrier" | br_ba == "Implementation barrier", -total, total),
+         code_level = if_else(br_ba %in% c("Ecological barrier", "Ecological bridge"), "Ecological", 
+                              if_else(br_ba %in% c("Data barrier", "Data bridge"), "Data",
+                              if_else(br_ba %in% c("Implementation barrier", "Implementation bridge"), "Implementation",
+                              if_else(br_ba %in% c("Social barrier", "Social bridge"), "Social", NA)))),
          code_brba = if_else(br_ba %in% c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge"), "bridge", "barrier")) %>%
-  group_by(code_level) %>%
+  group_by(code_brba, code_level) %>%
+  summarize(value = sum(percent)) %>%
+  mutate(value_label = ifelse(code_brba == "barrier", value*-1, value)) %>%
   distinct()
 
-code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Implementation bridge or barrier", "Social bridge or barrier", "Ecological bridge or barrier", "Data bridge or barrier"))
-code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("bridge", "barrier"))
+code_sum_s$code_level <- factor(code_sum_s$code_level, levels = c("Implementation", "Social", "Ecological", "Data"))
+code_sum_s$code_brba <- factor(code_sum_s$code_brba, levels = c("barrier", "bridge"))
 
 all_freq_survey <- ggplot(code_sum_s, aes(x = code_level, 
-             y = percent,
+             y = value,
              fill = code_brba)) +
   geom_col(width = 0.7) +
-  geom_text(aes(label = percent_label),
-            position = position_stack(vjust = 0.65),
+  geom_text(aes(label = value_label),
+            position = position_stack(vjust = 0.5),
             color = "black", 
             size = 5) +
-  ylim(-0.55,0.7)+
+  #ylim(-0.55,0.7)+
   coord_flip() +
   scale_x_discrete() +
-  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Bridge frequency", "Barrier frequency")) +
+  scale_fill_manual(values = c("goldenrod", "lightskyblue3"), labels = c("Barrier", "Bridge")) +
   theme_minimal() +
@@
         axis.text.x =element_blank(),
-        axis.text.y = element_text(size = 26, color = "black"),
+        axis.text.y = element_text(size = 20, color = "black"),
         panel.grid = element_blank(),
-        legend.position = c(-0.17, 0.99),
-        legend.text = element_text(size = 20, color = "black"),
-        strip.text.y.right = element_text(angle = 0, size = 18)) +
+        legend.position = c(-0.05, 1),
+        legend.text = element_text(size = 16, color = "black"),
+        strip.text.y.right = element_text(angle = 0, size = 16)) +
   geom_hline(yintercept = 0.0, linewidth = 1) + 
@@
 
-#ggsave("figures/ms_figs/all_freq/all_freq_survey.png", width = 13, height = 8, units = ("in"))
+#ggsave("figures/ms_figs/all_freq/all_freq_survey.png", width = 8, height = 6, units = ("in"))
+#ggsave("figures/slides_svg/freq_survey.svg", width = 8, height = 6, units = ("in"))
 
@@
   group_by(code_cat) %>%
-  arrange(code_name, desc(percent))
+  arrange(code_name, desc(total))
 
 #plot
-br_freq_s <- ggplot(code_sum_br_s, aes(x = value*100, y = reorder(code_name, value))) + 
-  geom_point(size = 5, color = "goldenrod") + 
+br_freq_s <- ggplot(code_sum_br_s, aes(x = total, y = reorder(code_name, total))) + 
+  geom_point(size = 5, color = "lightskyblue3") + 
   # scale_x_continuous(limits = c(0, 30), 
@@
   facet_wrap("code_cat", ncol = 1, scales = "free_y") +
-  scale_x_reverse(limits = c(20, 0), 
+  scale_x_continuous(limits = c(0, 20), 
                   #breaks = seq(0, 30, 5), 
-                  name = "Percent appearance (%)")+
+                  name = "Sub-theme count (#)")+
+  scale_y_discrete(position = "right") +
   theme(strip.placement = "outside",
@@
   group_by(code_cat) %>%
-  arrange(code_name, desc(percent))
+  arrange(code_name, desc(total))
 
 #plot
-ba_freq_s <- ggplot(code_sum_ba_s, aes(x = value*100, y = reorder(code_name, value))) + 
-  geom_point(size = 5, color = "lightskyblue3") + 
-  scale_x_continuous(limits = c(0, 20), 
-                     breaks = seq(0, 20, 10), 
-                     name = "Percent appearance (%)") +
-  scale_y_discrete(position = "right") +
+ba_freq_s <- ggplot(code_sum_ba_s, aes(x = total, y = reorder(code_name, total))) + 
+  geom_point(size = 5, color = "goldenrod") + 
+  scale_x_reverse(limits = c(20, 0), 
+                     breaks = seq(0, 20, 5), 
+                     name = "Sub-theme count (#)") +
   theme_minimal() +
@@
   theme(strip.placement = "outside",
-        strip.text = element_text(face = "bold", size = 16, hjust = 1), 
+        strip.text = element_text(face = "bold", size = 14, hjust = 1), 
         axis.text = element_text(size = 12, color = "black"), 
@@
 
-#ggsave("figures/ms_figs/all_freq/ba_freq_survey.png", width = 6, height = 9, units = c("in"))
+#ggsave("figures/ms_figs/all_freq/ba_freq_survey.png", width = 6, height = 8, units = c("in"))
 
@@
 theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]), 
-      panel.background = element_blank())+
+      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]))+
 geom_text(aes(label = total))+
@@
 #| warning: false
-#| fig-width: 10
+#| fig-width: 9
 #| fig-height: 5
@@
   gather(col, consv_topic, reason1:reason3) %>%
-  subset(select = consv_topic)
+  select(consv_topic)
 
@@
 consv_bar
+
+consv <- codes_LU %>%
+  gather(col, consv_topic, reason1:reason3) %>%
+  gather(test, fishery_channel, fishery_or_channel1:fishery_or_channel4) %>%
+  select(c(consv_topic, fishery_channel)) %>%
+  mutate(consv_bin = paste0(consv_topic, " - ", fishery_channel))
+
+consv_s <- consv %>%
+  group_by(consv_topic, consv_bin) %>%
+  filter(consv_topic != "NA") %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(perc = count/sum(count)*100)
+
+consv_bar2 <- ggplot(consv_s) +
+  geom_bar(aes(x = perc, y = reorder(consv_bin, perc), fill = consv_topic), width = 0.6, stat = "identity")+
+  scale_x_continuous(position = "top", 
+                     expand = c(0,0), 
+                     limits = c(0, 45))+
+  scale_y_discrete(expand = expansion(add = c(0,0))) + 
+  theme(
+    # Set background color to white
+    panel.background = element_rect(fill = "white"),
+    # Set the color and the width of the grid lines for the horizontal axis
+    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
+    # Remove tick marks by setting their length to 0
+    axis.ticks.length = unit(0, "mm"),
+    # Remove the title for both axes
+    axis.title = element_blank(),
+    # Only left line of the vertical axis is painted in black
+    axis.line.y.left = element_line(color = "black"),
+    # Remove labels from the vertical axis
+    axis.text.y = element_blank(),
+    # But customize labels for the horizontal axis
+    axis.text.x = element_text(family = "Arial", size = 12)) + 
+  geom_text(aes(x = perc, y = consv_bin, label = consv_bin),
+    hjust = 0,
+    nudge_x = 0.3,
+    colour = "dodgerblue4",
+    family = "Arial",
+    size = 3.5)+
+  labs(subtitle = "Percent of sum from all articles (%)") + 
+  theme(plot.subtitle = element_text(
+      family = "Arial",
+      size = 13)
+  )
+
+consv_bar2
 ```
@@
 #ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))
+#ggsave("figures/slides_svg/stack_survey.svg", width = 7, height = 6, units = c("in"))
 
@@
 freq_job_survey3 <- freq_job_survey %>%
-  group_by(fish_ship, bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(fish_ship, bridge_barr, code_name) %>% 
-  mutate(n_subtotal = sum(total)) %>%
-  reframe(value = (n_subtotal/n_total)*100) %>%
-  ungroup() %>%
+  # group_by(fish_ship, bridge_barr) %>%
+  # mutate(n_total = sum(total)) %>%
+  # ungroup() %>%
+  # group_by(fish_ship, bridge_barr, code_name) %>%
+  # mutate(n_subtotal = sum(total)) %>%
+  # reframe(value = (n_subtotal/n_total)*100) %>%
+  # ungroup() %>%
   mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
   distinct(id, .keep_all = TRUE) %>%
-  select(-c(id))
+  select(-c(id)) %>%
+  group_by(fish_ship, bridge_barr, code_name) %>%
+  summarise(value = sum(total))
 
@@
 top_bridge <- freq_job_survey3 %>%
+  ungroup() %>%
   subset(code_name %in% top_survey$code_name) %>% 
@@
 top_barrier <- freq_job_survey3 %>%
+  ungroup() %>%
   subset(code_name %in% top_survey$code_name) %>%
@@
 ggradar::ggradar(top_bridge,
-        values.radar = c(0, 16, 22), 
+        values.radar = c(0, 2, 4), 
         background.circle.colour = "white",
@@
         gridline.max.colour = "gray60",
-        group.colours = c("#F29325", "#007172"),
+        group.colours = c("#F29325", "#007172"),#007172
         legend.position = "bottom", 
@@
 #ggsave("figures/ms_figs/industry/radar_br_survey.png", height = 8, width = 8, units = c("in"))
+#ggsave("figures/slides_svg/radar_br.svg", height = 8, width = 8, units = c("in"))
 
 ggradar::ggradar(top_barrier,
-        values.radar = c(0, 17, 28), 
+        values.radar = c(0, 1, 3), 
         background.circle.colour = "white",
@@
         gridline.max.colour = "gray60",
-        group.colours = c("#F29325", "#007172"),
+        group.colours = c("#F29325", "#007172"),#007172
         legend.position = "none", 
@@
 #ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
+#ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))
 
@@
 freq_job_lit3 <- freq_job_lit %>%
-  group_by(fish_ship, bridge_barr) %>%
-  mutate(n_total = sum(total)) %>%
-  ungroup() %>%
-  group_by(fish_ship, bridge_barr, code_name) %>% 
-  mutate(n_subtotal = sum(total)) %>%
-  reframe(value = (n_subtotal/n_total)*100) %>%
-  ungroup() %>%
+  # group_by(fish_ship, bridge_barr) %>%
+  # mutate(n_total = sum(total)) %>%
+  # ungroup() %>%
+  # group_by(fish_ship, bridge_barr, code_name) %>% 
+  # mutate(n_subtotal = sum(total)) %>%
+  # reframe(value = (n_subtotal/n_total)*100) %>%
+  # ungroup() %>%
   mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
   distinct(id, .keep_all = TRUE) %>%
-  select(-c(id))
+  select(-c(id)) %>%
+  group_by(fish_ship, bridge_barr, code_name) %>%
+  summarise(value = sum(total))
 
@@
   pivot_wider(names_from = code_name, values_from = value) %>% 
+  ungroup() %>%
   select(-bridge_barr) %>%
@@
 ggradar::ggradar(top_bridge,
-        values.radar = c(0, 8, 16), 
+        values.radar = c(0, 15, 30), 
         background.circle.colour = "white",
@@
 ggradar::ggradar(top_barrier,
-        values.radar = c(0, 17, 37), 
+        values.radar = c(0, 15, 30), 
         background.circle.colour = "white",

### 2025-10-15 reports/draft_results.qmd
math error oops

@@
   # ungroup() %>%
-  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
-  distinct(id, .keep_all = TRUE) %>%
-  select(-c(id)) %>%
+  #mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
+  #distinct(id, .keep_all = TRUE) %>%
+  #select(-c(id))
   group_by(fish_ship, bridge_barr, code_name) %>%
@@
 ggradar::ggradar(top_bridge,
-        values.radar = c(0, 2, 4), 
+        values.radar = c(0, 5, 10), 
         background.circle.colour = "white",
@@
 ggradar::ggradar(top_barrier,
-        values.radar = c(0, 1, 3), 
+        values.radar = c(0, 3, 6), 
         background.circle.colour = "white",
@@
   # ungroup() %>%
-  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
-  distinct(id, .keep_all = TRUE) %>%
-  select(-c(id)) %>%
+  # mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
+  # distinct(id, .keep_all = TRUE) %>%
+  # select(-c(id)) %>%
   group_by(fish_ship, bridge_barr, code_name) %>%
@@
 ggradar::ggradar(top_bridge,
-        values.radar = c(0, 15, 30), 
+        values.radar = c(0, 20, 40), 
         background.circle.colour = "white",
@@
 ggradar::ggradar(top_barrier,
-        values.radar = c(0, 15, 30), 
+        values.radar = c(0, 15, 35), 
         background.circle.colour = "white",
@@
 
-#ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
+ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
 

### 2025-10-15 reports/draft_results.qmd
update figs

@@
 
-Here I've presented three options for presenting the themes and sub-themes identified in the review and surveys.
-I'd love feedback on which option or combination of options best visualize the codes!
-Depending on your feedback, I'll then spend time cleaning up the best option.
-
-### Option 1 - Sankey diagram
-
-Plot below only presents the review themes and sub-themes. If this is the best way to communicate the codes, I will add a diagram visualizing the survey codes.
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| include: false
 #| fig-width: 15
@@
 
-### Option 2 - Sunburst figure
-
-Plots below are from an old draft of the review themes and sub-themes. If this is the nicest way to plot the codes, I will update the diagram and generate one for the survey themes as well.
+### Sunburst figure
+
+Visualizes each of the themes (Data, Ecological, Social, and Implementation) identified in the literature and surveys.
+Also visualizes the sub-themes within each theme bin.
+Literature themes are on top while surveys are on the bottom.
+Cooler colors indicate bridges while warmer ones represent barriers.
+The small text/poor resolution should be resolved when the figure is viewed as a pdf!
 
@@
 
-### Option 3 - Table
+### Table
+
+May include in the supplemental, but could be redundant to the sunburst diagram.
 
@@
 :::
-
-### Result 2.2: Time series of top theme from literature, co-management
-
-Grey is the number of DOM publications per year, while blue is the number of times co-management and communication was referenced.
-Whanted to see if this code was referenced more over time, but seems that it just tracks the number of DOM publications.
-Likely won't include.
 
@@
 consv_bar
-
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| fig-width: 9
+#| fig-height: 10
+#| fig-align: center
 consv <- codes_LU %>%
@@
 
-ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
+#("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
 

### 2025-10-15 reports/draft_results.qmd
update results doc

@@
 
-### Result 2.3: Heat maps of theme co-occurence
+### Result 2.2: Heat maps of theme co-occurence
 
@@
 #| warning: false
-#| fig-width: 9
-#| fig-height: 5
+#| fig-width: 10
+#| fig-height: 4
 #| fig-align: center
@@
 #| fig-width: 9
-#| fig-height: 10
+#| fig-height: 12
 #| fig-align: center

### 2025-10-21 reports/draft_results.qmd
heatmap revise

@@
 code_rel <- read.csv(here("data/code_rel.csv"))
+code_rel2 <- read.csv(here("data/br_ba_code_lit.csv"))
 
@@
 code_freq_s <- read.csv(here("data/surveys/code_freq.csv"))
+code_rel_s <- read.csv(here("data/surveys/br_ba_code_survey.csv"))
 
@@
 This heatmap represents number of times two codes co-occurered together in the same article, or "theme co-occurence".
-I have filtered totals greater than or equal to 11, which was the 90% quantile of the co-occurrence total data set.
-Blue text represents data bridges and barriers, grey text represents ecological bridges and barriers, and orange text represents social bridges and barriers.
+Bridges are placed on rows and barriers are separated by columns.
+Literature codes are on the top and survey codes are on the bottom.
 
@@
 
-code_rel_melt <- reshape::melt(code_rel)
+#literature
+code_rel_melt <- reshape::melt(code_rel2)
 code_rel_melt$variable <- gsub(".", " ", code_rel_melt$variable, fixed = TRUE)
@@
 code_rel_melt2 <- code_rel_melt
-code_rel_melt2$brba_code2 <- NA
+#code_rel_melt2$brba_code2 <- NA
 
@@
 
-for(i in 1:nrow(code_rel_melt2)){
-  code_temp = code_rel_melt2$code2[i]
-
-  brba_temp = code_rel_melt2 %>% filter(code1 == code_temp & code2 == code_temp)
-  brba_code_temp = brba_temp$brba_code1[1]
-
-  code_rel_melt2$brba_code2[i] <- brba_code_temp
-}
-
-code_rel_melt2$brba_code2[code_rel_melt2$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
-
-group_colors = c("Data Bridge" = "dodgerblue4", "Data Barrier" = "dodgerblue4", "Ecological Bridge" = "honeydew4", "Ecological Barrier" = "honeydew4", "Social Bridge" = "darkorange4", "Social Barrier" = "darkorange4")
+# for(i in 1:nrow(code_rel_melt2)){
+#   code_temp = code_rel_melt2$code2[i]
+# 
+#   brba_temp = code_rel_melt2 %>% filter(code1 == code_temp & code2 == code_temp)
+#   brba_code_temp = brba_temp$brba_code1[1]
+# 
+#   code_rel_melt2$brba_code2[i] <- brba_code_temp
+# }
+# 
+# code_rel_melt2$brba_code2[code_rel_melt2$code2 == "Target species is a prey specialist"] <- "Ecological bridge"
+
+# group_colors = c("Data Bridge" = "dodgerblue4", "Data Barrier" = "dodgerblue4", "Ecological Bridge" = "honeydew4", "Ecological Barrier" = "honeydew4", "Social Bridge" = "darkorange4", "Social Barrier" = "darkorange4")
 
 code_rel_melt_h <- code_rel_melt2 %>%
-  filter(total >= 11) %>%
-  mutate(bor_box = ifelse(total >= 11, "TRUE", "FALSE"), 
-        bor_box = as.factor(bor_box), 
+  #filter(total >= 11) %>%
+  mutate(#bor_box = ifelse(total >= 11, "TRUE", "FALSE"), 
+        #bor_box = as.factor(bor_box), 
         code1 = as.factor(code1), 
@@
 
-code_rel_melt_h$bor_box <- factor(code_rel_melt_h$bor_box, levels = c("TRUE", "FALSE"))
-
-code_rel_melt_h <- code_rel_melt_h %>%
-  mutate(code1 = reorder(code1, -total, FUN = mean),
-         code2 = reorder(code2, total, FUN = mean))
-
-unique_x_groups <- code_rel_melt_h %>%
-distinct(code1, brba_code1) %>%
-arrange(code1)
-
-unique_y_groups <- code_rel_melt_h %>%
-distinct(code2, brba_code2) %>%
-arrange(code2)
-
-x_colors <- setNames(group_colors[unique_x_groups$brba_code1], unique_x_groups$code1)
-y_colors <- setNames(group_colors[unique_y_groups$brba_code2], unique_y_groups$code2)
-
-ggplot(code_rel_melt_h, aes(x = code1, y = reorder(code2, total))) +
-geom_tile(aes(fill = total, colour = bor_box)) + 
+code_rel_melt_h$code1 <- factor(code_rel_melt_h$code1, levels = c(as.character(unique(code_rel_melt_h$code1))))
+
+code_rel_melt_h$code2 <- factor(code_rel_melt_h$code2, levels =
+c("Need for multispecies management",	"Implementation costs",	"Indirect socioeconomic consequences",	"Discontinuity",	"Poor communication and outreach",	"Poor program implementation", "Model abuse", "Gaps and inaccuracy", "Climate change adding uncertainty to target species habitat use",	"Management scales do not align with system needs"))
+
+#code_rel_melt_h$bor_box <- factor(code_rel_melt_h$bor_box, levels = c("TRUE", "FALSE"))
+
+# code_rel_melt_h <- code_rel_melt_h %>%
+#   mutate(code1 = reorder(code1, -total, FUN = mean),
+#          code2 = reorder(code2, total, FUN = mean))
+
+# unique_x_groups <- code_rel_melt_h %>%
+# distinct(code1, brba_code1) %>%
+# arrange(code1)
+# 
+# unique_y_groups <- code_rel_melt_h %>%
+# distinct(code2, brba_code2) %>%
+# arrange(code2)
+
+# x_colors <- setNames(group_colors[unique_x_groups$brba_code1], unique_x_groups$code1)
+# y_colors <- setNames(group_colors[unique_y_groups$brba_code2], unique_y_groups$code2)
+
+ggplot(code_rel_melt_h, aes(x = code2, y = code1)) +
+geom_tile(aes(fill = total)) + 
 scale_fill_gradient2(high = "red")+
@@
 xlab("")+
+scale_x_discrete(position = "top") +
 labs(fill = "Number of co-occurences")+
-theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 14, face = "bold", color = x_colors[levels(code_rel_melt_h$code1)]), 
-      axis.text.y = element_text(size = 14, face = "bold", color = y_colors[levels(code_rel_melt_h$code2)]))+
+theme_minimal() + 
+theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.3, size = 13), 
+      axis.text.y = element_text(size = 13))+
 geom_text(aes(label = total))+
@@
 
-#ggsave("figures/ms_figs/heat_tile.png", width = 10, height = 8, units = c("in"))
-
-```
-
-![](images/heat_tile_ai.png){fig-align="center" width="10in", height = "8in"}
+#ggsave("figures/ms_figs/heat_tile.png", width = 11, height = 12, units = c("in"))
+
+#surveys
+#reshape data
+code_rel_melt_s <- reshape::melt(code_rel_s)
+code_rel_melt_s$variable <- gsub(".", " ", code_rel_melt_s$variable, fixed = TRUE)
+
+code_rel_melt_s <- code_rel_melt_s %>%
+  separate(Code.System, c("key", "code1"), "> ", convert = TRUE)
+
+code_rel_melt_s$key <- str_trim(code_rel_melt_s$key)
+
+colnames(code_rel_melt_s) <- c("brba_code1", "code1", "code2", "total")
+
+#add brba column to second code col
+code_rel_melt2_s <- code_rel_melt_s
+#code_rel_melt2$brba_code2 <- NA
+
+code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Interest holder conflicts"] <- "Interest-holder conflicts"
+code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Missing cross program comparisons"] <- "Missing cross-program comparisons"
+code_rel_melt2_s$code2[code_rel_melt2_s$code2 == "Lack of near real time data"] <- "Lack of near real-time data"
+
+code_rel_melt_h_s <- code_rel_melt2_s %>%
+  #filter(total >= 11) %>%
+  mutate(#bor_box = ifelse(total >= 11, "TRUE", "FALSE"), 
+        #bor_box = as.factor(bor_box), 
+        code1 = as.factor(code1), 
+        code2 = as.factor(code2))
+
+#relevel
+code_rel_melt_h_s$code1 <- factor(code_rel_melt_h_s$code1, levels = c(as.character(unique(code_rel_melt_h_s$code1))))
+
+code_rel_melt_h_s$code2 <- factor(code_rel_melt_h_s$code2, levels =
+c("Unpredictable bycatch patterns", "Missing cross-program comparisons",	"Gaps and inaccuracy",	"Lack of near real-time data", "Cost",	"Discontinuity",	"Confidentiality",	"Lack of incentives",	"Volunteer programs reduce participation",	"Regulated programs reduce participation",	"External factors reducing participation",	"Poor communication and outreach",	"Interest-holder conflicts",	"Stigmatization", "Difficulty assessing impact",	"Limited relevance"))
+
+#plot
+ggplot(code_rel_melt_h_s, aes(x = code2, y = code1)) +
+geom_tile(aes(fill = total)) + 
+scale_fill_gradient2(high = "red")+
+ylab("")+
+xlab("")+
+scale_x_discrete(position = "top") +
+labs(fill = "Number of co-occurences")+
+theme_minimal() + 
+theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.3, size = 13), 
+      axis.text.y = element_text(size = 13))+
+geom_text(aes(label = total))+
+scale_color_manual(values = c("black", "#00000000"))+
+guides(color = "none")
+
+#ggsave("figures/ms_figs/heat_tile_survey.png", width = 8.5, height = 8, units = c("in"))
+
+```
+
+![](images/heat_tile_ai.png){fig-align="center" width="10in", height = "12in"}
+
+![](images/heat_tile_survey_ai.png){fig-align="center" width="10in", height = "12in"}
 

### 2025-11-25 reports/draft_results.qmd
positron

@@
   theme(
-    # Set background color to white
     panel.background = element_rect(fill = "white"),
-    # Set the color and the width of the grid lines for the horizontal axis
     panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
-    # Remove tick marks by setting their length to 0
     axis.ticks.length = unit(0, "mm"),
-    # Remove the title for both axes
     axis.title = element_blank(),
-    # Only left line of the vertical axis is painted in black
     axis.line.y.left = element_line(color = "black"),
-    # Remove labels from the vertical axis
     axis.text.y = element_blank(),
-    # But customize labels for the horizontal axis
     axis.text.x = element_text(family = "Arial", size = 12)) + 
@@
     colour = "dodgerblue4",
-    family = "Arial",
+    #family = "Arial",
     size = 3.5)+
@@
   theme(plot.subtitle = element_text(
-      family = "Arial",
+      #family = "Arial",
       size = 13)
@@
 consv_bar
+#ggsave("figures/ms_figs/consv_perc/consv_bar.pdf", consv_bar, height = 5, width = 5, units = c("in"))
 ```
@@
   distinct(id, .keep_all = TRUE)
+
+freq_job_survey2 %>%
+  mutate(all_codes = sum(value)) %>%
+  group_by(code_cat) %>%
+  summarise(prop = value/all_codes)
 
@@
 ::: panel-tabset
-
 #### Literature
@@
 ![](images/survey_combo.png){fig-align="center" width="5in", height = "8in"}
-
 :::
@@
 #survey figs
-
 #format data

### 2025-12-08 reports/draft_results.qmd
update fig 6,7

@@
 sum_codes <- sum(code_freq$total) #710 codes
+
 code_freq %>% 
@@
 #stacked bar plots
-ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
+freq_job_survey2$code_cat <- factor(freq_job_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))
+
+ggplot(freq_job_survey2, aes(fill=code_cat, y=value, x=fish_ship)) + 
     geom_bar(position="stack", stat="identity") +
-    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
+    scale_fill_manual(values = c("#CFE2F3", "#6D8C9E","#516875","#28343B", "#F1DA9F", "#FED240", "#DBA400", "#614900")) +
     facet_wrap(~bridge_barr) +
@@
     xlab("") + 
-    ylab("Proportion of theme (%)")
-
-#ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))
+    ylab("Percent of theme (%)")
+
+#ggsave("figures/ms_figs/industry/stack_survey.png", width = 8, height = 6, units = c("in"))
 #ggsave("figures/slides_svg/stack_survey.svg", width = 7, height = 6, units = c("in"))
@@
 freq_job_survey3 <- freq_job_survey %>%
-  # group_by(fish_ship, bridge_barr) %>%
-  # mutate(n_total = sum(total)) %>%
-  # ungroup() %>%
-  # group_by(fish_ship, bridge_barr, code_name) %>%
-  # mutate(n_subtotal = sum(total)) %>%
-  # reframe(value = (n_subtotal/n_total)*100) %>%
-  # ungroup() %>%
-  #mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
-  #distinct(id, .keep_all = TRUE) %>%
-  #select(-c(id))
+  group_by(fish_ship, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
   group_by(fish_ship, bridge_barr, code_name) %>%
-  summarise(value = sum(total))
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
+  distinct(id, .keep_all = TRUE) %>%
+  select(-c(id)) %>%
+  group_by(fish_ship, bridge_barr, code_name) %>%
+  summarise(value = sum(value))
 
@@
 ggradar::ggradar(top_bridge,
-        values.radar = c(0, 5, 10), 
+        values.radar = c(0, 11, 22), 
         background.circle.colour = "white",
@@
 ggradar::ggradar(top_barrier,
-        values.radar = c(0, 3, 6), 
+        values.radar = c(0, 14, 28), 
         background.circle.colour = "white",
@@
 
-#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
+ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
 #ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))
@@
 table(n_job_lit$fish_ship)
-
 ```

### 2025-12-11 reports/draft_results.qmd
update ms figures

@@
 
-freq_job_survey$bridge_barr <- factor(freq_job_survey$bridge_barr, levels = c("Bridge", "Barrier"))
+freq_job_survey$bridge_barr <- factor(freq_job_survey$bridge_barr, levels = c("Barrier", "Bridge"))
 
@@
 freq_job_survey2$code_cat <- factor(freq_job_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))
+#freq_job_survey2$bridge_barr <- factor(freq_job_survey2$bridge_barr, levels = c())
 
@@
         gridline.max.colour = "gray60",
-        group.colours = c("#F29325", "#007172"),#007172
+        group.colours = c("#A4BFB8", "#3B5948"),
         legend.position = "bottom", 
@@
         gridline.max.colour = "gray60",
-        group.colours = c("#F29325", "#007172"),#007172
+        group.colours = c("#A4BFB8", "#3B5948"),#007172
         legend.position = "none", 
@@
 
-ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
+#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))
 #ggsave("figures/slides_svg/radar_ba.svg", height = 8, width = 8, units = c("in"))
@@
             .groups = "drop") %>%
-  filter(fish_ship == "Bycatch" | fish_ship == "Ship strikes" | fish_ship == "Overfishing" | fish_ship == "Entanglement" | fish_ship == "Avoid fisheries discharge")
+  filter(fish_ship == "Bycatch" | fish_ship == "Ship strikes")
 
@@
 
-freq_job_lit$bridge_barr <- factor(freq_job_lit$bridge_barr, levels = c("Bridge", "Barrier"))
+freq_job_lit$bridge_barr <- factor(freq_job_lit$bridge_barr, levels = c("Barrier", "Bridge"))
 
@@
 #stacked bar plots
-ggplot(freq_job_lit2, aes(fill=code_level, y=value, x=fish_ship)) + 
+freq_job_lit2$code_cat <- factor(freq_job_lit2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Data barrier", "Ecological barrier", "Social barrier"))
+
+ggplot(freq_job_lit2, aes(fill=code_cat, y=value, x=fish_ship)) + 
     geom_bar(position="stack", stat="identity") +
-    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","#45818E")) +
+    scale_fill_manual(values = c("#CFE2F3", "#6D8C9E","#516875", "#F1DA9F", "#FED240", "#DBA400")) +
     facet_wrap(~bridge_barr) +
@@
     xlab("") + 
-    ylab("Proportion of theme (%)")
+    ylab("Percent of theme (%)")
 
@@
 freq_job_lit3 <- freq_job_lit %>%
-  # group_by(fish_ship, bridge_barr) %>%
-  # mutate(n_total = sum(total)) %>%
-  # ungroup() %>%
-  # group_by(fish_ship, bridge_barr, code_name) %>% 
-  # mutate(n_subtotal = sum(total)) %>%
-  # reframe(value = (n_subtotal/n_total)*100) %>%
-  # ungroup() %>%
-  # mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
-  # distinct(id, .keep_all = TRUE) %>%
-  # select(-c(id)) %>%
+  group_by(fish_ship, bridge_barr) %>%
+  mutate(n_total = sum(total)) %>%
+  ungroup() %>%
   group_by(fish_ship, bridge_barr, code_name) %>% 
-  summarise(value = sum(total))
+  mutate(n_subtotal = sum(total)) %>%
+  reframe(value = (n_subtotal/n_total)*100) %>%
+  ungroup() %>%
+  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
+  distinct(id, .keep_all = TRUE) %>%
+  select(-c(id)) %>%
+  group_by(fish_ship, bridge_barr, code_name) %>%
+  summarise(value = sum(value))
 
@@
 ggradar::ggradar(top_bridge,
-        values.radar = c(0, 20, 40), 
+        values.radar = c(0, 8, 16), 
         background.circle.colour = "white",
@@
         gridline.max.colour = "gray60",
-        group.colours = c("#F29325", "#007172"),
+        group.colours = c("#A4BFB8", "#3B5948"),
         legend.position = "bottom", 
@@
 ggradar::ggradar(top_barrier,
-        values.radar = c(0, 15, 35), 
+        values.radar = c(0, 16, 38), 
         background.circle.colour = "white",
@@
         gridline.max.colour = "gray60",
-        group.colours = c("#F29325", "#007172"),
+        group.colours = c("#A4BFB8", "#3B5948"),
         legend.position = "none", 
@@
 
-#("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
+#ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
 
@@
 
-freq_pos_survey$bridge_barr <- factor(freq_pos_survey$bridge_barr, levels = c("Bridge", "Barrier"))
+#freq_pos_survey$bridge_barr <- factor(freq_pos_survey$bridge_barr, levels = c("Bridge", "Barrier"))
 
@@
 #stacked bar plots
-ggplot(freq_pos_survey2, aes(fill=code_level, y=value, x=position)) + 
+freq_pos_survey2$code_cat <- factor(freq_pos_survey2$code_cat, levels = c("Data bridge", "Ecological bridge", "Social bridge", "Implementation bridge", "Data barrier", "Ecological barrier", "Social barrier", "Implementation barrier"))
+
+ggplot(freq_pos_survey2, aes(fill=code_cat, y=value, x=position)) + 
     geom_bar(position="stack", stat="identity") +
-    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
-    facet_wrap(~bridge_barr) +
+    scale_fill_manual(values = c("#CFE2F3", "#6D8C9E","#516875","#28343B", "#F1DA9F", "#FED240", "#DBA400", "#614900")) +
+    facet_wrap(~bridge_barr, ncol = 1) +
     labs(fill = "") +
@@
     xlab("") + 
-    ylab("Proportion of theme (%)")+
+    ylab("Percent of theme (%)")+
     theme(axis.text.x = element_text(size = 14, color = "black", angle = 60, hjust = 1))
 
-#ggsave("figures/ms_figs/position/stack_survey.png", width = 10, height = 8, units = c("in"))
+ggsave("figures/ms_figs/supp/position/stack_survey.png", width = 8, height = 11, units = c("in"))
 
